### 2018-06-22 ZCB Pricing .Rmd
test 1

---
title: "ZCB Pricing"
author: "VGV"
date: "6/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
print("hello world")
```

### 2018-06-24 ZCB Pricing .Rmd
test 2
Testing repository
test 3
test 4
Real Work

@@
 title: "ZCB Pricing"
-author: "VGV"
+author: 
+- Valentine Chisango
+- George Parekkadavil
+- Vegan Pather
+
 date: "6/22/2018"
@@
 
-```{r}
-print("hello world")
+```{r 1}
+# Closed form solution to Bond price
+
+bond_price <- function(alpha,beta,sigma,t,T,r){
+  A <- (beta*(1-exp(-beta*(T-t))))/(alpha)
+  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
+  exp(-A*r +B)
+}
+
 ```

### 2018-06-24 ZCB Pricing .Rmd
Real Work

@@
 ```
+
+```{r 2}
+# Monte Carlo Simulation
+
+monte_carlo <- function(alpha, beta, sigma, t, T, r, n, s){
+  # s = number of sub-intervals
+  # n = number of simulation trials
+
+  dt <- T/s
+  sim_path <- matrix(NA,nrow = n, ncol = 1) # matrix to store simulated path integrals
+  sim_r <- NULL # vector to store rates on the path
+
+  for (d in 1:n){
+    sim_r[1] <- r
+    for (j in 2:s){
+      mu <- alpha/beta + exp(-beta*dt)*(sim_r[j-1] -alpha/beta)
+      sd <- sqrt((sigma^2/(2*beta))*(1 -exp(-2*beta*(dt))))
+      sim_r[j] <- rnorm(1,mu,sd)
+    }
+
+    int <- dt*(sum(sim_r)) # integral of path
+    sim_path[d,1] <- exp(-int) # bond price of path
+
+  }
+  mean(sim_path) # empirical expectation of bond price using all paths
+}
+
+```
+
+```{r 3}
+# Explicit Method
+```
+
+```{r 4}
+# Implicit Method
+```
+
+```{r 5}
+# Crank-Nicholson Method
+```
+
+```{r 6}
+# Modified Fully Implicit Method
+```
+
+```{r 7, echo = FALSE}
+# Comparison of results
+# Varying short rates
+
+compare_mat <- matrix(NA,nrow = 10, ncol = 8) # matrix of comparison
+
+colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations")
+
+a = 0.01
+b = 0.1
+s = 0.04
+t= 0
+T = 1
+
+for (j in 1:10){
+  compare_mat[j,1] <- a
+  compare_mat[j,2] <- b
+  compare_mat[j,3] <- s
+  compare_mat[j,4] <- 0.01 +0.01*(j-1)
+  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
+  start_time <- proc.time()[1]
+  compare_mat[j,6] <- monte_carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4], n = 1000, s=250)
+  compare_mat[j,7] <- proc.time()[1] -start_time
+  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
+}
+
+var <- sum(compare_mat[,8])/9
+
+library(knitr)
+kable(compare_mat,align = "c")
+
+```

### 2018-06-25 ZCB Pricing .Rmd
Real Work
Addition of explicit method

@@
 - Vegan Pather
-
-date: "6/22/2018"
-output: html_document
+date: "`r format(Sys.time(), '%d %B %Y')`"
+output:
+  html_document: default
 ---
@@
 ```{r 3}
-# Explicit Method
+# Improvements to the Monte Carlo Simulation
+# Antithetic Variates
+
 ```
@@
 ```{r 4}
+# Explicit Method
+
+# Simple Bond price function
+B <- function(t,r){
+  exp(-(T-t)*r)
+}
+
+explicit <- function(alpha, beta, sigma, T, r, j, s){
+
+# j = number of sub-intervals for the short rate
+# s = number of sub-intervals for the time interval
+
+dr = 1/j # lenght of short rate intervals
+dt = T/s # lenght of time intervals
+
+p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
+p_m <- 1/dt -(sigma^2)/(dr^2)
+p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)
+
+V <- matrix(NA, nrow = j + 1, ncol = s + 1)
+V[,s+1] <- rep(1)
+V[j+1,] <- rep(1)
+for (n in seq(s,0,-1)){
+    for (i in 1:j)
+       if (i == 1)
+         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
+       else
+         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])
+
+}
+V
+}
+
+```
+
+```{r 5}
 # Implicit Method
@@
 
-```{r 5}
+```{r 6}
 # Crank-Nicholson Method
@@
 
-```{r 6}
+```{r 7}
 # Modified Fully Implicit Method
@@
 
-```{r 7, echo = FALSE}
+```{r 8, echo = FALSE}
 # Comparison of results

### 2018-07-01 ZCB Pricing .Rmd
Added some initial conditions to the explicit funciton. Not sure what this funciton outputs though? Need to know to continue
New explicit example

@@
 
-explicit <- function(alpha, beta, sigma, T, r, j, s){
+alpha = 0.01
+beta = 0.1
+sigma = 0.04
+I = 1:20
+J = seq(0,0.2,0.005)
 
-# j = number of sub-intervals for the short rate
-# s = number of sub-intervals for the time interval
+dt = 1/length(I)
+dr = J[2] -J[1]
 
-dr = 1/j # lenght of short rate intervals
-dt = T/s # lenght of time intervals
+J[8]
+nr <- length(J)
+nt <- length(I)+1
+V <- matrix(NA, nrow = length(J), ncol = length(I)+1)
 
-p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
-p_m <- 1/dt -(sigma^2)/(dr^2)
-p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)
+V[,length(I)+1] <- rep(1)
 
-V <- matrix(NA, nrow = j + 1, ncol = s + 1)
-V[,s+1] <- rep(1)
-V[j+1,] <- rep(1)
-for (n in seq(s,0,-1)){
-    for (i in 1:j)
-       if (i == 1)
-         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
-       else
-         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])
+count <- 0
+for (i in rev(I)){
+  count <- count+1
+for (j in (1+count):(nr-count)){
+  pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)
+  pm <- 1/dt -sigma^2/(dr^2)
+  pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) 
+  V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
+}
 
 }
-V
-}
+
+V[(nr+1)/2,1]
 

### 2018-07-01 ZCB Pricing .Rmd
More on the explicit method

@@
 knitr::opts_chunk$set(echo = TRUE)
+rm(list = ls(all =TRUE))
 ```
@@
 
-alpha = 0.01
-beta = 0.1
-sigma = 0.04
-I = 1:20
-J = seq(0,0.2,0.005)
+explicit <- function(alpha,beta,sigma,r,I,dr){
 
-dt = 1/length(I)
-dr = J[2] -J[1]
+# I = partition of time
+# dr = length of rate sub-intervals
+# r must be in the middle of partition of J
+# length of J must be twice the length of I
 
-J[8]
-nr <- length(J)
-nt <- length(I)+1
-V <- matrix(NA, nrow = length(J), ncol = length(I)+1)
+J <- seq(0,2*r,dr)
 
-V[,length(I)+1] <- rep(1)
+dt = 1/length(I) # length of each time sub-interval
+dr = J[2] -J[1] # length of each rate sub-interval
 
-count <- 0
-for (i in rev(I)){
-  count <- count+1
+V <- matrix(NA, nrow = length(J), ncol = length(I)+1) # empty matrix
+nr <- length(J) # number of rows of the matrix - represents partition of rate
+nt <- length(I)+1 # number of columns - represents partition of time
+
+V[,length(I)+1] <- rep(1) # Boundary condition at expiry of bond
+
+count <- 0 # set up count variable
+for (i in rev(I)){ # rev is the reverse order of the time partition
+  count <- count+1 # keeping track of loop
   for (j in (1+count):(nr-count)){
-  pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)
-  pm <- 1/dt -sigma^2/(dr^2)
-  pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) 
+    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
+    pm <- 1/dt -sigma^2/(dr^2) # middle value
+    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
     V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
@@
 V[(nr+1)/2,1]
+}
+
+explicit(0.01,0.1,0.04,0.10,1:20,0.005)
 

### 2018-07-02 ZCB Pricing .Rmd
Modified explicit method function

@@
 
-explicit <- function(alpha,beta,sigma,r,I,dr){
+explicit <- function(alpha,beta,sigma,r,I){
 
 # I = partition of time
+# J = partition of rate
 # dr = length of rate sub-intervals
@@
 # length of J must be twice the length of I
+dr <- 2*r/(2*length(I))
 
@@
 dt = 1/length(I) # length of each time sub-interval
-dr = J[2] -J[1] # length of each rate sub-interval
 
@@
 
-explicit(0.01,0.1,0.04,0.10,1:20,0.005)
+explicit(0.01,0.1,0.04,0.05,1:10)
 
@@
 # Implicit Method
+
 ```

### 2018-07-02 ZCB Pricing .Rmd
I have uploaded another verion of the MOnte Carlo simulations as well. This makes use of the Euler discretization. It turns out that the Euler and Milstein discretization is the same.
The variance reduction methods have also been uploaded

@@
 
+```{r}
+#Generate normal RV
+z=rnorm(1000)
+z.=-z
+
+# Another Version of the MOnte Carlo simulations
+Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){
+
+  # alpha, beta, sigma <- Fixed Parameters
+  # T <- maturity time
+  # r0 <- Initial rate at time 0
+  # n <- Number of Simulations
+  # s <- NUmber of Subintervals
+
+  #Simulate interest rates
+  dt <- T/s # Length of sub-intervals
+  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,]= r0
+
+  for (i in 1:n){
+    for (j in 2:(s+1)){
+      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
+      sim_path[j,i]=sim_path[j-1,i]+dr
+    }
+  }
+
+  # Monte Carlo Simulations
+  Sum=colSums(sim_path[2:(s+1),]*dt)
+  int=exp(-Sum)
+  mean=mean(int)
+  sd=sd(int)/sqrt(n)
+  result=c(mean,sd)
+  result
+}
+```
+
 ```{r 3}
 # Improvements to the Monte Carlo Simulation
+
+#################################################################################
 # Antithetic Variates
+################################################################################
+
+Antithetic_variates= function(alpha,beta,sigma,T,r0,n,s){
+  dt <- T/s # Length of sub-intervals
+  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using inverse RV
+  sim_path[1,]= r0
+  sim_path_inv[1,]=r0
+
+  for (i in 1:n){
+    for (j in 2:(s+1)){
+      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
+      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
+      sim_path[j,i]=sim_path[j-1,i]+dr
+      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i
+
+    }
+  }
+
+  # Monte Carlo Simulations
+  Sum=colSums(sim_path[2:(s+1),]*dt)
+  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
+  int.=exp(-Sum.)
+  int=exp(-Sum)# Estimate using the conjugate rates
+  Average=(int+int.)/2 # Average of estimates
+  mean=mean(Average)
+  sd=sd(Average)/sqrt(n)
+  result=c(mean,sd)
+  result
+
+}
+
+```
+
+```{r}
+#################################################################################
+# Moment matching
+#################################################################################
+
+Moment_Matching=function(alpha,beta,sigma,T,r0,n,s){
+
+  # alpha, beta, sigma <- Fixed Parameters
+  # T <- maturity time
+  # r0 <- Initial rate at time 0
+  # n <- Number of Simulations
+  # s <- NUmber of Subintervals
+
+  #Simulate interest rates
+  dt <- T/s # Length of sub-intervals
+  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,]= r0
+  z=rnorm(s)
+  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION
+
+  for (i in 1:n){
+    for (j in 2:(s+1)){
+      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j-1]# Euler Discretization
+      sim_path[j,i]=sim_path[j-1,i]+dr
+    }
+  }
+
+  # Monte Carlo Simulations
+  Sum=colSums(sim_path[2:(s+1),]*dt)
+  int=exp(-Sum)
+  mean=mean(int)
+  sd=sd(int)/sqrt(n)
+  result=c(mean,sd)
+  result
+}
+```
+
+```{r}
+#################################################################################
+# Control Variates
+#################################################################################
+
+# We have decided to make use of the CIR model as our control variate process.
+# Below is the closed form solution under the CIR model
+bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
+  h <- sqrt(alpha^(2)+2*sigma^(2))
+  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
+  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
+  A*exp(-B*r0)
+}
+
+# Monte Carlo Simulations of Bond Price under the CIR model
+
+CIR_MC= function(alpha,beta,sigma,T,r0,n,s){
+
+  dt <- T/s # Length of sub-intervals
+  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,]= r0
+
+  for (i in 1:n){
+    for (j in 2:(s+1)){
+      dr=alpha*(beta-sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
+      sim_path[j,i]=sim_path[j-1,i]+dr
+
+    }
+  }
+
+  # Monte Carlo Simulations
+  Sum=colSums(sim_path[2:(s+1),]*dt)
+  int=exp(-Sum)
+  mean=mean(int)
+  sd=sd(int)/sqrt(n)
+  result=c(mean,sd)
+  result
+
+}
+
+# Therefore the control variates estimate:
+
+Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
+  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
+}
 

### 2018-07-02 ZCB Pricing .Rmd
I have uploaded aother verion og the MOnte Carlo simulations which makes use of the Euler discretization.
The Variance reduction methods have also been uploaded

@@
 knitr::opts_chunk$set(echo = TRUE)
-rm(list = ls(all =TRUE))
 ```
@@
 ```{r}
+# Another version of the MOnte Carlo simulation
+
 #Generate normal RV
@@
 
-# Another Version of the MOnte Carlo simulations
 Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){
@@
       dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
-      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
+      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]# Makes use of conjugate estimates
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   int.=exp(-Sum.)
-  int=exp(-Sum)# Estimate using the conjugate rates
-  Average=(int+int.)/2 # Average of estimates
+  int=exp(-Sum)
+  Average=(int+int.)/2 # Average of both vectors
   mean=mean(Average)
@@
 }
-
 ```
@@
   z=rnorm(s)
-  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION
+  z_m= z-mean(z)  # Moment matching transformation
 
@@
 
-explicit <- function(alpha,beta,sigma,r,I){
+explicit <- function(alpha, beta, sigma, T, r, j, s){
 
-# I = partition of time
-# J = partition of rate
-# dr = length of rate sub-intervals
-# r must be in the middle of partition of J
-# length of J must be twice the length of I
-dr <- 2*r/(2*length(I))
+# j = number of sub-intervals for the short rate
+# s = number of sub-intervals for the time interval
 
-J <- seq(0,2*r,dr)
+dr = 1/j # lenght of short rate intervals
+dt = T/s # lenght of time intervals
 
-dt = 1/length(I) # length of each time sub-interval
+p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
+p_m <- 1/dt -(sigma^2)/(dr^2)
+p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)
 
-V <- matrix(NA, nrow = length(J), ncol = length(I)+1) # empty matrix
-nr <- length(J) # number of rows of the matrix - represents partition of rate
-nt <- length(I)+1 # number of columns - represents partition of time
-
-V[,length(I)+1] <- rep(1) # Boundary condition at expiry of bond
-
-count <- 0 # set up count variable
-for (i in rev(I)){ # rev is the reverse order of the time partition
-  count <- count+1 # keeping track of loop
-  for (j in (1+count):(nr-count)){
-    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
-    pm <- 1/dt -sigma^2/(dr^2) # middle value
-    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
-    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
-  }
+V <- matrix(NA, nrow = j + 1, ncol = s + 1)
+V[,s+1] <- rep(1)
+V[j+1,] <- rep(1)
+for (n in seq(s,0,-1)){
+    for (i in 1:j)
+       if (i == 1)
+         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
+       else
+         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])
 
 }
-
-V[(nr+1)/2,1]
+V
 }
-
-explicit(0.01,0.1,0.04,0.05,1:10)
 
@@
 # Implicit Method
-
 ```

### 2018-07-04 ZCB Pricing .Rmd
Addition of rough implicit method

--- 2018-07-02 ZCB Pricing .Rmd
@@
 # Implicit Method
+# Implicit Method
+
+implicit <- function(alpha,beta,sigma,r,I,J){
+  # I = partition of time interval
+  # J = partition of short rate variable
+
+  nr <- length(J) # number of rows based on rate grid points
+  nc <- length(I) # number of columns based on number of time grid points
+
+  dr <- J[2] - J[1] #length of each sub-interval across J
+  dt <- 1/length(I) #length of each sub-interval across I
+
+  # For each j in J we define the following functions at a fixed time point
+
+  pd <- function(j){
+    dt*((alpha-beta*J[j+1])/(2*dr) - (sigma^2)/(2*dr^2))
+
+  }
+
+  pm <- function(j){
+    dt*(J[j+1] + 1/dt)
+  }
+
+  pu <- function(j){
+    -dt*((alpha-beta*J[j+1])/(2*dr) + (sigma^2)/(2*dr^2))
+
+  }
+
+  # Setting up tridiagonal matrix
+  Diag <- matrix(0,nrow = nr-1,ncol = nr-1)
+
+  # Filling main diagonal
+  for (j in 1:(nr-1)){
+    Diag[j,j] <- pm(j)
+
+  }
+
+  # Filling lower diagonal
+  for (j in 2:(nr-1)){
+    Diag[j,j-1] <- pd(j)
+  }
+
+  # Filling upper diagonal
+  for (j in 1:(nr-2)){
+    Diag[j,j+1] <- pu(j)
+  }
+
+  B <- matrix(1,ncol = 1,nrow = nr-1) # The matrix of bond prices at maturity time
+
+  for (i in I){
+    C <- matrix(0,ncol = 1, nrow = nr-1) # Another matrix for boundary conditions
+    C[nr-1,1] <- (-pu(nr-1))*B[nr-1,1]
+    C[1,1] <- -pd(1)
+    A <- B + C # Working backwards recursively 
+    B <- solve(Diag)%*%A 
+  }
+
+  B # Output of bond prices at time 0 for varying rates
+
+}
+
+R <- implicit(0.08,0.8,0.005,0.05,1:50,seq(0,0.1,0.01))
 

### 2018-07-04 ZCB Pricing .Rmd
in explicit: added comments and changed parameter values to match implicit

@@
 count <- 0 # set up count variable
-for (i in rev(I)){ # rev is the reverse order of the time partition
+for (i in rev(I)){ # rev is the reverse order of the time partition | i corresponds to the columns of the lattice
   count <- count+1 # keeping track of loop
-  for (j in (1+count):(nr-count)){
+  for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
     pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
@@
 
-explicit(0.01,0.1,0.04,0.05,1:10)
+explicit(0.08,0.8,0.005,0.05,1:10)
 

### 2018-07-05 ZCB Pricing .Rmd
Modifications to the implicit method
Addition of the Crank-Nicholson Method

@@
 # Simple Bond price function
-B <- function(t,r){
+B <- function(t,T,r){
   exp(-(T-t)*r)
@@
 ```{r 5}
-# Implicit Method
+
 # Implicit Method
@@
   pm <- function(j){
-    dt*(J[j+1] + 1/dt)
+    dt*(J[j+1] + 1/dt +sigma^2/(dr^2))
   }
@@
 # Crank-Nicholson Method
+
+CN <- function(alpha, beta, sigma, r, I, J){
+  # I = partition of time interval
+  # J = partition of short rate interval
+
+  X <- length(I) # number of time grid points
+  Y <- length(J) # number of rate grid points
+
+  nr <- Y - 1 # number of rows
+
+  dr <- J[2] - J[1]
+  dt <- 1/X
+
+  #===========================================================================================
+  # Define the following functions for j = 1,...,nr at each time point i
+
+  pd <- function(j){
+    (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
+  }
+
+  pm_1 <- function(j){
+    J[j+1]/2 + 1/dt + sigma^2/(2*dr^2)
+  }
+
+  pm_2 <- function(j){
+    -J[j+1]/2 + 1/dt - sigma^2/(2*dr^2)
+  }
+
+  pu <- function(j){
+    - (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
+  }
+
+  #===========================================================================================
+  # Define 2 tridiagonal matricies. One for time point i and one for time point i+1
+
+  Diag_1 <- matrix(0,nrow = nr,ncol = nr)
+  Diag_2 <- matrix(0,nrow = nr,ncol = nr)
+
+  # Main diagonal of matrix 1
+  for (j in 1:nr){
+    Diag_1[j,j] <- pm_1(j)
+
+  }
+
+  # Filling lower diagonal of matrix 1
+  for (j in 2:nr){
+    Diag_1[j,j-1] <- pd(j)
+  }
+
+  # Filling upper diagonal of matirx 1
+  for (j in 1:(nr-1)){
+    Diag_1[j,j+1] <- pu(j)
+  }
+
+  # Main diagonal of matrix 2
+  for (j in 1:nr){
+    Diag_2[j,j] <- pm_2(j)
+
+  }
+
+  # Filling lower diagonal of matrix 2
+  for (j in 2:nr){
+    Diag_2[j,j-1] <- -pd(j)
+  }
+
+  # Filling upper diagonal of matirx 2
+  for (j in 1:(nr-1)){
+    Diag_2[j,j+1] <- -pu(j)
+  }
+
+  #===========================================================================================
+  # Constructing more matricies and iterating the procedure from maturity to time 0
+  # These matricies take care of the boundary conditions
+  C_1 <- matrix(0,nrow = nr,ncol = 1)
+  C_1[1,1] <- pd(1)
+  C_1[nr,1] <- pu(nr)
+
+  C_2 <- matrix(0,nrow = nr,ncol = 1)
+  C_2[1,1] <- -pd(1)
+  C_2[nr,1] <- -pu(nr)
+
+  # Vector of bond price values at time i
+  Bond_values <- matrix(1,nrow = nr, ncol = 1)
+
+  for (i in I){
+    Inv <- solve(Diag_1)
+    RHS <- Diag_2%*%Bond_values + C_2 - C_1
+    Bond_values <- Inv%*%RHS
+  }
+
+  Bond_values
+
+}
+
+G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))
+
 ```

### 2018-07-05 ZCB Pricing .Rmd
Added corrected bond function and some plots

@@
 bond_price <- function(alpha,beta,sigma,t,T,r){
-  A <- (beta*(1-exp(-beta*(T-t))))/(alpha)
+  A <- (1-exp(-beta*(T-t)))/(beta)
   B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
@@
 
-G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))
+G <- CN(0.08,0.8,0.005,0.05,I=1:100, J = seq(-0.3,0.5,0.01))
 
+#============================================================================================
+# Doing some plots
+plot(G)
+xvec <- seq(-0.3,0.5,0.01)
+S <- NULL
+for (r in 1:length(xvec)){
+  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+}
+plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+lines(xvec,S, col ="blue", lty =1.5)
 ```

### 2018-07-05 ZCB Pricing .Rmd
Extra plot

--- 2018-07-05 ZCB Pricing .Rmd
@@
 
-R <- implicit(0.08,0.8,0.005,0.05,1:50,seq(0,0.1,0.01))
+R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01))
 
+#============================================================================================
+# Doing some plots
+
+xvec <- seq(-0.3,0.5,0.01)
+S <- NULL
+for (r in 1:length(xvec)){
+  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+  }
+plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
+lines(xvec,S, col ="blue", lty =1.5)
 ```
@@
 
-G <- CN(0.08,0.8,0.005,0.05,I=1:1000, J = seq(0,0.10,0.01))
+G <- CN(0.08,0.8,0.005,0.05, I=1:100, J = seq(-0.3,0.5,0.01))
 
+#============================================================================================
+# Doing some plots
+
+xvec <- seq(-0.3,0.5,0.01)
+S <- NULL
+for (r in 1:length(xvec)){
+  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+}
+plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+lines(xvec,S, col ="blue", lty =1.5)
 ```

### 2018-07-24 ZCB Pricing .Rmd
Extra stuff

@@
 
-explicit <- function(alpha,beta,sigma,r,I){
+explicit <- function(alpha,beta,sigma,r,I,T){
 
@@
 
-dt = 1/length(I) # length of each time sub-interval
+dt = T/length(I) # length of each time sub-interval
 
@@
   for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
-    pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr) # up value
-    pm <- 1/dt -sigma^2/(dr^2) # middle value
-    pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) # down value
-    V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
+    pu <- dt*(sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)) # up value
+    pm <- 1 - (sigma^2*dt)/(dr^2) # middle value
+    pd <- dt*(sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr)) # down value
+    V[j,i] <- ((1+J[nr-j]*dt)^(-1))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
   }
@@
 V[(nr+1)/2,1]
+
 }
 
-explicit(0.08,0.8,0.005,0.05,1:10)
+X = explicit(0.08,0.8,0.005,0.03,1:50,T=1)
+Z <- bond_price(0.08,0.8,0.005,0,1,0.03)
 
@@
 
-implicit <- function(alpha,beta,sigma,r,I,J){
+implicit <- function(alpha,beta,sigma,r,I,J,T){
   # I = partition of time interval
@@
   dr <- J[2] - J[1] #length of each sub-interval across J
-  dt <- 1/length(I) #length of each sub-interval across I
+  dt <- T/length(I) #length of each sub-interval across I
 
@@
 
-R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01))
+R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01),T=5)
 
@@
 for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
   }
@@
 
-CN <- function(alpha, beta, sigma, r, I, J){
+CN <- function(alpha, beta, sigma, r,T, I, J){
   # I = partition of time interval
@@
   dr <- J[2] - J[1]
-  dt <- 1/X
+  dt <- T/X
 
@@
 
-G <- CN(0.08,0.8,0.005,0.05, I=1:100, J = seq(-0.3,0.5,0.01))
+G <- CN(0.08,0.8,0.005,0.05, T=5, I=1:365, J = seq(-0.3,0.5,0.01))
 

### 2018-07-24 ZCB Pricing .Rmd
Changes to monte carlo

@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
-      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
+      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
+      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j-1]# Euler Discretization
+      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr

### 2018-07-24 ZCB Pricing .Rmd
Modifications to Monte Carlo

@@
 
-bond_price <- function(alpha,beta,sigma,t,T,r){
+bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=1,r=0.08){
   A <- (1-exp(-beta*(T-t)))/(beta)
@@
 
-monte_carlo <- function(alpha, beta, sigma, t, T, r, n, s){
+monte_carlo <- function(alpha =0.08, beta=0.8, sigma=0.005, t=0, T=1, r=0.08, n=1000, s=100){
   # s = number of sub-intervals
@@
 ```{r}
-#Generate normal RV
-z=rnorm(1000)
-z.=-z
 
 # Another Version of the MOnte Carlo simulations
-Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){
+Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
 
@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sd=sd(int)/sqrt(n)
-  result=c(mean,sd)
+  result=mean
   result
 }
+
 ```
@@
 
-Antithetic_variates= function(alpha,beta,sigma,T,r0,n,s){
+Antithetic_variates= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
   dt <- T/s # Length of sub-intervals
@@
   sim_path_inv[1,]=r0
+  z = rnorm(n)
+  z. = -z
 
@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
-      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
+      dr_i= (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sd=sd(Average)/sqrt(n)
-  result=c(mean,sd)
+  result= mean
   result
@@
 
-Moment_Matching=function(alpha,beta,sigma,T,r0,n,s){
+Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
 
@@
   sim_path[1,]= r0
-  z=rnorm(s)
+  z=rnorm(n)
   z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION
@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
+```{r}
+
+#============================================================================================
+# Doing some plots
+
+xvec <- seq(-0.3,0.5,0.01)
+S <- NULL
+for (r in 1:length(xvec)){
+  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
+}
+
+CR <- NULL
+AV <- NULL
+MM <- NULL
+
+for (k in 1: length(xvec)){
+  CR[k] <- Crude_Monte_Carlo(r0 = xvec[k], T=5)
+}
+
+for (s in 1: length(xvec)){
+  AV[s] <- Antithetic_variates(r0 = xvec[s], T =5)
+
+}
+
+for (j in 1: length(xvec)){
+  MM[j] <- Moment_Matching(r0 = xvec[j], T =5)
+
+}
+
+plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
+lines(xvec,S, col ="blue", lty =1.5)
+lines(xvec,AV, col ="black", lty =1.5)
+lines(xvec,MM, col ="yellow", lty =1.5)
+```
+
 ```{r 4}
@@
 
-explicit <- function(alpha,beta,sigma,r,I,T){
+explicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100,T=2){
 
@@
 
-X = explicit(0.08,0.8,0.005,0.03,1:50,T=1)
-Z <- bond_price(0.08,0.8,0.005,0,1,0.03)
+#============================================================================================
+#Doing some plots
+# 
+# xvec <- seq(-0.3,0.5,0.01)
+# H <- NULL
+# for (r in 1:length(xvec)){
+#   S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+# }
+# 
+# for (i in 1:length(xvec)){
+#   H[i] <- explicit(r = xvec[i], I= 1:50, T=5)
+# }
+# 
+# plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+# lines(xvec,S, col ="blue", lty =1.5)
 
@@
 
-implicit <- function(alpha,beta,sigma,r,I,J,T){
+implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100, J =seq(0,0.10,0.01),T=1){
   # I = partition of time interval
@@
 
-R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01),T=5)
+#============================================================================================
 
-#============================================================================================
 # Doing some plots
 
-xvec <- seq(-0.3,0.5,0.01)
+xvec <- seq(-0.3,0.6,0.01)
+R <- implicit(T=5,J= xvec, I = 1:1250)
 S <- NULL
@@
 lines(xvec,S, col ="blue", lty =1.5)
+
 ```
@@
 
+```{r}
+# Crank Nicolson 2.0
+
+CN_2 <- function(alpha = 0.08,beta =0.8,sigma=0.005,T=5,r =0.05,I = 1:1250, J = seq(-0.3,0.5,0.01)){
+
+  M <- length(J)
+
+}
+
+```
+
 ```{r 7}

### 2018-07-24 ZCB Pricing .Rmd
Modified CN

@@
 
-CN <- function(alpha, beta, sigma, r,T, I, J){
+CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250==, J = seq(-0.3,0.5,0.01)){
   # I = partition of time interval
@@
 
-  X <- length(I) # number of time grid points
-  Y <- length(J) # number of rate grid points
+  M <- length(J)
+  N <- length(I)
 
-  nr <- Y - 1 # number of rows
-
-  dr <- J[2] - J[1]
-  dt <- T/X
-
+  dt <- T/N
+  dr <- J[2] -J[1]
   #===========================================================================================
-  # Define the following functions for j = 1,...,nr at each time point i
+  # Define the following functions for j = 1,...,M at each time point i
 
   pd <- function(j){
-    (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
+    (alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2))
   }
 
-  pm_1 <- function(j){
-    J[j+1]/2 + 1/dt + sigma^2/(2*dr^2)
-  }
-
-  pm_2 <- function(j){
-    -J[j+1]/2 + 1/dt - sigma^2/(2*dr^2)
+  pm <- function(j){
+    sigma^2/(2*(dr^2)) + J[j]/2
   }
@@
   pu <- function(j){
-    - (alpha -beta*J[j+1])/(2*dr) - sigma^2/(4*dr^2)
+    -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2)) 
   }
@@
 
-  Diag_1 <- matrix(0,nrow = nr,ncol = nr)
-  Diag_2 <- matrix(0,nrow = nr,ncol = nr)
+  Diag_1 <- matrix(0,nrow = M,ncol = M)
+  Diag_2 <- matrix(0,nrow = M,ncol = M)
 
   # Main diagonal of matrix 1
-  for (j in 1:nr){
-    Diag_1[j,j] <- pm_1(j)
+  for (j in 1:M){
+    Diag_1[j,j] <- -1/dt - pm(j)
 
@@
   # Filling lower diagonal of matrix 1
-  for (j in 2:nr){
-    Diag_1[j,j-1] <- pd(j)
+  for (j in 2:M){
+    Diag_1[j,j-1] <- -pd(j)
   }
@@
   # Filling upper diagonal of matirx 1
-  for (j in 1:(nr-1)){
-    Diag_1[j,j+1] <- pu(j)
+  for (j in 1:M-1){
+    Diag_1[j,j+1] <- -pu(j)
   }
@@
   # Main diagonal of matrix 2
-  for (j in 1:nr){
-    Diag_2[j,j] <- pm_2(j)
+  for (j in 1:M){
+    Diag_2[j,j] <- -1/dt + pm(j)
 
@@
   # Filling lower diagonal of matrix 2
-  for (j in 2:nr){
-    Diag_2[j,j-1] <- -pd(j)
+  for (j in 2:M){
+    Diag_2[j,j-1] <- pd(j)
   }
@@
   # Filling upper diagonal of matirx 2
-  for (j in 1:(nr-1)){
-    Diag_2[j,j+1] <- -pu(j)
+  for (j in 1:M-1){
+    Diag_2[j,j+1] <- pu(j)
   }
@@
   # Constructing more matricies and iterating the procedure from maturity to time 0
-  # These matricies take care of the boundary conditions
-  C_1 <- matrix(0,nrow = nr,ncol = 1)
-  C_1[1,1] <- pd(1)
-  C_1[nr,1] <- pu(nr)
 
-  C_2 <- matrix(0,nrow = nr,ncol = 1)
-  C_2[1,1] <- -pd(1)
-  C_2[nr,1] <- -pu(nr)
+  Bond_values <- matrix(1,nrow = M, ncol = 1)
 
-  # Vector of bond price values at time i
-  Bond_values <- matrix(1,nrow = nr, ncol = 1)
+  # C_1 <- matrix(0,nrow = M,ncol = 1)
+  # C_1[1,1] <- -pd(1)
+  # C_1[M,1] <- -pu(M)
+  # 
+  # C_2 <- matrix(0,nrow = M,ncol = 1)
+  # C_2[1,1] <- pd(1)
+  # C_2[M,1] <- pu(M)
 
-  for (i in I){
+  for (i in 1:(length(I)+1)){
     Inv <- solve(Diag_1)
-    RHS <- Diag_2%*%Bond_values + C_2 - C_1
+    RHS <- Diag_2%*%Bond_values 
     Bond_values <- Inv%*%RHS
@@
 
-G <- CN(0.08,0.8,0.005,0.05, T=5, I=1:365, J = seq(-0.3,0.5,0.01))
-
 #============================================================================================
@@
 for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
 }
-plot(G, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
 lines(xvec,S, col ="blue", lty =1.5)
-```
-
-```{r}
-# Crank Nicolson 2.0
-
-CN_2 <- function(alpha = 0.08,beta =0.8,sigma=0.005,T=5,r =0.05,I = 1:1250, J = seq(-0.3,0.5,0.01)){
-
-  M <- length(J)
-
-}
-
 ```

### 2018-07-24 ZCB Pricing .Rmd
Modified CN

@@
 
-CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250==, J = seq(-0.3,0.5,0.01)){
+CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.6,0.01)){
   # I = partition of time interval
@@
 
-xvec <- seq(-0.3,0.5,0.01)
+xvec <- seq(-0.4,0.6,0.01)
 S <- NULL

### 2018-07-25 ZCB Pricing .Rmd
Updated CN and some Comparisons with MCs

@@
   # C_1 <- matrix(0,nrow = M,ncol = 1)
-  # C_1[1,1] <- -pd(1)
-  # C_1[M,1] <- -pu(M)
+  # C_1[1,1] <- -2*pd(1)
+  # C_1[M,1] <- -2*pu(M)
   # 
@@
   # C_2[M,1] <- pu(M)
+  Inv <- solve(Diag_1)
 
-  for (i in 1:(length(I)+1)){
-    Inv <- solve(Diag_1)
+  for (i in 1:(length(I))){
+
     RHS <- Diag_2%*%Bond_values 
@@
 
-compare_mat <- matrix(NA,nrow = 10, ncol = 8) # matrix of comparison
+compare_mat <- matrix(NA,nrow = 10, ncol = 10) # matrix of comparison
 
-colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations")
-
-a = 0.01
-b = 0.1
-s = 0.04
-t= 0
-T = 1
+colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations", "Moment Matching", "System Time")
 
 for (j in 1:10){
-  compare_mat[j,1] <- a
-  compare_mat[j,2] <- b
-  compare_mat[j,3] <- s
+  compare_mat[j,1] <- 0.08
+  compare_mat[j,2] <- 0.8
+  compare_mat[j,3] <- 0.005
   compare_mat[j,4] <- 0.01 +0.01*(j-1)
@@
   start_time <- proc.time()[1]
-  compare_mat[j,6] <- monte_carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4], n = 1000, s=250)
+  compare_mat[j,6] <- Crude_Monte_Carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
   compare_mat[j,7] <- proc.time()[1] -start_time
   compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
+  start_time <- proc.time()[1]
+  compare_mat[j,9] <- Moment_Matching(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
+  compare_mat[j,10] <- proc.time()[1] - start_time
+
 }

### 2018-07-25 ZCB Pricing .Rmd
Removed my MC chunk

@@
 ```{r 2}
-# Monte Carlo Simulation
-
-monte_carlo <- function(alpha =0.08, beta=0.8, sigma=0.005, t=0, T=1, r=0.08, n=1000, s=100){
-  # s = number of sub-intervals
-  # n = number of simulation trials
-
-  dt <- T/s
-  sim_path <- matrix(NA,nrow = n, ncol = 1) # matrix to store simulated path integrals
-  sim_r <- NULL # vector to store rates on the path
-
-  for (d in 1:n){
-    sim_r[1] <- r
-    for (j in 2:s){
-      mu <- alpha/beta + exp(-beta*dt)*(sim_r[j-1] -alpha/beta)
-      sd <- sqrt((sigma^2/(2*beta))*(1 -exp(-2*beta*(dt))))
-      sim_r[j] <- rnorm(1,mu,sd)
-    }
-
-    int <- dt*(sum(sim_r)) # integral of path
-    sim_path[d,1] <- exp(-int) # bond price of path
-
-  }
-  mean(sim_path) # empirical expectation of bond price using all paths
-}
-
-```
-
-```{r}
-
-# Another Version of the MOnte Carlo simulations
+#################################################################################
+# Crude Monte Carlo
+#################################################################################
 Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
@@
 
-```{r}
+```{r 4}
 #################################################################################
@@
 
-```{r}
+```{r 5}
 #################################################################################
@@
 
-```{r}
+```{r 6}
 
-#============================================================================================
+#======================================================================================
 # Doing some plots
@@
 
-```{r 4}
+```{r 7}
 # Explicit Method
@@
 
-```{r 5}
+```{r 8}
 
@@
 
-```{r 6}
+```{r 9}
 # Crank-Nicholson Method
@@
 
-```{r 7}
+```{r 11}
 # Modified Fully Implicit Method
@@
 
-```{r 8, echo = FALSE}
+```{r 12, echo = FALSE}
 # Comparison of results
@@
 
-var <- sum(compare_mat[,8])/9
-
-library(knitr)
-kable(compare_mat,align = "c")
+# library(knitr)
+# kable(compare_mat,align = "c")
 

### 2018-07-26 ZCB Pricing .Rmd
CN

@@
 
-implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100, J =seq(0,0.10,0.01),T=1){
+implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
   # I = partition of time interval
@@
 
-xvec <- seq(-0.3,0.6,0.01)
+xvec <- seq(-0.4,0.6,0.005)
 R <- implicit(T=5,J= xvec, I = 1:1250)
@@
 
-CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.6,0.01)){
+CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.8,0.005)){
   # I = partition of time interval
@@
     -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2))
+
   }
@@
 
-  for (i in 1:(length(I))){
+  for (i in I){
 
@@
 
-xvec <- seq(-0.4,0.6,0.01)
+xvec <- seq(-0.4,0.8,0.005)
 S <- NULL
@@
 ```{r 11}
-# Modified Fully Implicit Method
+
 ```

### 2018-07-27 ZCB Pricing .Rmd
MC Comments and adapting finite difference methods

@@
 
-bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=1,r=0.08){
+bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=5,r=0.08){
   A <- (1-exp(-beta*(T-t)))/(beta)
@@
 ```{r 2}
-#################################################################################
+
 # Crude Monte Carlo
-#################################################################################
-Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
+
+Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
 
@@
   # T <- maturity time
-  # r0 <- Initial rate at time 0
+  # r <- Initial rate at time 0
   # n <- Number of Simulations
-  # s <- NUmber of Subintervals
+  # s <- NUmber of Sub-intervals over time
 
@@
   dt <- T/s # Length of sub-intervals
-  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path[1,]= r0
+  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,]= r # Initial rates on first row.
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt)
-  int=exp(-Sum)
-  mean=mean(int)
-  sd=sd(int)/sqrt(n)
-  result=mean
+  Sum = colSums(sim_path[2:(s+1),]*dt) # Approximate the integral using summation
+  int = exp(-Sum) # Take the exponent of the Integral
+  mean = mean(int) # Find the average of expression
+  sd = sd(int)/sqrt(n)
+  result = mean
   result
@@
 
-#################################################################################
 # Antithetic Variates
-################################################################################
 
-Antithetic_variates= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
+Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r = 0.08,n=1000,s=100){
   dt <- T/s # Length of sub-intervals
   sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using inverse RV
-  sim_path[1,]= r0
-  sim_path_inv[1,]=r0
-  z = rnorm(n)
-  z. = -z
+  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
+  sim_path[1,] = r
+  sim_path_inv[1,] = r
+  z = rnorm(n) # Generate standard normal values
+  z. = -z # Estimate negative value
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
-      dr_i= (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
+      dr_i= (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt)
+  Sum=colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
   Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
-  int.=exp(-Sum.)
-  int=exp(-Sum)# Estimate using the conjugate rates
-  Average=(int+int.)/2 # Average of estimates
-  mean=mean(Average)
+  int=exp(-Sum.) #Exponential of the estimate
+  int.=exp(-Sum) #Exponential of the estimate under the negative rv 
+  Average=(int+int.)/2   # The average of the expressions is taken for new estimate
+  mean=mean(Average)  # The average of the expression is taken for the estimate
   sd=sd(Average)/sqrt(n)
@@
 
-Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
+Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=100000,s=100){
 
@@
 
-# Simple Bond price function
-B <- function(t,T,r){
-  exp(-(T-t)*r)
+explicit = function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
+
+  # I = partition of time interval
+  # J = partition of short rate interval
+
+  M <- length(J)
+  N <- length(I)
+
+  dt <- T/N
+  dr <- J[2] -J[1]
+
+  pd <- function(j){
+    ((J[j]+1/dt)^(-1))*(sigma^2/(2*(dr^2)) -(alpha -beta*J[j])/(2*dr))
   }
 
-explicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100,T=2){
+  pm <- function(j){
+    ((J[j]+1/dt)^(-1))*(1/dt -sigma^2/(dr^2))
+  }
 
-# I = partition of time
-# J = partition of rate
-# dr = length of rate sub-intervals
-# r must be in the middle of partition of J
-# length of J must be twice the length of I
-dr <- 2*r/(2*length(I))
+  pu <- function(j){
+    ((J[j]+1/dt)^(-1))*(sigma^2/(2*(dr^2)) + (alpha -beta*J[j])/(2*dr))
+  }
 
-J <- seq(0,2*r,dr)
+  Diag_1 <- matrix(0,ncol = M, nrow = M)
+    # Main diagonal of matrix 1
 
-dt = T/length(I) # length of each time sub-interval
-
-V <- matrix(NA, nrow = length(J), ncol = length(I)+1) # empty matrix
-nr <- length(J) # number of rows of the matrix - represents partition of rate
-nt <- length(I)+1 # number of columns - represents partition of time
-
-V[,length(I)+1] <- rep(1) # Boundary condition at expiry of bond
-
-count <- 0 # set up count variable
-for (i in rev(I)){ # rev is the reverse order of the time partition | i corresponds to the columns of the lattice
-  count <- count+1 # keeping track of loop
-  for (j in (1+count):(nr-count)){ # j corresponds to the rows of the lattice
-    pu <- dt*(sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)) # up value
-    pm <- 1 - (sigma^2*dt)/(dr^2) # middle value
-    pd <- dt*(sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr)) # down value
-    V[j,i] <- ((1+J[nr-j]*dt)^(-1))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
-  }
+  for (j in 1:M){
+    Diag_1[j,j] <- pm(j)
 
@@
 
-V[(nr+1)/2,1]
+  # Filling lower diagonal of matrix 1
+  for (j in 2:M){
+    Diag_1[j,j-1] <- pd(j)
+  }
 
+  # Filling upper diagonal of matirx 1
+  for (j in 1:(M-1)){
+    Diag_1[j,j+1] <- pu(j)
+  }
+
+  Bond_values <- matrix(1,nrow=M, ncol =1)
+
+  for (i in I){
+    Bond_values <- Diag_1%*%Bond_values
+    Bond_values <- Bond_values
+  }
+
+  index = match(as.character(r),xvec)
+  Bond_values[index]
 }
@@
 # 
-# xvec <- seq(-0.3,0.5,0.01)
-# H <- NULL
-# for (r in 1:length(xvec)){
-#   S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
+#  xvec <- seq(-0.4,0.6,0.005)
+# S <- NULL
+# for (i in 1:length(xvec)){
+#    S[i] <- bond_price(alpha = 0.08,beta =0.8,sigma =0.005,t = 0, T = 5, r = xvec[i])
 #  }
 #  
-# for (i in 1:length(xvec)){
-#   H[i] <- explicit(r = xvec[i], I= 1:50, T=5)
-# }
+# H <- explicit(r = 0.08, I= 1:100000, T=5,alpha = 0.08, beta =0.8, sigma= 0.005, J = xvec)
 # 
-# plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+#  
+#  plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit vs Known Solution")
 #  lines(xvec,S, col ="blue", lty =1.5)
@@
     C[1,1] <- -pd(1)
-    A <- B + C # Working backwards recursively 
+    A <- B  # Working backwards recursively 
     B <- solve(Diag)%*%A 
@@
 
-  B # Output of bond prices at time 0 for varying rates
-
+  #B # Output of bond prices at time 0 for varying rates
+  index = match(as.character(r),xvec)
+  B[index]
 }
@@
 
-xvec <- seq(-0.4,0.6,0.005)
-R <- implicit(T=5,J= xvec, I = 1:1250)
-S <- NULL
-for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-  }
-plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
-lines(xvec,S, col ="blue", lty =1.5)
+# xvec <- seq(-0.4,0.6,0.005)
+# R <- implicit(T=5,J= xvec, I = 1:1250)
+# S <- NULL
+# for (r in 1:length(xvec)){
+#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
+#   }
+# plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
+# lines(xvec,S, col ="blue", lty =1.5)
 
@@
 
-  Bond_values
+  #Bond_values
 
+  index = match(as.character(r),xvec)
+  Bond_values[index]
 }
@@
 
-xvec <- seq(-0.4,0.8,0.005)
-S <- NULL
-for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-}
-plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
-lines(xvec,S, col ="blue", lty =1.5)
+# xvec <- seq(-0.4,0.8,0.005)
+# S <- NULL
+# for (r in 1:length(xvec)){
+#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
+# }
+# plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
+# lines(xvec,S, col ="blue", lty =1.5)
 ```

### 2018-07-27 ZCB Pricing .Rmd
ffff

--- 2018-07-25 ZCB Pricing .Rmd
@@
 
+Crude_Monte_Carlo()
+bond_price()
 ```
@@
 
-Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
+Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08,n=1000,s=100){
   Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
@@
 
+V=seq(0.01,0.05,0.01)
+J=NULL
+K=NULL
+for ( i in 1:length(V)){
+  J[i]=Control_Variates_estimate(r0=V[i])
+  K[i]=bond_price(r=V[i])
+}
+P=(J-K)^2
+P
+```
+
+```{r}
+# Comparisons of different methods
+#################################################################################
+# Stability of results
+#################################################################################
+
+# We do this by checking the variance amongst the results when simulated many times.
+
+r_vec=seq(-0.4,0.5,0.005)
+CR=NULL
+N=NULL
+for (i in 1:length(r_vec)){
+  CR[i]=Crude_Monte_Carlo(r0=r_vec[i])
+  if(CR[i])
+}
+
+Var=var(CR)
+Var
+CR
+Crude_Monte_Carlo(r0=-0.4)
 ```
@@
 MM <- NULL
+CO <- NULL
 
@@
 
+for (t in 1: length(xvec)){
+  CO[t] <- Control_Variates_estimate(r0 = xvec[t], T =5)
+
+}
+
 plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
@@
 lines(xvec,MM, col ="yellow", lty =1.5)
+lines(xvec,MM, col ="green", lty =1.5)
 ```

### 2018-07-28 ZCB Pricing .Rmd
Cleaned up some code. Modified the finite difference methods to produce one price. Added some more chunks

--- 2018-07-27 ZCB Pricing .Rmd
@@
 ```{r 1}
-# Closed form solution to Bond price
+# Closed form solution of the Bond price
 
 bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=5,r=0.08){
+  # alpha, beta, sigma <- Fixed Parameters
+  # T <- maturity time
+  # r <- Initial rate at time 0  
   A <- (1-exp(-beta*(T-t)))/(beta)
@@
 
-# Crude Monte Carlo
+# Crude Monte Carlo function
 
-Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
+Crude_Monte_Carlo = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){
 
@@
   # n <- Number of Simulations
-  # s <- NUmber of Sub-intervals over time
+  # s <- NUmber of Subintervals over time
 
   #Simulate interest rates
-  dt <- T/s # Length of sub-intervals
+  dt <- T/s # Length of subintervals
   sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
@@
 
-Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r = 0.08,n=1000,s=100){
-  dt <- T/s # Length of sub-intervals
+Antithetic_variates = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){
+
+  dt <- T/s # Length of subintervals
   sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
-  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
-  int=exp(-Sum.) #Exponential of the estimate
-  int.=exp(-Sum) #Exponential of the estimate under the negative rv 
-  Average=(int+int.)/2   # The average of the expressions is taken for new estimate
-  mean=mean(Average)  # The average of the expression is taken for the estimate
-  sd=sd(Average)/sqrt(n)
-  result= mean
+  Sum = colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
+  Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
+  int = exp(-Sum.) #Exponential of the estimate
+  int.= exp(-Sum) #Exponential of the estimate under the negative rv 
+  Average = (int+int.)/2   # The average of the expressions is taken for new estimate
+  mean = mean(Average)  # The average of the expression is taken for the estimate
+  sd =sd(Average)/sqrt(n)
+  result = mean
   result
@@
 ```{r 4}
-#################################################################################
+
 # Moment matching
-#################################################################################
 
-Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=100000,s=100){
+Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 200){
 
@@
   # T <- maturity time
-  # r0 <- Initial rate at time 0
+  # r <- Initial rate at time 0
   # n <- Number of Simulations
@@
   #Simulate interest rates
-  dt <- T/s # Length of sub-intervals
-  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path[1,]= r0
-  z=rnorm(n)
-  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION
+  dt <- T/s # Length of subintervals
+  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,]= r
+  z = rnorm(n)
+  z_m = z-mean(z) # MOMENT MATCHING TRANSFORMATION
 
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt)
-  int=exp(-Sum)
-  mean=mean(int)
-  sd=sd(int)/sqrt(n)
-  result=mean
+  Sum = colSums(sim_path[2:(s+1),]*dt)
+  int = exp(-Sum)
+  mean = mean(int)
+  sd = sd(int)/sqrt(n)
+  result= mean
   result
@@
 ```{r 5}
-#################################################################################
+
 # Control Variates
-#################################################################################
 
@@
 # Below is the closed form solution under the CIR model
-bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
+bond_price_CIR <- function(alpha, beta, sigma, t, T, r){
   h <- sqrt(alpha^(2)+2*sigma^(2))
@@
   B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
-  A*exp(-B*r0)
+  A*exp(-B*r)
 }
@@
 
-CIR_MC= function(alpha,beta,sigma,T,r0,n,s){
+CIR_MC= function(alpha  = 0.08, beta = 0.8, sigma = 0.005, T = 5, r = 0.08, n = 1000, s = 200){
 
-  dt <- T/s # Length of sub-intervals
-  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path[1,]= r0
+  dt <- T/s # Length of subintervals
+  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
+  sim_path[1,] = r
 
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt)
-  int=exp(-Sum)
-  mean=mean(int)
-  sd=sd(int)/sqrt(n)
-  result=c(mean,sd)
+  Sum = colSums(sim_path[2:(s+1),]*dt)
+  int = exp(-Sum)
+  mean = mean(int)
+  sd = sd(int)/sqrt(n)
+  result = mean
   result
@@
 
-Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
-  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
+Control_Variates_estimate = function(alpha = 0.08, beta = 0.8, sigma = 0.005,t = 0,T = 5,r = 0.08,n = 1000,s = 200){
+  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
 }
@@
 ```{r 6}
-
-#======================================================================================
-# Doing some plots
-
-xvec <- seq(-0.3,0.5,0.01)
-S <- NULL
-for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-}
-
-CR <- NULL
-AV <- NULL
-MM <- NULL
-
-for (k in 1: length(xvec)){
-  CR[k] <- Crude_Monte_Carlo(r0 = xvec[k], T=5)
-}
-
-for (s in 1: length(xvec)){
-  AV[s] <- Antithetic_variates(r0 = xvec[s], T =5)
-
-}
-
-for (j in 1: length(xvec)){
-  MM[j] <- Moment_Matching(r0 = xvec[j], T =5)
-
-}
-
-plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
-lines(xvec,S, col ="blue", lty =1.5)
-lines(xvec,AV, col ="black", lty =1.5)
-lines(xvec,MM, col ="yellow", lty =1.5)
-```
-
-```{r 7}
 # Explicit Method
 
-explicit = function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
+explicit = function(alpha = 0.08,beta = 0.8, sigma = 0.005,r = 0.08, I = 1:1250, J = seq(-0.4,0.6,0.005),T = 5){
 
   # I = partition of time interval
-  # J = partition of short rate interval
+  # J = partition of short rates sequence
 
-  M <- length(J)
-  N <- length(I)
+  M <- length(J) # Number of short rate grid points
+  N <- length(I) # Number of time grid poiints
 
-  dt <- T/N
-  dr <- J[2] -J[1]
+  dt <- T/N # Lenght of each time subinterval
+  dr <- J[2] -J[1] # Lenght of each time interval
+
+  # For each j in J we define the following functions at a fixed time point
 
@@
 
+  #Setting up tridiagonal matrix
+
   Diag_1 <- matrix(0,ncol = M, nrow = M)
-    # Main diagonal of matrix 1
+    # Main diagonal of matrix
 
@@
 
-  # Filling lower diagonal of matrix 1
+  # Filling lower diagonal of matrix 
   for (j in 2:M){
@@
 
-  # Filling upper diagonal of matirx 1
+  # Filling upper diagonal of matirx 
   for (j in 1:(M-1)){
@@
 
+  # Bond price values at maturity are all 1 unit   
   Bond_values <- matrix(1,nrow=M, ncol =1)
 
-  for (i in I){
+  # Working backwards in time
+  for (i in 1:(length(I)+1)){
     Bond_values <- Diag_1%*%Bond_values
@@
 
-  index = match(as.character(r),xvec)
+  # Finding index of the desired short rate
+  index = match(as.character(r),J)
+  # Output is the corresponding bond price at time 0
   Bond_values[index]
@@
 
-#============================================================================================
-#Doing some plots
-# 
-#  xvec <- seq(-0.4,0.6,0.005)
-# S <- NULL
-# for (i in 1:length(xvec)){
-#    S[i] <- bond_price(alpha = 0.08,beta =0.8,sigma =0.005,t = 0, T = 5, r = xvec[i])
-#  }
-#  
-# H <- explicit(r = 0.08, I= 1:100000, T=5,alpha = 0.08, beta =0.8, sigma= 0.005, J = xvec)
-# 
-#  
-#  plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit vs Known Solution")
-#  lines(xvec,S, col ="blue", lty =1.5)
-
 ```
 
-```{r 8}
-
+```{r 7}
 # Implicit Method
 
-implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
+implicit <- function(alpha = 0.08,beta = 0.8,sigma = 0.005,r = 0.08,I = 1:1250, J =seq(-0.4,0.6,0.005),T=5){
+
   # I = partition of time interval
@@
 
-  nr <- length(J) # number of rows based on rate grid points
-  nc <- length(I) # number of columns based on number of time grid points
+  M <- length(J) # Number of short rate grid points
+  N <- length(I) # Number of time grid poiint
 
-  dr <- J[2] - J[1] #length of each sub-interval across J
-  dt <- T/length(I) #length of each sub-interval across I
+  dr <- J[2] - J[1] # length of each sub-interval across J
+  dt <- T/N # length of each sub-interval across I
 
@@
   pd <- function(j){
-    dt*((alpha-beta*J[j+1])/(2*dr) - (sigma^2)/(2*dr^2))
+    dt*((alpha-beta*J[j])/(2*dr) - (sigma^2)/(2*dr^2))
 
@@
   pm <- function(j){
-    dt*(J[j+1] + 1/dt +sigma^2/(dr^2))
+    dt*(J[j] + 1/dt +sigma^2/(dr^2))
   }
@@
   pu <- function(j){
-    -dt*((alpha-beta*J[j+1])/(2*dr) + (sigma^2)/(2*dr^2))
-
+    -dt*((alpha-beta*J[j])/(2*dr) + (sigma^2)/(2*dr^2))
   }
@@
   # Setting up tridiagonal matrix
-  Diag <- matrix(0,nrow = nr-1,ncol = nr-1)
+  Diag <- matrix(0,nrow = M,ncol = M)
 
   # Filling main diagonal
-  for (j in 1:(nr-1)){
+  for (j in 1:M){
     Diag[j,j] <- pm(j)
@@
   # Filling lower diagonal
-  for (j in 2:(nr-1)){
+  for (j in 2:M){
     Diag[j,j-1] <- pd(j)
@@
   # Filling upper diagonal
-  for (j in 1:(nr-2)){
+  for (j in 1:(M-1)){
     Diag[j,j+1] <- pu(j)
@@
 
-  B <- matrix(1,ncol = 1,nrow = nr-1) # The matrix of bond prices at maturity time
+  Bond_values <- matrix(1,ncol = 1,nrow = M) # The matrix of bond prices at maturity time 
+  Inv <- solve(Diag) # Inverse of tridiagonal matrix
 
-  for (i in I){
-    C <- matrix(0,ncol = 1, nrow = nr-1) # Another matrix for boundary conditions
-    C[nr-1,1] <- (-pu(nr-1))*B[nr-1,1]
+  for (i in 1:(length(I) +1)){
+    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
+    C[M,1] <- (-pu(M))*Bond_values[M,1]
     C[1,1] <- -pd(1)
-    A <- B  # Working backwards recursively 
-    B <- solve(Diag)%*%A 
+
+    RHS <- Bond_values  # Working backwards recursively 
+    Bond_values <- Inv%*%RHS
   }
 
-  #B # Output of bond prices at time 0 for varying rates
-  index = match(as.character(r),xvec)
-  B[index]
+  # Finding index of the desired short rate
+  index = match(as.character(r),J)
+  # Output is the corresponding bond price at time 0
+  Bond_values[index]
 }
-
-#============================================================================================
-
-# Doing some plots
-
-# xvec <- seq(-0.4,0.6,0.005)
-# R <- implicit(T=5,J= xvec, I = 1:1250)
-# S <- NULL
-# for (r in 1:length(xvec)){
-#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-#   }
-# plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
-# lines(xvec,S, col ="blue", lty =1.5)
 
@@
 
-```{r 9}
+```{r 8}
 # Crank-Nicholson Method
 
-CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T =5 , I = 1:1250, J = seq(-0.4,0.8,0.005)){
+CN <- function(alpha = 0.08, beta = 0.8, sigma = 0.005, r = 0.08, T = 5 , I = 1:1250, J = seq(-0.4,0.6,0.005)){
+
   # I = partition of time interval
@@
 
-  M <- length(J)
-  N <- length(I)
+  M <- length(J) # Number of short rate grid points
+  N <- length(I) # Number of time grid poiints
 
-  dt <- T/N
-  dr <- J[2] -J[1]
+  dt <- T/N # Length of each time subinterval
+  dr <- J[2] -J[1] # Lenght of each rate subinterval
   #===========================================================================================
@@
     Diag_2[j,j] <- -1/dt + pm(j)
-
     }
@@
 
-  for (i in I){
+  for (i in 1:(length(I)+1)){
 
@@
 
-  #Bond_values
-
-  index = match(as.character(r),xvec)
+  # Index of rate corresponding to desired short rate
+  index = match(as.character(r), J)
+  # Output corresponding to desired short rate
   Bond_values[index]
@@
 
-#============================================================================================
-# Doing some plots
-
-# xvec <- seq(-0.4,0.8,0.005)
-# S <- NULL
-# for (r in 1:length(xvec)){
-#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-# }
-# plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
-# lines(xvec,S, col ="blue", lty =1.5)
 ```
 
-```{r 11}
+```{r 9}
+# Modified Fully Implicit Method
 
@@
 
-```{r 12, echo = FALSE}
-# Comparison of results
-# Varying short rates
+```{r 10}
+# Plots of the different methods
+par(mfrow = c(2,2))
 
-compare_mat <- matrix(NA,nrow = 10, ncol = 10) # matrix of comparison
+xvec <- seq(-0.4,0.6,0.005) # Vector for rates
 
-colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations", "Moment Matching", "System Time")
+known_sol <- NULL # Vector to hold the known closed form solution
+for (r in 1:length(xvec)){
+  known_sol[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
+}
 
-for (j in 1:10){
-  compare_mat[j,1] <- 0.08
-  compare_mat[j,2] <- 0.8
-  compare_mat[j,3] <- 0.005
-  compare_mat[j,4] <- 0.01 +0.01*(j-1)
-  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
+CR <- NULL # Vector to hold Crude Monte Carlo Solutions
+AV <- NULL # Vector to hold Antithetic Monte Carlo Solutions
+MM <- NULL # Vector to hold Moment Matching  Carlo Solutions
+CV <- NULL # Vector to hold Control Variates Monte Carlo Solutions
+
+Expl <- NULL # Vector to hold Explicit method Solutions
+Impl <- NULL # Vector to hold Implicit method Solutions
+Crank <- NULL # Vector to hold Crank-Nicolson Solutions
+
+# Plots of Monte Carlo Methods ----------------------------------------------------------------------
+
+for (i in 1: length(xvec)){
+  CR[i] <- Crude_Monte_Carlo(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  AV[i] <- Antithetic_variates(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  MM[i] <- Moment_Matching(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  CV[i] <- Control_Variates_estimate(r = xvec[i])
+}
+
+plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo Solutions vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+lines(xvec, AV, col ="black", lty =1.5)
+lines(xvec, MM, col ="yellow", lty =1.5)
+lines(xvec, CV, col ="green", lty =1.5)
+
+# Plots of Finite Difference Methods ----------------------------------------------------------------------
+
+for (i in 1: length(xvec)){
+  Expl[i] <- explicit(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  Impl[i] <- implicit(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  Crank[i] <- CN(r = xvec[i])
+}
+
+plot(Expl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+
+plot(Impl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+
+plot(Crank, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank-Nicolson Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+
+```
+
+```{r 11, echo = FALSE}
+# Comparison of results for numerical methods
+
+compare_mat <- matrix(NA,nrow = 7, ncol = 4) # matrix of comparison
+
+colnames(compare_mat) <- c("Price", "Known Price", "Error", "System Time")
+rownames(compare_mat) <- c("Crude Monte Carlo", "Antithetic Variates", "Moment Matching", "Control Variates", "Explicit Method", "Implicit Method", "Crank-Nicolson Method")
+
+compare_mat[,2] <- bond_price()
+
+# Crude Monte Carlo
 start_time <- proc.time()[1]
-  compare_mat[j,6] <- Crude_Monte_Carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
-  compare_mat[j,7] <- proc.time()[1] -start_time
-  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
+compare_mat[1,1] <- Crude_Monte_Carlo()
+compare_mat[1,4] <- proc.time()[1] - start_time
+compare_mat[1,3] <- compare_mat[1,2] - compare_mat[1,1]
+
+# Antithetic Variates
 start_time <- proc.time()[1]
-  compare_mat[j,9] <- Moment_Matching(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
-  compare_mat[j,10] <- proc.time()[1] - start_time
+compare_mat[2,1] <- Antithetic_variates()
+compare_mat[2,4] <- proc.time()[1] - start_time
+compare_mat[2,3] <- compare_mat[2,2] - compare_mat[2,1]
 
-}
+# Moment Matching
+start_time <- proc.time()[1]
+compare_mat[3,1] <- Moment_Matching()
+compare_mat[3,4] <- proc.time()[1] - start_time
+compare_mat[3,3] <- compare_mat[3,2] - compare_mat[3,1]
+
+# Control Variates
+start_time <- proc.time()[1]
+compare_mat[4,1] <- Control_Variates_estimate()
+compare_mat[4,4] <- proc.time()[1] - start_time
+compare_mat[4,3] <- compare_mat[4,2] - compare_mat[4,1]
+
+# Explicit method
+start_time <- proc.time()[1]
+compare_mat[5,1] <- explicit()
+compare_mat[5,4] <- proc.time()[1] - start_time
+compare_mat[5,3] <- compare_mat[5,2] - compare_mat[5,1]
+
+# Implicit method
+start_time <- proc.time()[1]
+compare_mat[6,1] <- implicit()
+compare_mat[6,4] <- proc.time()[1] - start_time
+compare_mat[6,3] <- compare_mat[6,2] - compare_mat[6,1]
+
+# Crank-Nicolson method
+start_time <- proc.time()[1]
+compare_mat[7,1] <- CN()
+compare_mat[7,4] <- proc.time()[1] - start_time
+compare_mat[7,3] <- compare_mat[7,2] - compare_mat[7,1]
 
@@
 ```
+
+```{r 12}
+# Sensitivity Tests
+
+```

### 2018-07-28 ZCB Pricing .Rmd
ff

--- 2018-07-27 ZCB Pricing .Rmd
@@
   z=rnorm(n)
-  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION
+  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] # Simulate rates using the transformed rv 
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
-  # Monte Carlo Simulations
   Sum=colSums(sim_path[2:(s+1),]*dt)
@@
 # Below is the closed form solution under the CIR model
-bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
+bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08){
   h <- sqrt(alpha^(2)+2*sigma^(2))
@@
 
-CIR_MC= function(alpha,beta,sigma,T,r0,n,s){
+CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
 
@@
 }
-
+bond_price_CIR()
+CIR_MC()
 # Therefore the control variates estimate:
@@
 
-r_vec=seq(-0.4,0.5,0.005)
-CR=NULL
-N=NULL
-for (i in 1:length(r_vec)){
-  CR[i]=Crude_Monte_Carlo(r0=r_vec[i])
-  if(CR[i])
-}
-
-Var=var(CR)
-Var
-CR
-Crude_Monte_Carlo(r0=-0.4)
 ```

### 2018-07-29 ZCB Pricing .Rmd
sensitivity test part 1

--- 2018-07-28 ZCB Pricing .Rmd
@@
 
+senses <- matrix(nrow=10, ncol=9) # matrix to hold prices for various parameters
+colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
+
+#Initial Parameters
+senses[1,2]=bond_price()
+senses[1,3]=Crude_Monte_Carlo()
+senses[1,4]=Antithetic_variates()
+senses[1,5]=Moment_Matching()
+senses[1,6]=Control_Variates_estimate()
+senses[1,7]=explicit()
+senses[1,8]=implicit()
+senses[1,9]=CN()
+
+#r=0.1
+senses[2,2]=bond_price(r=0.1)
+senses[2,3]=Crude_Monte_Carlo(r=0.1)
+senses[2,4]=Antithetic_variates(r=0.1)
+senses[2,5]=Moment_Matching(r=0.1)
+senses[2,6]=Control_Variates_estimate(r=0.1)
+senses[2,7]=explicit(r=0.1)
+senses[2,8]=implicit(r=0.1)
+senses[2,9]=CN(r=0.1)
 ```

### 2018-07-31 ZCB Pricing .Rmd

--- 2018-07-28 ZCB Pricing .Rmd
@@
 
+senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
+colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
+
+#Initial Parameters
+senses[1,2]=bond_price()
+senses[1,3]=Crude_Monte_Carlo()
+senses[1,4]=Antithetic_variates()
+senses[1,5]=Moment_Matching()
+senses[1,6]=Control_Variates_estimate()
+senses[1,7]=explicit()
+senses[1,8]=implicit()
+senses[1,9]=CN()
+
+#r=0.05
+senses[2,2]=bond_price(r=0.05)
+senses[2,3]=Crude_Monte_Carlo(r=0.05)
+senses[2,4]=Antithetic_variates(r=0.05)
+senses[2,5]=Moment_Matching(r=0.05)
+senses[2,6]=Control_Variates_estimate(r=0.05)
+senses[2,7]=explicit(r=0.05)
+senses[2,8]=implicit(r=0.05)
+senses[2,9]=CN(r=0.05)
+
+#r=0.1
+senses[3,2]=bond_price(r=0.1)
+senses[3,3]=Crude_Monte_Carlo(r=0.1)
+senses[3,4]=Antithetic_variates(r=0.1)
+senses[3,5]=Moment_Matching(r=0.1)
+senses[3,6]=Control_Variates_estimate(r=0.1)
+senses[3,7]=explicit(r=0.1)
+senses[3,8]=implicit(r=0.1)
+senses[3,9]=CN(r=0.1)
+
+#T=1
+senses[4,2]=bond_price(T=1)
+senses[4,3]=Crude_Monte_Carlo(T=1)
+senses[4,4]=Antithetic_variates(T=1)
+senses[4,5]=Moment_Matching(T=1)
+senses[4,6]=Control_Variates_estimate(T=1)
+senses[4,7]=explicit(T=1)
+senses[4,8]=implicit(T=1)
+senses[4,9]=CN(T=1)
+
+#T=10
+senses[5,2]=bond_price(T=10)
+senses[5,3]=Crude_Monte_Carlo(T=10)
+senses[5,4]=Antithetic_variates(T=10)
+senses[5,5]=Moment_Matching(T=10)
+senses[5,6]=Control_Variates_estimate(T=10)
+senses[5,7]=explicit(T=10)
+senses[5,8]=implicit(T=10)
+senses[5,9]=CN(T=10)
+
+#sigma=0.001
+senses[6,2]=bond_price(sigma=0.001)
+senses[6,3]=Crude_Monte_Carlo(sigma=0.001)
+senses[6,4]=Antithetic_variates(sigma=0.001)
+senses[6,5]=Moment_Matching(sigma=0.001)
+senses[6,6]=Control_Variates_estimate(sigma=0.001)
+senses[6,7]=explicit(sigma=0.001)
+senses[6,8]=implicit(sigma=0.001)
+senses[6,9]=CN(sigma=0.001)
+
+#sigma=0.01
+senses[7,2]=bond_price(sigma=0.01)
+senses[7,3]=Crude_Monte_Carlo(sigma=0.01)
+senses[7,4]=Antithetic_variates(sigma=0.01)
+senses[7,5]=Moment_Matching(sigma=0.01)
+senses[7,6]=Control_Variates_estimate(sigma=0.01)
+senses[7,7]=explicit(sigma=0.01)
+senses[7,8]=implicit(sigma=0.01)
+senses[7,9]=CN(sigma=0.01)
+
+#alpha=0.01
+senses[8,2]=bond_price(alpha=0.01)
+senses[8,3]=Crude_Monte_Carlo(alpha=0.01)
+senses[8,4]=Antithetic_variates(alpha=0.01)
+senses[8,5]=Moment_Matching(alpha=0.01)
+senses[8,6]=Control_Variates_estimate(alpha=0.01)
+senses[8,7]=explicit(alpha=0.01)
+senses[8,8]=implicit(alpha=0.01)
+senses[8,9]=CN(alpha=0.01)
+
+#alpha=0.016
+senses[9,2]=bond_price(alpha=0.016)
+senses[9,3]=Crude_Monte_Carlo(alpha=0.016)
+senses[9,4]=Antithetic_variates(alpha=0.016)
+senses[9,5]=Moment_Matching(alpha=0.016)
+senses[9,6]=Control_Variates_estimate(alpha=0.016)
+senses[9,7]=explicit(alpha=0.016)
+senses[9,8]=implicit(alpha=0.016)
+senses[9,9]=CN(alpha=0.016)
+
+#beta=0.1
+senses[10,2]=bond_price(beta=0.1)
+senses[10,3]=Crude_Monte_Carlo(beta=0.1)
+senses[10,4]=Antithetic_variates(beta=0.1)
+senses[10,5]=Moment_Matching(beta=0.1)
+senses[10,6]=Control_Variates_estimate(beta=0.1)
+senses[10,7]=explicit(beta=0.1)
+senses[10,8]=implicit(beta=0.1)
+senses[10,9]=CN(beta=0.1)
+
+#beta=0.16
+senses[11,2]=bond_price(beta=0.16)
+senses[11,3]=Crude_Monte_Carlo(beta=0.16)
+senses[11,4]=Antithetic_variates(beta=0.16)
+senses[11,5]=Moment_Matching(beta=0.16)
+senses[11,6]=Control_Variates_estimate(beta=0.16)
+senses[11,7]=explicit(beta=0.16)
+senses[11,8]=implicit(beta=0.16)
+senses[11,9]=CN(beta=0.16)
+
+#alpha=0.01,beta=0.1
+senses[12,2]=bond_price(alpha=0.01,beta=0.1)
+senses[12,3]=Crude_Monte_Carlo(alpha=0.01,beta=0.1)
+senses[12,4]=Antithetic_variates(alpha=0.01,beta=0.1)
+senses[12,5]=Moment_Matching(alpha=0.01,beta=0.1)
+senses[12,6]=Control_Variates_estimate(alpha=0.01,beta=0.1)
+senses[12,7]=explicit(alpha=0.01,beta=0.1)
+senses[12,8]=implicit(alpha=0.01,beta=0.1)
+senses[12,9]=CN(alpha=0.01,beta=0.1)
+
+#alpha=0.016,beta=0.16
+senses[13,2]=bond_price(alpha=0.016,beta=0.16)
+senses[13,3]=Crude_Monte_Carlo(alpha=0.016,beta=0.16)
+senses[13,4]=Antithetic_variates(alpha=0.016,beta=0.16)
+senses[13,5]=Moment_Matching(alpha=0.016,beta=0.16)
+senses[13,6]=Control_Variates_estimate(alpha=0.016,beta=0.16)
+senses[13,7]=explicit(alpha=0.016,beta=0.16)
+senses[13,8]=implicit(alpha=0.016,beta=0.16)
+senses[13,9]=CN(alpha=0.016,beta=0.16)
+
+par(mfrow = c(2,2))
+plot(1:8,senses[1,2:9])
+lines(1:8,senses[2, 2:9], col="red", type="l")
+
 ```
+
+```{r}
+#Stability
+stables <- matrix(nrow=4, ncol=100) # matrix to hold prices for various parameters
+
+for (i in 1:100){
+  stables[1,i] <- Crude_Monte_Carlo()
+  stables[2,i] <- Antithetic_variates()
+}
+
+for (i in 1:100){
+  stables[3,i] <- Moment_Matching()
+  stables[4,i] <- Control_Variates_estimate()
+}
+
+plot(1:100, stables[1,], type="l", col="blue")
+lines(x=1:100, y=stables[2,], col="red")
+
+```

### 2018-07-31 ZCB Pricing .Rmd
d

--- 2018-07-28 ZCB Pricing .Rmd
@@
 
-Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r = 0.08,n=1000,s=100){
+Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){
   dt <- T/s # Length of sub-intervals
@@
 
-Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=100000,s=100){
+Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r0 = 0.08,n=100000,s=100){
 
@@
 # Below is the closed form solution under the CIR model
-bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08){
+bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
   h <- sqrt(alpha^(2)+2*sigma^(2))
@@
 
-CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
+CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){
 
@@
   sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path[1,]= r0
+  sim_path[1,]= r
 
@@
   sd=sd(int)/sqrt(n)
-  result=c(mean,sd)
+  result=mean
   result
@@
 
-Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08,n=1000,s=100){
-  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
+Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
+  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
 }
 
-V=seq(0.01,0.05,0.01)
-J=NULL
-K=NULL
-for ( i in 1:length(V)){
-  J[i]=Control_Variates_estimate(r0=V[i])
-  K[i]=bond_price(r=V[i])
-}
-P=(J-K)^2
-P
 ```

### 2018-08-01 ZCB Pricing .Rmd
Changed the MCs

@@
   mean = mean(int) # Find the average of expression
-  sd = sd(int)/sqrt(n)
-  result = mean
-  result
+  mean
+
 }
@@
 
-Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){
+Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
   dt <- T/s # Length of sub-intervals
@@
   z = rnorm(n) # Generate standard normal values
-  z. = -z # Estimate negative value
+  z. = -z # Negative RV
 
@@
   int.=exp(-Sum) #Exponential of the estimate under the negative rv 
-  Average=(int+int.)/2   # The average of the expressions is taken for new estimate
-  mean=mean(Average)  # The average of the expression is taken for the estimate
-  sd=sd(Average)/sqrt(n)
-  result= mean
+  mean_1=mean(int) # Estimate using Z_i
+  mean_2=mean(int.)  # Estimate using -Z_i
+  result= (mean_1+mean_2)/2 # Final estimate
   result
@@
 
-Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r0 = 0.08,n=100000,s=100){
+Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r0 = 0.08,n=1000,s=100){
 
@@
   int=exp(-Sum)
-  mean=mean(int)
-  sd=sd(int)/sqrt(n)
-  result=mean
+  result=mean(int)
   result
+
+}
+
+A=NULL
+B=NULL
+C=NULL
+
+for( i in 1:100){
+  A[i]=Crude_Monte_Carlo()
+  B[i]=Antithetic_variates()
+  C[i]=Moment_Matching()
 }
@@
 
-CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=100000,s=200){
+CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
 
@@
   int=exp(-Sum)
-  mean=mean(int)
-  sd=sd(int)/sqrt(n)
-  result=mean
+  result=mean(int)
   result
@@
 }
-bond_price_CIR()
-CIR_MC()
 # Therefore the control variates estimate:
@@
   Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
+}
+
+A=NULL
+B=NULL
+C=NULL
+D=NULL
+
+for (i in 1:100){
+  A[i]=Crude_Monte_Carlo()
+  B[i]=Antithetic_variates()
+  C[i]=Moment_Matching()
+  D[i]=Control_Variates_estimate()
 }
@@
 ```
+
+```{r}
+# Sensitivity Tests
+
+senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
+colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
+
+#Initial Parameters
+senses[1,2]=bond_price()
+senses[1,3]=Crude_Monte_Carlo()
+senses[1,4]=Antithetic_variates()
+senses[1,5]=Moment_Matching()
+senses[1,6]=Control_Variates_estimate()
+senses[1,7]=explicit()
+senses[1,8]=implicit()
+senses[1,9]=CN()
+
+#r=0.05
+senses[2,2]=bond_price(r=0.05)
+senses[2,3]=Crude_Monte_Carlo(r=0.05)
+senses[2,4]=Antithetic_variates(r=0.05)
+senses[2,5]=Moment_Matching(r=0.05)
+senses[2,6]=Control_Variates_estimate(r=0.05)
+senses[2,7]=explicit(r=0.05)
+senses[2,8]=implicit(r=0.05)
+senses[2,9]=CN(r=0.05)
+
+#r=0.1
+senses[3,2]=bond_price(r=0.1)
+senses[3,3]=Crude_Monte_Carlo(r=0.1)
+senses[3,4]=Antithetic_variates(r=0.1)
+senses[3,5]=Moment_Matching(r=0.1)
+senses[3,6]=Control_Variates_estimate(r=0.1)
+senses[3,7]=explicit(r=0.1)
+senses[3,8]=implicit(r=0.1)
+senses[3,9]=CN(r=0.1)
+
+#T=1
+senses[4,2]=bond_price(T=1)
+senses[4,3]=Crude_Monte_Carlo(T=1)
+senses[4,4]=Antithetic_variates(T=1)
+senses[4,5]=Moment_Matching(T=1)
+senses[4,6]=Control_Variates_estimate(T=1)
+senses[4,7]=explicit(T=1)
+senses[4,8]=implicit(T=1)
+senses[4,9]=CN(T=1)
+
+#T=10
+senses[5,2]=bond_price(T=10)
+senses[5,3]=Crude_Monte_Carlo(T=10)
+senses[5,4]=Antithetic_variates(T=10)
+senses[5,5]=Moment_Matching(T=10)
+senses[5,6]=Control_Variates_estimate(T=10)
+senses[5,7]=explicit(T=10)
+senses[5,8]=implicit(T=10)
+senses[5,9]=CN(T=10)
+
+#sigma=0.001
+senses[6,2]=bond_price(sigma=0.001)
+senses[6,3]=Crude_Monte_Carlo(sigma=0.001)
+senses[6,4]=Antithetic_variates(sigma=0.001)
+senses[6,5]=Moment_Matching(sigma=0.001)
+senses[6,6]=Control_Variates_estimate(sigma=0.001)
+senses[6,7]=explicit(sigma=0.001)
+senses[6,8]=implicit(sigma=0.001)
+senses[6,9]=CN(sigma=0.001)
+
+#sigma=0.01
+senses[7,2]=bond_price(sigma=0.01)
+senses[7,3]=Crude_Monte_Carlo(sigma=0.01)
+senses[7,4]=Antithetic_variates(sigma=0.01)
+senses[7,5]=Moment_Matching(sigma=0.01)
+senses[7,6]=Control_Variates_estimate(sigma=0.01)
+senses[7,7]=explicit(sigma=0.01)
+senses[7,8]=implicit(sigma=0.01)
+senses[7,9]=CN(sigma=0.01)
+
+#alpha=0.01
+senses[8,2]=bond_price(alpha=0.01)
+senses[8,3]=Crude_Monte_Carlo(alpha=0.01)
+senses[8,4]=Antithetic_variates(alpha=0.01)
+senses[8,5]=Moment_Matching(alpha=0.01)
+senses[8,6]=Control_Variates_estimate(alpha=0.01)
+senses[8,7]=explicit(alpha=0.01)
+senses[8,8]=implicit(alpha=0.01)
+senses[8,9]=CN(alpha=0.01)
+
+#alpha=0.016
+senses[9,2]=bond_price(alpha=0.016)
+senses[9,3]=Crude_Monte_Carlo(alpha=0.016)
+senses[9,4]=Antithetic_variates(alpha=0.016)
+senses[9,5]=Moment_Matching(alpha=0.016)
+senses[9,6]=Control_Variates_estimate(alpha=0.016)
+senses[9,7]=explicit(alpha=0.016)
+senses[9,8]=implicit(alpha=0.016)
+senses[9,9]=CN(alpha=0.016)
+
+#beta=0.1
+senses[10,2]=bond_price(beta=0.1)
+senses[10,3]=Crude_Monte_Carlo(beta=0.1)
+senses[10,4]=Antithetic_variates(beta=0.1)
+senses[10,5]=Moment_Matching(beta=0.1)
+senses[10,6]=Control_Variates_estimate(beta=0.1)
+senses[10,7]=explicit(beta=0.1)
+senses[10,8]=implicit(beta=0.1)
+senses[10,9]=CN(beta=0.1)
+
+#beta=0.16
+senses[11,2]=bond_price(beta=0.16)
+senses[11,3]=Crude_Monte_Carlo(beta=0.16)
+senses[11,4]=Antithetic_variates(beta=0.16)
+senses[11,5]=Moment_Matching(beta=0.16)
+senses[11,6]=Control_Variates_estimate(beta=0.16)
+senses[11,7]=explicit(beta=0.16)
+senses[11,8]=implicit(beta=0.16)
+senses[11,9]=CN(beta=0.16)
+
+#alpha=0.01,beta=0.1
+senses[12,2]=bond_price(alpha=0.01,beta=0.1)
+senses[12,3]=Crude_Monte_Carlo(alpha=0.01,beta=0.1)
+senses[12,4]=Antithetic_variates(alpha=0.01,beta=0.1)
+senses[12,5]=Moment_Matching(alpha=0.01,beta=0.1)
+senses[12,6]=Control_Variates_estimate(alpha=0.01,beta=0.1)
+senses[12,7]=explicit(alpha=0.01,beta=0.1)
+senses[12,8]=implicit(alpha=0.01,beta=0.1)
+senses[12,9]=CN(alpha=0.01,beta=0.1)
+
+#alpha=0.016,beta=0.16
+senses[13,2]=bond_price(alpha=0.016,beta=0.16)
+senses[13,3]=Crude_Monte_Carlo(alpha=0.016,beta=0.16)
+senses[13,4]=Antithetic_variates(alpha=0.016,beta=0.16)
+senses[13,5]=Moment_Matching(alpha=0.016,beta=0.16)
+senses[13,6]=Control_Variates_estimate(alpha=0.016,beta=0.16)
+senses[13,7]=explicit(alpha=0.016,beta=0.16)
+senses[13,8]=implicit(alpha=0.016,beta=0.16)
+senses[13,9]=CN(alpha=0.016,beta=0.16)
+
+par(mfrow = c(2,2))
+plot(1:8,senses[1,2:9])
+lines(1:8,senses[2, 2:9], col="red", type="l")
+
+```
+
+```{r}
+#Stability
+stables <- matrix(nrow=4, ncol=100) # matrix to hold prices for various parameters
+
+for (i in 1:100){
+  stables[1,i] <- Crude_Monte_Carlo()
+  stables[2,i] <- Antithetic_variates()
+}
+
+for (i in 1:100){
+  stables[3,i] <- Moment_Matching()
+  stables[4,i] <- Control_Variates_estimate()
+}
+
+plot(1:100, stables[1,], type="l", col="blue")
+lines(x=1:100, y=stables[2,], col="red")
+
+```

### 2018-08-01 ZCB Pricing .Rmd
Stability changes

@@
 
-A=NULL
-B=NULL
-C=NULL
-
-for( i in 1:100){
-  A[i]=Crude_Monte_Carlo()
-  B[i]=Antithetic_variates()
-  C[i]=Moment_Matching()
-}
-
 ```
@@
 bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
-  h <- sqrt(alpha^(2)+2*sigma^(2))
-  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
-  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
+  h <- sqrt(beta^(2)+2*sigma^(2))
+  A <-(2*h*exp((beta+h)*(T-t)/2)/(2*h+(beta+h)*(exp((T-t)*(h))-1)))^((2*alpha)/sigma^(2))
+  B <-2*(exp((T-t)*(h))-1)/(2*h+(beta+h)*(exp((T-t)*(h))-1))
   A*exp(-B*r)
@@
     for (j in 2:(s+1)){
-      dr=alpha*(beta-sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
-A=NULL
-B=NULL
-C=NULL
-D=NULL
-
-for (i in 1:100){
-  A[i]=Crude_Monte_Carlo()
-  B[i]=Antithetic_variates()
-  C[i]=Moment_Matching()
-  D[i]=Control_Variates_estimate()
-}
-
+bond_price()
+Control_Variates_estimate()
 ```
@@
 # We do this by checking the variance amongst the results when simulated many times.
+
+CR=NULL
+AN=NULL
+MM=NULL
+CV=NULL
+
+for ( i in 1:100){
+  CR[i]=Crude_Monte_Carlo()
+  #AN[i]=Antithetic_variates()
+  #MM[i]=Moment_Matching()
+  CV[i]=Control_Variates_estimate()
+}
 

### 2018-08-01 Draft.tex
Add files via upload

\documentclass[12pt,a4paper]{article}
\usepackage{natbib}
\usepackage{url}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{array}
%\usepackage{appendix}
\usepackage[british]{babel}
\bibpunct[:]{(}{)}{;}{a}{,}{,}

%\newcommand{\dd}[1]{\mathrm{d}#1}
\renewcommand{\baselinestretch}{1.5}

\newcommand{\bi}{\begin{itemize}}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
	\newcommand{\ee}{\end{enumerate}}

\begin{document}

	\begin{titlepage}

		\begin{center}
			\textbf{{\Large Draft Paper}}\\
			\vspace{1cm}
			{\Large Pricing a zero coupon bond by Monte Carlo and Finite Difference Methods when the term structure of interest rates is a mean reverting Ornstein-Uhlenbeck process}\\
			\vspace{1cm}
			\today\\
			Valentine Chisango (CHSVAL002)\\
			{\tt vmchisango@gmail.com}\\

			George Parekkadavil (PRKMAT004)\\
			{\tt gparekkadavil@gmail.com}\\

			Vegan Pather (PTHVEG001)\\
			\tt {veganpather@gmail.com}

		\end{center}

	\begin{abstract}
		Something interesting in this section
	\end{abstract}

	\end{titlepage}
	\pagenumbering{arabic}
	\newpage

	\section{Introduction}
	\label{sec: Intro}

	\newpage
	\section{Background}
	\label{sec: Backgrd}

	\newpage
	\section{Methodology}
	\label{sec: Method}

	\newpage
	\section{Results}
	\label{sec: Results}

	\subsection{Comparision of Numerical Methods}
	\label{subsec: Compar}
	The methodology was implemented in R under an arbitrary set of parameters, where $\alpha = 0.08$, $\beta = 0.8$ and $\sigma=0.005$. This implied a mean rate of 0.10 under the short rate model and an initial rate of 0.08 was selected. These are annually effective and the time to maturity is 5 years. The Monte Carlo methods were all implemented under 1000 trials and with a partition of 200 subintervals over the time range. The partition of time for the finite difference methods was composed of 1250 equally-spaced subintervals, which is consistent with 250 trading days per year. The discrete set of short rates ranged from -0.4 to 0.6 with a step of 0.005. Table 1 provides the corresponding bond prices for each method under these parameters along with the differences between these prices and the known solution. The approximate time to run each method is provided in seconds.

\begin{table}[ht]
	\centering
	\caption{Comparision of Bond Prices for Numerical Methods}

	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|}
		\hline
		Numerical Method & Price & Known Price & Error & Computation Time \\ 
		\hline
		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 \\ 
		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 \\ 
		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 \\ 
		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 \\ 
		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 \\ 
		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 \\ 
		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 \\ 
		\hline
	\end{tabular}
\end{table}
	\newpage
	\section{Discussion}
	\label{sec: Discuss}

	\newpage
	\section{Conclusions}
	\label{sec : Concl}

	\newpage
	\bibliographystyle{natbib}
	\bibliography{myref}

	\newpage
	\appendix
	\section{Appendix A}
	\label{sec: Appendix A}
	\subsection{Details of the Model}
	\label{subsec: Details}
	The formulation consists of a zero-coupon bond issued at some time $t \geq 0$ where a corresponding payment of 1 unit will be made at the maturity time $T \geq t$. The risk of default is negligible \citep{shreve2004stochastic}. The bond is priced by using the short rate process $\{r_{s}:t \leq s \leq T\}$.

	For the time interval $[t,T]$ the filtered probability space $(\Omega, \mathcal{F}^W,\mathbb{F}^W,\mathbb{P})$ is used and $r_t$ is known \citep{mamon2004three}. A risk neutral measure $\mathbb{Q}$ is defined and it is equivalent to $\mathbb{P}$ \citep{shreve2004stochastic}. The short rate process, which is an Ornstein-Uhlenbeck process, then satisfies the following stochastic differential equation: 
	\begin{equation}
	dr_{t} = (\alpha-\beta r_{t})dt + \sigma dW_{t} \quad \alpha, \beta \in \mathbb{R}, \sigma>0, \beta \neq 0
	\end{equation}

	The bond price $B(t,T,r_t)$ with boundary condition of $B(T,T,r_t) = 1$, is then determined through computing the following risk-neutral expectation:
	\begin{equation}
	B(t,T,r_t) = \mathbb{E}^{\mathbb{Q}}\left[exp\left(-\int_{t}^{T}r_{s} ds\right)\middle\vert\mathcal{F}_{t}^{W_{t}}\right]
	\end{equation}

	\subsection{The Partial Differential Equation}
	\label{subsec: PDE}
	The following expression is the PDE, derived from (2), which is required to obtain the price of a zero-coupon bond when the term structure of interest rates follows the Ornstein-Uhlenbeck process. .
	$$\boxed{-r_t B(t,T,r_t) + \frac{\partial}{\partial t} B(t,T,r_t) + \frac{\partial}{\partial r_t}B(t,T,r_t)(\alpha - \beta r_t) +\frac{1}{2} \sigma^2 \frac{\partial^2}{\partial r_t^2} B(t,T,r_t) = 0 }$$

	\noindent This PDE is accompanied by the boundary condition $B(T,T,r_t) = 1$
	\subsection{The Closed Form Solution}
	\label{subsec: Closed Form}

	A closed form solution to the above PDE exists and as per \cite{mamon2004three}, it is given by the following expression:
	\begin{gather*}
	\boxed{B(t,T,r_t) =exp(-A(t,T)r_t+D(t,T))}
	\end{gather*}
	where
	\begin{align*}
	A(t,T)&=\frac{\beta(1-e^{-\beta(T-t)})}{\alpha}\\
	D(t,T)&=\frac{1}{\beta}\left[\left(\alpha-\frac{\sigma^2}{2\beta}\right)[A(t,T)-(T-t)]-\frac{\sigma^2A(t,T)^2}{4}\right]
	\end{align*}

	\newpage
	\section{Appendix B}
	\label{sec: Appendix B}
	\subsection{Monte Carlo Simulation}
	\label{subsec: MC}
	The methodology involved in Monte-Carlo simulations are:

	\begin{itemize}
		\item Discretize the SDE using a scheme over a time period [0,T]
		\item Simulate random i.i.d standard normal variables.
		\item Simulate a path of interest rates using the discretized SDE and the i.i.d standard normal variables.
		\item Evaluate the integral $e^{-\int_{t}^{T} r(u)du}$ using one simulated path.
		\item Repeat the evaluation for more paths and take the sample mean as the final estimate of the bond price.

		The above steps are mentioned in Cairns(2004:185)
	\end{itemize}

	\subsubsection{Schurman's Method Under the Vasicek Model}
	\label{subsubsec: Schurman}

	Schurman(2009) determined the following formula as the bond price for one interest rate path with fixed parameters.

	$$f(h,n)=F\times exp[-\{\frac{1}{2}r_{0}+\sum_{j=1}^{k-1}r_{j} +\frac{1}{2}r_{k}\}h]$$

	where F is the face value of the bond, h is the time interval, n being the number of the path simulated and $r_{j}$ are the short rate values simulated. Monte Carlo simulations are then run on each path level to determine the price of along that simulated interest rate path. Once N simulations have been completed, the final price is then determined by taking the average of the prices across N simulations.

	\subsection{Finite Difference Methods}
	\label{subsec: FD}
	A space-time grid (or lattice) is defined by the independent variables of $t$ and $r_t$ \citep{crank}. The interval $[t,T]$ is partitioned into equal sub-intervals with indices of  $n=0,1,...,N$. The range of $r_t$ (which is treated as the space variable) is partitioned with indices of $i = 1,...,I$. The lenght of each $r$ sub-interval is taken as $\Delta r_t$ and the lenght of each $t$ sub-interval is taken as $\Delta t$. The function in the PDE is given by $f(t,r_t)= B(t,T,r_t)$ with boundary condition $f(T,r_t) = 1$ and $r_t$ being known. The algorithm starts at $f(T,r_t)$ works backwards until the solution is reached and this runs over the $(N+1)\times(I+1)$ grid points. At a single gridpoint $(n,i)$, the following approximations are made:
	\subsubsection{Explicit Method}
	\label{subsubsec: Explicit}
	$$\frac{\partial f}{\partial t} = \frac{f(n+1,i) - f(n,i)}{\Delta t}$$
	$$\frac{\partial f}{\partial r_i} = \frac{f(n+1,i+1) -f(n+1,i-1)}{2 \Delta r_i}$$
	$$\frac{\partial^2 f}{\partial r_i^2} = \frac{f(n+1,i+1) - 2f(n+1,i) +f(n+1,i-1)}{\Delta r_i^2}$$

	This is used in the PDE as follows
	$$-r_i f(n,i)  + \frac{\partial f}{\partial t} + \frac{\partial f}{\partial r_i}(\alpha - \beta r_i) +\frac{1}{2} \sigma^2 \frac{\partial^2 f}{\partial r_i^2}  = 0 $$

	\subsubsection{Implicit Method}
	\label{subsubsec: Implicit}
	$$\frac{\partial f}{\partial t} = \frac{f(n+1,i) - f(n,i)}{\Delta t}$$
	$$\frac{\partial f}{\partial r_i} = \frac{f(n,i+1) -f(n,i-1)}{2 \Delta r_i}$$
	$$\frac{\partial^2 f}{\partial r_i^2} = \frac{f(n,i+1) - 2f(n,i) +f(n,i-1)}{\Delta r_i^2}$$

	This is used in the PDE as follows
	$$-r_i f(n+1,i)  + \frac{\partial f}{\partial t} + \frac{\partial f}{\partial r_i}(\alpha - \beta r_i) +\frac{1}{2} \sigma^2 \frac{\partial^2 f}{\partial r_i^2}  = 0 $$
	\subsubsection{Crank-Nicolson Method}
	\label{subsubsec: Crank Method}

	$$\frac{\partial f}{\partial t} = \frac{f(n+1,i) - f(n,i)}{\Delta t}$$
	$$\frac{\partial f}{\partial r_i} = \frac{f(n,i+1) - f(n,i-1) +f(n+1,i+1) -f(n+1,i-1)}{2 \Delta r_i}$$

	\begin{gather*}
	\frac{\partial^2 f}{\partial r_i^2} = \frac{f(n,i+1) - 2f(n,i) + f(n,i-1)}{2\Delta r_i^2}
	+ \frac{f(n+1,i+1) - 2f(n+1,i) +f(n+1,i-1)}{2\Delta r_i^2}
	\end{gather*}

	This is used in the PDE as follows
	$$-\frac{1}{2}r_i f(n,i)-\frac{1}{2} r_i f(n+1,i) + \frac{\partial f}{\partial t} + \frac{\partial f}{\partial r_i}(\alpha - \beta r_i) +\frac{1}{2} \sigma^2 \frac{\partial^2 f}{\partial r_i^2}  = 0 $$

	The PDE can then be simplified further which results in solving a tridiagonal system of equations \citep{Cairns}.

\end{document}

### 2018-08-01 ZCB Pricing .Rmd
Adjustments

@@
 
-# Crude Monte Carlo
+# Crude Monte Carlo function
 
@@
 
-Crude_Monte_Carlo()
-bond_price()
 ```
@@
 Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
+
+  # alpha, beta, sigma <- Fixed Parameters
+  # T <- maturity time
+  # r <- Initial rate at time 0
+  # n <- Number of Simulations
+  # s <- NUmber of Sub-intervals over time
+
   dt <- T/s # Length of sub-intervals
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
-      dr_i= (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
-      sim_path[j,i]=sim_path[j-1,i]+dr
-      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i
+      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
+      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
+      sim_path[j,i] =s im_path[j-1,i]+dr
+      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i
 
@@
   # Monte Carlo Simulations
-  Sum=colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
-  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
-  int=exp(-Sum.) #Exponential of the estimate
-  int.=exp(-Sum) #Exponential of the estimate under the negative rv 
-  mean_1=mean(int) # Estimate using Z_i
-  mean_2=mean(int.)  # Estimate using -Z_i
-  result= (mean_1+mean_2)/2 # Final estimate
+  Sum = colSums(sim_path[2:(s+1),]*dt) # The Sum and Sum. variables record the summation of their respective rates to approximate the integral
+  Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
+  int = exp(-Sum.) #Exponential of the estimate
+  int.= exp(-Sum) #Exponential of the estimate under the negative rv 
+  mean_1 = mean(int) # Estimate using Z_i
+  mean_2 = mean(int.)  # Estimate using -Z_i
+  result = (mean_1+mean_2)/2 # Final estimate
   result
@@
 ```{r 4}
-#################################################################################
+
 # Moment matching
-#################################################################################
 
-Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r0 = 0.08,n=1000,s=100){
+Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 200){
 
@@
 
-bond_price()
-Control_Variates_estimate()
-```
-
-```{r}
-# Comparisons of different methods
-#################################################################################
-# Stability of results
-#################################################################################
-
-# We do this by checking the variance amongst the results when simulated many times.
-
-CR=NULL
-AN=NULL
-MM=NULL
-CV=NULL
-
-for ( i in 1:100){
-  CR[i]=Crude_Monte_Carlo()
-  #AN[i]=Antithetic_variates()
-  #MM[i]=Moment_Matching()
-  CV[i]=Control_Variates_estimate()
-}
-
 ```
@@
 ```{r 6}
-
-#======================================================================================
-# Doing some plots
-
-xvec <- seq(-0.3,0.5,0.01)
-S <- NULL
-for (r in 1:length(xvec)){
-  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-}
-
-CR <- NULL
-AV <- NULL
-MM <- NULL
-CO <- NULL
-
-for (k in 1: length(xvec)){
-  CR[k] <- Crude_Monte_Carlo(r0 = xvec[k], T=5)
-}
-
-for (s in 1: length(xvec)){
-  AV[s] <- Antithetic_variates(r0 = xvec[s], T =5)
-
-}
-
-for (j in 1: length(xvec)){
-  MM[j] <- Moment_Matching(r0 = xvec[j], T =5)
-
-}
-
-for (t in 1: length(xvec)){
-  CO[t] <- Control_Variates_estimate(r0 = xvec[t], T =5)
-
-}
-
-plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
-lines(xvec,S, col ="blue", lty =1.5)
-lines(xvec,AV, col ="black", lty =1.5)
-lines(xvec,MM, col ="yellow", lty =1.5)
-lines(xvec,MM, col ="green", lty =1.5)
-```
-
-```{r 7}
 # Explicit Method
 
-explicit = function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:1250, J =seq(-0.4,0.6,0.005),T=5){
+explicit = function(alpha = 0.08,beta = 0.8, sigma = 0.005,r = 0.08, I = 1:1250, J = seq(-0.4,0.6,0.005),T = 5){
 
   # I = partition of time interval
-  # J = partition of short rate interval
+  # J = partition of short rates sequence
 
-  M <- length(J)
-  N <- length(I)
+  M <- length(J) # Number of short rate grid points
+  N <- length(I) # Number of time grid poiints
 
-  dt <- T/N
-  dr <- J[2] -J[1]
+  dt <- T/N # Lenght of each time subinterval
+  dr <- J[2] -J[1] # Lenght of each time interval
+
+  # For each j in J we define the following functions at a fixed time point
 
@@
 
-#============================================================================================
-# Doing some plots
-
-# xvec <- seq(-0.4,0.8,0.005)
-# S <- NULL
-# for (r in 1:length(xvec)){
-#   S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-# }
-# plot(CN(), x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
-# lines(xvec,S, col ="blue", lty =1.5)
 ```
 
-```{r 11}
+```{r 9}
+# Plots of the different methods
+par(mfrow = c(2,2))
+
+xvec <- seq(-0.4,0.6,0.005) # Vector for rates
+
+known_sol <- NULL # Vector to hold the known closed form solution
+for (r in 1:length(xvec)){
+  known_sol[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
+}
+
+CR <- NULL # Vector to hold Crude Monte Carlo Solutions
+AV <- NULL # Vector to hold Antithetic Monte Carlo Solutions
+MM <- NULL # Vector to hold Moment Matching  Carlo Solutions
+CV <- NULL # Vector to hold Control Variates Monte Carlo Solutions
+
+Expl <- NULL # Vector to hold Explicit method Solutions
+Impl <- NULL # Vector to hold Implicit method Solutions
+Crank <- NULL # Vector to hold Crank-Nicolson Solutions
+
+# Plots of Monte Carlo Methods ----------------------------------------------------------------------
+
+for (i in 1: length(xvec)){
+  CR[i] <- Crude_Monte_Carlo(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  AV[i] <- Antithetic_variates(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  MM[i] <- Moment_Matching(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  CV[i] <- Control_Variates_estimate(r = xvec[i])
+}
+
+plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo Solutions vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+lines(xvec, AV, col ="black", lty =1.5)
+lines(xvec, MM, col ="yellow", lty =1.5)
+lines(xvec, CV, col ="green", lty =1.5)
+
+# Plots of Finite Difference Methods ----------------------------------------------------------------------
+
+for (i in 1: length(xvec)){
+  Expl[i] <- explicit(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  Impl[i] <- implicit(r = xvec[i])
+}
+
+for (i in 1: length(xvec)){
+  Crank[i] <- CN(r = xvec[i])
+}
+
+plot(Expl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+
+plot(Impl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
+
+plot(Crank, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank-Nicolson Method vs Known Solution")
+lines(xvec, known_sol, col ="blue", lty =1.5)
 
@@
 
-```{r 12, echo = FALSE}
-# Comparison of results
-# Varying short rates
+```{r 10, echo = FALSE}
+# Comparison of results for numerical methods
 
-compare_mat <- matrix(NA,nrow = 10, ncol = 10) # matrix of comparison
+compare_mat <- matrix(NA,nrow = 7, ncol = 4) # matrix of comparison
 
-colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations", "Moment Matching", "System Time")
+colnames(compare_mat) <- c("Price", "Known Price", "Error", "System Time")
+rownames(compare_mat) <- c("Crude Monte Carlo", "Antithetic Variates", "Moment Matching", "Control Variates", "Explicit Method", "Implicit Method", "Crank-Nicolson Method")
 
-for (j in 1:10){
-  compare_mat[j,1] <- 0.08
-  compare_mat[j,2] <- 0.8
-  compare_mat[j,3] <- 0.005
-  compare_mat[j,4] <- 0.01 +0.01*(j-1)
-  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
+compare_mat[,2] <- bond_price()
+
+# Crude Monte Carlo
 start_time <- proc.time()[1]
-  compare_mat[j,6] <- Crude_Monte_Carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
-  compare_mat[j,7] <- proc.time()[1] -start_time
-  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
+compare_mat[1,1] <- Crude_Monte_Carlo()
+compare_mat[1,4] <- proc.time()[1] - start_time
+compare_mat[1,3] <- compare_mat[1,2] - compare_mat[1,1]
+
+# Antithetic Variates
 start_time <- proc.time()[1]
-  compare_mat[j,9] <- Moment_Matching(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
-  compare_mat[j,10] <- proc.time()[1] - start_time
+compare_mat[2,1] <- Antithetic_variates()
+compare_mat[2,4] <- proc.time()[1] - start_time
+compare_mat[2,3] <- compare_mat[2,2] - compare_mat[2,1]
 
-}
+# Moment Matching
+start_time <- proc.time()[1]
+compare_mat[3,1] <- Moment_Matching()
+compare_mat[3,4] <- proc.time()[1] - start_time
+compare_mat[3,3] <- compare_mat[3,2] - compare_mat[3,1]
+
+# Control Variates
+start_time <- proc.time()[1]
+compare_mat[4,1] <- Control_Variates_estimate()
+compare_mat[4,4] <- proc.time()[1] - start_time
+compare_mat[4,3] <- compare_mat[4,2] - compare_mat[4,1]
+
+# Explicit method
+start_time <- proc.time()[1]
+compare_mat[5,1] <- explicit()
+compare_mat[5,4] <- proc.time()[1] - start_time
+compare_mat[5,3] <- compare_mat[5,2] - compare_mat[5,1]
+
+# Implicit method
+start_time <- proc.time()[1]
+compare_mat[6,1] <- implicit()
+compare_mat[6,4] <- proc.time()[1] - start_time
+compare_mat[6,3] <- compare_mat[6,2] - compare_mat[6,1]
+
+# Crank-Nicolson method
+start_time <- proc.time()[1]
+compare_mat[7,1] <- CN()
+compare_mat[7,4] <- proc.time()[1] - start_time
+compare_mat[7,3] <- compare_mat[7,2] - compare_mat[7,1]
 
@@
 
-```{r}
+```{r 11}
 # Sensitivity Tests
@@
 
-```{r}
+```{r 12}
 #Stability
-stables <- matrix(nrow=4, ncol=100) # matrix to hold prices for various parameters
 
-for (i in 1:100){
-  stables[1,i] <- Crude_Monte_Carlo()
-  stables[2,i] <- Antithetic_variates()
+# We do this by checking the variance amongst the results when simulated many times.
+
+CR = NULL
+AN = NULL
+MM = NULL
+CV = NULL
+
+for ( i in 1:100){
+  CR[i]=Crude_Monte_Carlo()
+  #AN[i]=Antithetic_variates()
+  #MM[i]=Moment_Matching()
+  CV[i]=Control_Variates_estimate()
 }
 
-for (i in 1:100){
-  stables[3,i] <- Moment_Matching()
-  stables[4,i] <- Control_Variates_estimate()
-}
-
-plot(1:100, stables[1,], type="l", col="blue")
-lines(x=1:100, y=stables[2,], col="red")
-
 ```

### 2018-08-02 ZCB Pricing .Rmd
Added some convergence tests

@@
       dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
-      sim_path[j,i] =s im_path[j-1,i]+dr
+      sim_path[j,i] =sim_path[j-1,i]+dr
       sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i
@@
 ```{r 12}
-#Stability
+#Stability Tests
 
@@
 ```
+
+```{r 13}
+# Convergence Tests
+# Varying time steps
+
+time_vec <- seq(0,100,1)
+
+closed <- NULL
+CN_conv <- NULL
+Impl_conv <- NULL
+Expl_conv <- NULL
+
+for (i in 1:length(time_vec)){
+  closed[i] <- bond_price()
+}
+
+for (i in 1:length(time_vec)){
+  CN_conv[i] <- CN(I = 1:time_vec[i])
+}
+
+for (i in 1:length(time_vec)){
+  Impl_conv[i] <- implicit(I = 1:time_vec[i])
+}
+
+for (i in 1:length(time_vec)){
+  Expl_conv[i] <- explicit(I = 1:time_vec[i])
+}
+
+plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
+lines(x = time_vec, y = CN_conv, type = "l", lty = 2)
+lines(x = time_vec, y = Impl_conv, type = "l", lty = 3, col = "blue")
+lines(x = time_vec, y = Expl_conv, type = "l", lty = 4, col = "red")
+legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)
+
+```

### 2018-08-02 ZCB Pricing .Rmd
small change

@@
   sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
-  sim_path[1,]= r0
+  sim_path[1,]= r
   z=rnorm(n)

### 2018-08-02 ZCB Pricing .Rmd
More convergence

@@
 
-par(mfrow = c(2,2))
-plot(1:8,senses[1,2:9])
-lines(1:8,senses[2, 2:9], col="red", type="l")
+#par(mfrow = c(2,2))
+#plot(1:8,senses[1,2:9])
+#lines(1:8,senses[2, 2:9], col="red", type="l")
 
@@
 ```{r 13}
-# Convergence Tests
+# Convergence Tests for finite difference methods
 # Varying time steps
@@
 
+par(mfrow = c(1,1))
 plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
@@
 ```
+
+```{r}
+# Covergence tests for Monte Carlo functions
+
+trials_vec <- seq(10,2000,50)
+
+closed_1 <- NULL
+CR_conv <- NULL
+AV_conv <- NULL
+MM_conv <- NULL
+CV_conv <- NULL
+
+for (i in 1:length(trials_vec)){
+  closed_1[i] <- bond_price()
+}
+
+for (i in 1:length(trials_vec)){
+  CR_conv[i] <- Crude_Monte_Carlo(n = trials_vec[i])
+}
+
+for (i in 1:length(trials_vec)){
+  AV_conv[i] <- Antithetic_variates(n = trials_vec[i])
+}
+
+for (i in 1:length(trials_vec)){
+  MM_conv[i] <- Moment_Matching(n = trials_vec[i])
+}
+
+for (i in 1:length(trials_vec)){
+  CV_conv[i] <- Control_Variates_estimate(n = trials_vec[i])
+}
+
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price")
+lines(x = trials_vec, y = CR_conv, type = "l", lty = 2)
+lines(x = trials_vec, y = AV_conv, type = "l", lty = 3, col = "blue")
+lines(x = trials_vec, y = MM_conv, type = "l", lty = 4, col = "red")
+lines(x = trials_vec, y = CV_conv, type = "l", lty = 5, col = "grey")
+
+legend(x = 1500, y = 0.618, legend = c("Closed Form", "Crude", "Antithetic Variates", "Moment Matching","Control Variates"), lty = 1:5, col = c("black","black","blue", "red","grey"), cex = 0.5)
+
+```
+
+```

### 2018-08-02 ZCB Pricing .Rmd
Convergence test for rates

@@
   Diag_1 <- matrix(0,ncol = M, nrow = M)
-    # Main diagonal of matrix
 
+  # Filling main diagonal of matrix 
   for (j in 1:M){
@@
   dr <- J[2] -J[1] # Lenght of each rate subinterval
-  #===========================================================================================
+
+  #========================================================================================
   # Define the following functions for j = 1,...,M at each time point i
@@
     -(alpha -beta*J[j])/(4*dr) - sigma^2/(4*(dr^2)) 
-
   }
 
-  #===========================================================================================
+  #========================================================================================
   # Define 2 tridiagonal matricies. One for time point i and one for time point i+1
@@
 
-  # Main diagonal of matrix 1
+  # Filling main diagonal of matrix 1
   for (j in 1:M){
     Diag_1[j,j] <- -1/dt - pm(j)
-
   }
@@
 
-  # Main diagonal of matrix 2
+  # Filling main diagonal of matrix 2
   for (j in 1:M){
@@
 
-  #===========================================================================================
+  #========================================================================================
   # Constructing more matricies and iterating the procedure from maturity to time 0
@@
 
-```{r}
+```{r 14}
+# Convergence Tests for finite difference methods
+# Varying rate steps
+
+# rate_step <- c(0.02,0.016,0.012,0.010,0.008,0.006,0.005,0.004,0.003,0.002)
+# rate_vec <- NULL
+# for (i in 1:length(rate_step)){
+#   rate_vec[i] <- length(seq(-0.4,0.6,rate_step[i])) 
+# }
+# 
+# 
+# closed_r <- NULL
+# CN_conv_1 <- NULL
+# Impl_conv_1 <- NULL
+# Expl_conv_1 <- NULL
+# 
+# 
+# 
+# for (i in 1:length(rate_step)){
+#   closed_r[i] <- bond_price()
+# }
+# 
+# for (i in 1:length(rate_step)){
+#   CN_conv_1[i] <- CN(J = seq(-0.4,0.6,rate_step[i]))
+# }
+# 
+# for (i in 1:length(rate_step)){
+#   Impl_conv_1[i] <- implicit(J = seq(-0.4,0.6,rate_step[i]))
+# }
+# 
+# for (i in 1:length(rate_step)){
+#   Expl_conv_1[i] <- explicit(J = seq(-0.4,0.6,rate_step[i]))
+# }
+# 
+# par(mfrow = c(1,1))
+# plot(closed_r, x = rate_vec, type = "l", xlab = "Number of time steps", ylab = "Estimated Price")
+# lines(x = rate_vec, y = CN_conv_1, type = "l", lty = 2)
+# lines(x = rate_vec, y = Impl_conv_1, type = "l", lty = 3, col = "blue")
+# lines(x = rate_vec, y = Expl_conv_1, type = "l", lty = 4, col = "red")
+# legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)
+
+```
+
+```{r 15}
 # Covergence tests for Monte Carlo functions

### 2018-08-03 ZCB Pricing .Rmd
Sensitivity tests
njhjhjh

@@
 
-# library(knitr)
-# kable(compare_mat,align = "c")
+library(xtable)
+xtable(compare_mat, digits = 5)
 
@@
 
-#par(mfrow = c(2,2))
-#plot(1:8,senses[1,2:9])
-#lines(1:8,senses[2, 2:9], col="red", type="l")
+par(mfrow = c(2,2))
+first <- as.vector(senses[1,2:9])
+plot(1:8,first)
+test <- as.vector(senses[2, 2:9])
+lines(1:8,test, col="red", type="l")
 

### 2018-08-03 Draft.tex
Update Draft.tex
First half of sensitivity analysis

@@
 \end{table}
+newpage
+\subsection{Sensitivity tests}
+\label{subsec: Senses}
+In order to confirm that the behaviour of the numerical methods is as expected under different parameters, several different parameter values are tested.
+The initial set of parameters are those used in section \ref{sec : Compar}.
+From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested.
+For each parameter varied, the bond price produced by each numerical method under the chosen scenarios is plotted along with the bond price produced by the closed form solution.\\\\
+In varying the interest rate from the initial $8\%$, all methods behave as expected.
+When the interest rate is reduced to $5\%$, the bond price decreases.
+When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$.
+However, the bond price produced by the explicit method decreases significantly and is in fact negative.
+This is caused by [missing].\\\\
+All the methods behave normally when the standard deviation is increase from the initial $0.5\%$ to $1\%$.
+When the standard deviation is decreases to $0.1\%$, the Monte-Carlo methods produce slightly lower bond prices while the finite differences produce bond prices in excess of 2.
+This highlight the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the partial differential equation from which the tridiagonal matrices used for the methods are created.
 	\newpage

### 2018-08-04 ZCB Pricing .Rmd
Senses

@@
 first <- as.vector(senses[1,2:9])
-plot(1:8,first)
+plot(1:8,first, ylim =c(0.58,0.66))
 test <- as.vector(senses[2, 2:9])
-lines(1:8,test, col="red", type="l")
-
+lines(1:8, test, col="red")
+lines(1:8, senses[3,2:9],col ="blue")
 ```
@@
 par(mfrow = c(1,1))
-plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
-lines(x = time_vec, y = CN_conv, type = "l", lty = 2)
-lines(x = time_vec, y = Impl_conv, type = "l", lty = 3, col = "blue")
-lines(x = time_vec, y = Expl_conv, type = "l", lty = 4, col = "red")
-legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)
+plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
+lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5)
+lines(x = time_vec, y = Impl_conv, type = "l", lty = 2, col = "blue",lwd =1.5)
+lines(x = time_vec, y = Expl_conv, type = "l", lty = 2, col = "red",lwd =1.5)
+legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","black","blue", "red"), cex = 0.8, bty ="n")
 
@@
 
-plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price")
-lines(x = trials_vec, y = CR_conv, type = "l", lty = 2)
-lines(x = trials_vec, y = AV_conv, type = "l", lty = 3, col = "blue")
-lines(x = trials_vec, y = MM_conv, type = "l", lty = 4, col = "red")
-lines(x = trials_vec, y = CV_conv, type = "l", lty = 5, col = "grey")
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
+lines(x = trials_vec, y = CR_conv, type = "l", lty = 1, lwd =1.5)
+lines(x = trials_vec, y = AV_conv, type = "l", lty = 1, col = "blue", lwd =1.5)
+lines(x = trials_vec, y = MM_conv, type = "l", lty = 1, col = "green", lwd =1.5)
+lines(x = trials_vec, y = CV_conv, type = "l", lty = 1, col = "red", lwd = 2)
 
-legend(x = 1500, y = 0.618, legend = c("Closed Form", "Crude", "Antithetic Variates", "Moment Matching","Control Variates"), lty = 1:5, col = c("black","black","blue", "red","grey"), cex = 0.5)
+legend(x = 600, y = 0.62, legend = c("Closed Form", "Crude Monte Carlo", "Antithetic Variates"), lty = c(2,1,1), lwd =c(1.5,1.5,1.5),col = c("black","black","blue"), cex = 0.8, bty="n")
+
+legend(x = 1200, y = 0.62, legend = c("Moment Matching","Control Variates"), lty = c(1,1), lwd =c(1.5,1.5),col = c("green","red"), cex = 0.8, bty="n")
 
 ```
-
-```

### 2018-08-04 Draft.tex
Methodology first edition

@@
 	\label{sec: Method}
+
+	\section{Monte-Carlo}
+
+According to Cairns, the methodology involves:
+
+\begin{itemize}
+	\item Discretize the SDE using a scheme over a time period [0,T]
+	\item Simulate random i.i.d standard normal variables.
+	\item Simulate a path of interest rates using the discretized SDE and the i.i.d standard normal variables.
+	\item Evaluate the integral $e^{-\int_{t}^{T} r(u)du}$ using one simulated path.
+	\item Repeat the evaluation for more paths and take the sample mean as the final estimate of the bond price.
+
+	The above steps are mentioned in Cairns(2004:185)
+\end{itemize}
+
+A short rate model can be discretized by use of either the Euler or Milstein method.
+According to Van Appel, the disretization for the Vasicek model is the same under the Euler or Milstein method.
+The reason for this being the diffusion term does not depend on $r_t$.
+
+Under this:
+
+$$ \Delta r_t= (alpha-beta r_t)\Delta t+ \sigma \sqrt{\Delta t} z_t+1$$ where $Z_i$
+
+$$r_t+1=r_t+\Delta r_t$$ given $r_0$ to be the initial short rate.
+
+\subsection{Variance reduction techniques}
+
+We make use of three techniques to decrease variance amongst the estimates.The antithetic and moment matching make use of a similar method to the crude monte carlo.
+The difference occurs in the simulation of the normal RV's.
+Dependent $Z_i's$  are used to decrease the variance and increase stability amongst the estimate.The control variates makes use of an positively correlated short rate model who's closed form is known.
+
+\subsubsection{Antithetic variates}
+
+Under this technique,
+
+\begin{itemize}
+	\item First simulate n i.i.d $Z_i's$ and follow the crude monte carlo technique as above.
+	\item Repeat the same procedure using  $-Z_i's$
+	\item The average of estimates is taken to be the final estimate 
+\end{itemize}
+
+Note that $Z_{i}$ and $-Z_{i}$ are negatively correlated and dependent and as such COV( $Z_{i}$,$-Z_{i}$) <0.
+Therefore if $X$ is the price estimated using $Z_i's$ and $Y$ is estimates using $-Z_i's$, then :
+
+$$Z =\frac{X+Y}{2}$$
+
+and
+
+$$VAR(Z)=(\frac{1}{2})^{2}(VAR(X)+VAR(Y)+2COV(X,Y))$$
+
+Since the covariance is negative, the larger its value, the lower the variance of the estimate.
+
+\subsubsection{Moment matching}
+The moment matching method, specifically first moment matching, where the sample normal $Z_{i}s$ are transformed to $\hat{Z}_{i}=Z_{i}-\bar{Z}$ where $\bar{Z}=\sum_{i=1}^{n}\frac{Z_{i}}{n}$.
+
+The resulting $\hat{Z}_{i}s$ are not independent and are then used to simulate the short rate values and find the estimates.
+
+\subsubsection{Control variates}
+Andersen (1995) made use of the Vasicek model as a control variate process when deriving the bond price using the Cox-Ingersoll-Ross(CIR) model.
+In this paper we use the opposite approach and use the CIR model as the control variate process.
+
+The methodology around this involves
+
+\begin{itemize}
+
+	\item Define the price under the close form of the CIR model to be $P_{C}$
+	\item Conduct Monte Carlo simulations for the CIR model and define the price under this to be $\hat{P}_{C}$
+	\item Conduct Monte Carlo simulations for the Vasicek model and define the price under this to be $\hat{P}_{V}$
+	\item Therefore the estimate $P_{V}$:
+		  \\$E[P_{V}]=E[P_{C}]-E[\hat{P}_{C}-\hat{P}_{V}]$
+		         \\ $= E[P_{V}]$
+	\item The variance under such a method will then be 
+	\\$VAR[P_{V}]=VAR[\hat{P}_{V}]+VAR[\hat{P}_{C}]-2COV[\hat{P}_{V},\hat{P}_{C}]$
+
+\end{itemize}
+
+The same case here as a larger covariance will decrease the overall variance.
+
+\section{Finite difference method}
+
+The finite difference methods works on a space which is partitioned into a grid by two independent variables.
+The y variable is the initial rate whilst the x variable is time.
+A boundary condition exists at time T where the price, f(T,.), is set to be 1.The PDE is first discretized .Partial differentials are then calculated at each point on the grid.
+The bond price is then calculated iteratively at all the grid points by solving for the PDE.
+The methodology makes use of matrices to solve for the bond prices.
+
+\subsection{Explicit method}
+
+After discretizing the PDE and grouping the similar terms we arrive at the following equation.
+
+$$f_{i-1,j}=a_{j}f_{i,j-1}+b_{j}f_{i,j}+c_{j}f{i,j+1}$$
+
+where i= 0,....,T \\
+      j= $r_0, ....r_n$
+
+Using the boundary values we substitute into $f_{i,j-1}, f_{i,j}, f{i,j+1}$ and work backwards to calculate the value at point $f_{i-1,j}$ and repeat the process until time t to get the prices for varying interest rates.
+
+Note that:
+
+$$a_{j}=(r_t+1/\Delta t)^{-1}\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j}$$
+$$b_{j}=(r_t+1/\Delta t)^{-1}\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2}$$
+$$c_{j}=(r_t+1/\Delta t)^{-1}\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j}$$
+
+Under the matrix formulation we have the equation to be:
+
+$$F_{i-1}=AF_{i}+K_{i}$$
+
+where
+
+$$F_{i}= \begin{bmatrix}
+			f_{i,1} \\
+			f_{i,2} \\
+			\vdots \\
+			f_{i,r_{n-1}}
+		\end{bmatrix}
+$$
+
+$$K_{i}= \begin{bmatrix}
+			a_{1}f_{i,0} \\
+			0 \\
+			\vdots \\
+			0 \\
+			c_{j-1}f_{i, r_{n-1}}
+		\end{bmatrix}  $$
+
+$$ A= \left( \begin{array}{cccccc}
+b_{1} & c_{1} & 0 & \cdots  & 0 & 0\\
+a_{2} & b_{2} & c_{2} &\cdots & 0 & 0 \\
+ & a_{3} & b_{3} & \cdots & 0 & 0  \\
+ & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+ & 0 & 0 & \cdots & a_{n-1} & b_{n-1} \end{array} \right) $$
+
+\subsection{ Implicit method}
+
+Under this case , once the dicretizationa and grouping of terms occur , we obtain
+
+$$f_{i+1,j}= a_{j}f_{i,j-1}+b_{j}f_{i,j}+c_{j}f{i,j+1} $$
+
+In this case the value at $f_{i+1,j}$ is used to work out the other 3 values.
+This can be done simultaneously as when all the equations are written down, there are equal number of equations as to unknowns.
+
+Under this case
+
+$$a_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
+$$b_{j}= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
+$$c_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$
+
+The matrix formulation is:
+
+$$ BF_{i}= F_{i+1}+K{i}$$
+
+$$F_{i}= \begin{bmatrix}
+f_{i,1} \\
+f_{i,2} \\
+\vdots \\
+f_{i,r_{n-1}}
+\end{bmatrix}
+$$
+
+$$K_{i}= \begin{bmatrix}
+-a_{1}f_{i,0} \\
+0 \\
+\vdots \\
+0 \\
+-c_{j-1}f_{i, r_{n-1}}
+\end{bmatrix}  $$
+
+where $B$ is the tridiagonal matrix with the entries similar to the explicit method.
+
+\subsection{Crank Nicholson}
+
+$$a_{j}=(\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}) $$
+
+$$b_{j}= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
+
+$$c_{j}=(-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}) $$
+
+The matrix formulation under this method is :
+
+$$CF_{i-1}=DF_{i-1}+K_{i-1}+K_{i}$$
+
+where
+
+$$ A= \left( \begin{array}{cccccc}
+1-b_{1} & -c_{1} & 0 & \cdots  & 0 & 0\\
+-a_{2} & 1-b_{2} & -c_{2} &\cdots & 0 & 0 \\
+& -a_{3} & 1-b_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & -a_{n-1} & 1-b_{n-1} \end{array} \right) $$
+
+$$ D= \left( \begin{array}{cccccc}
+1+b_{1} & c_{1} & 0 & \cdots  & 0 & 0\\
+a_{2} & 1+b_{2} & c_{2} &\cdots & 0 & 0 \\
+& a_{3} & 1+b_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & -a_{n-1} & 1+b_{n-1} \end{array} \right) $$
 

### 2018-08-04 ZCB Pricing .Rmd
Plots for sensitivity

@@
 colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
+xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods
 
@@
 
-#alpha=0.016
-senses[9,2]=bond_price(alpha=0.016)
-senses[9,3]=Crude_Monte_Carlo(alpha=0.016)
-senses[9,4]=Antithetic_variates(alpha=0.016)
-senses[9,5]=Moment_Matching(alpha=0.016)
-senses[9,6]=Control_Variates_estimate(alpha=0.016)
-senses[9,7]=explicit(alpha=0.016)
-senses[9,8]=implicit(alpha=0.016)
-senses[9,9]=CN(alpha=0.016)
+#alpha=0.16
+senses[9,2]=bond_price(alpha=0.16)
+senses[9,3]=Crude_Monte_Carlo(alpha=0.16)
+senses[9,4]=Antithetic_variates(alpha=0.16)
+senses[9,5]=Moment_Matching(alpha=0.16)
+senses[9,6]=Control_Variates_estimate(alpha=0.16)
+senses[9,7]=explicit(alpha=0.16)
+senses[9,8]=implicit(alpha=0.16)
+senses[9,9]=CN(alpha=0.16)
 
@@
 
-#beta=0.16
-senses[11,2]=bond_price(beta=0.16)
-senses[11,3]=Crude_Monte_Carlo(beta=0.16)
-senses[11,4]=Antithetic_variates(beta=0.16)
-senses[11,5]=Moment_Matching(beta=0.16)
-senses[11,6]=Control_Variates_estimate(beta=0.16)
-senses[11,7]=explicit(beta=0.16)
-senses[11,8]=implicit(beta=0.16)
-senses[11,9]=CN(beta=0.16)
+#beta=1.6
+senses[11,2]=bond_price(beta=1.6)
+senses[11,3]=Crude_Monte_Carlo(beta=1.6)
+senses[11,4]=Antithetic_variates(beta=1.6)
+senses[11,5]=Moment_Matching(beta=1.6)
+senses[11,6]=Control_Variates_estimate(beta=1.6)
+senses[11,7]=explicit(beta=1.6)
+senses[11,8]=implicit(beta=1.6)
+senses[11,9]=CN(beta=1.6)
 
@@
 
-#alpha=0.016,beta=0.16
-senses[13,2]=bond_price(alpha=0.016,beta=0.16)
-senses[13,3]=Crude_Monte_Carlo(alpha=0.016,beta=0.16)
-senses[13,4]=Antithetic_variates(alpha=0.016,beta=0.16)
-senses[13,5]=Moment_Matching(alpha=0.016,beta=0.16)
-senses[13,6]=Control_Variates_estimate(alpha=0.016,beta=0.16)
-senses[13,7]=explicit(alpha=0.016,beta=0.16)
-senses[13,8]=implicit(alpha=0.016,beta=0.16)
-senses[13,9]=CN(alpha=0.016,beta=0.16)
+#alpha=0.16,beta=1.6
+senses[13,2]=bond_price(alpha=0.16,beta=1.6)
+senses[13,3]=Crude_Monte_Carlo(alpha=0.16,beta=1.6)
+senses[13,4]=Antithetic_variates(alpha=0.16,beta=1.6)
+senses[13,5]=Moment_Matching(alpha=0.16,beta=1.6)
+senses[13,6]=Control_Variates_estimate(alpha=0.16,beta=1.6)
+senses[13,7]=explicit(alpha=0.16,beta=1.6)
+senses[13,8]=implicit(alpha=0.16,beta=1.6)
+senses[13,9]=CN(alpha=0.16,beta=1.6)
 
-par(mfrow = c(2,2))
-first <- as.vector(senses[1,2:9])
-plot(1:8,first, ylim =c(0.58,0.66))
-test <- as.vector(senses[2, 2:9])
-lines(1:8, test, col="red")
-lines(1:8, senses[3,2:9],col ="blue")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[2,2:9], col="red",type = "p")
+lines(1:8, senses[3,2:9],col ="blue",type = "p")
+legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[4,2:9], col="red",type = "p")
+lines(1:8, senses[5,2:9],col ="blue",type = "p")
+legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Variance")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[6,2:9], col="red",type = "p")
+lines(1:8, senses[7,2:9],col ="blue",type = "p")
+legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[8,2:9], col="red",type = "p")
+lines(1:8, senses[9,2:9],col ="blue",type = "p")
+legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[10,2:9], col="red",type = "p")
+lines(1:8, senses[11,2:9],col ="blue",type = "p")
+legend("topright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[12,2:9], col="red",type = "p")
+lines(1:8, senses[13,2:9],col ="blue",type = "p")
+legend("topright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
 ```

### 2018-08-04 Draft.tex
Update Draft.tex

@@
 From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested.
-For each parameter varied, the bond price produced by each numerical method under the chosen scenarios is plotted along with the bond price produced by the closed form solution.\\\\
+For each parameter varied, the bond price produced by each numerical method (labelled from 2 to 8 in the order Closed Form,Crude Monte Carlo, Antithetic Variates, Moment Matching, Control Variates, Explicit, Implicit, Crank Nicholson) under the chosen scenarios is plotted along with the bond price produced by the closed form solution (labelled 1).\\\\
 In varying the interest rate from the initial $8\%$, all methods behave as expected.
@@
 When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$.
-However, the bond price produced by the explicit method decreases significantly and is in fact negative.
+However, the bond price produced by the explicit method decreases significantly and is in fact $-4.873359\times10^{32}$.
 This is caused by [missing].\\\\
-All the methods behave normally when the standard deviation is increase from the initial $0.5\%$ to $1\%$.
-When the standard deviation is decreases to $0.1\%$, the Monte-Carlo methods produce slightly lower bond prices while the finite differences produce bond prices in excess of 2.
-This highlight the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the partial differential equation from which the tridiagonal matrices used for the methods are created.
+All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$.
+When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2.
+This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
+When alpha is decreased from the initial $0.08$, the bond prices for all methods increase.
+When alpha is increased, the bond prices for all methods decrease, with the price produced by the explicit method again decreasing rapidly to $-1.257679$.
+When the value of beta is decreased from the initial $0.8$, the bond price produced by all methods decreases.
+When beta is increases, the bond price produced by all methods increases, which the exception of the explicit.
+For the explicit method, the price is once again negative and equal to $-2.492100\times10^{45}$.
+If alpha and beta are varied simultaneously such the mean remains constant and only the mean reversion rate changes then the bond prices don't vary significantly, with the prices being higher for the higher mean reversion rates (i.e.
+the higher beta value).
+Again an exception is found with the explicit method, where the price for the increased beta is $-5.065734\times10^{34}$.
 	\newpage

### 2018-08-05 Draft.tex
pickle rick !!!!!!!!!
PC Time 2

--- 2018-08-04 Draft.tex
@@
 		\hline
-		Numerical Method & Price & Known Price & Error & Computation Time \\ 
+		Numerical Method & Price & Known Price & Error & Computation Time PC 1& Computation Time PC 2\\ 
 		\hline
-		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 \\ 
-		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 \\ 
-		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 \\ 
-		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 \\ 
-		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 \\ 
-		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 \\ 
-		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 \\ 
+		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 & 0.37700\\ 
+		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 & 0.10100\\ 
+		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 & 0.09700\\ 
+		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 & 0.59300\\ 
+		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 & 0.08400\\ 
+		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 & 0.11300\\ 
+		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 & 0.15900\\ 
 		\hline

### 2018-08-05 Draft.tex
Update Draft.tex

--- 2018-08-04 Draft.tex
@@
 
-	\section{Monte-Carlo}
+	\subsection{Monte-Carlo}
 
@@
 
-\section{Finite difference method}
+\subsection{Finite difference method}
 
@@
 
-\subsection{Explicit method}
+\subsubsection{Explicit method}
 
@@
 
-\subsection{ Implicit method}
+\subsubsection{ Implicit method}
 
@@
 
-\subsection{Crank Nicholson}
+\subsubsection{Crank Nicholson}
 
@@
 		\hline
-		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 \\ 
-		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 \\ 
-		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 \\ 
-		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 \\ 
-		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 \\ 
-		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 \\ 
-		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 \\ 
+		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 & 0.37700\\ 
+		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 & 0.10100\\ 
+		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 & 0.09700\\ 
+		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 & 0.59300\\ 
+		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 & 0.08400\\ 
+		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 & 0.11300\\ 
+		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 & 0.15900\\  
 		\hline

### 2018-08-05 Draft.tex
Update Draft.tex

@@
 
-	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|}
+	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|}
 		\hline
-		Numerical Method & Price & Known Price & Error & Computation Time \\ 
+		Numerical Method & Price & Known Price & Error & Computation Time & Computation Time \\ 
 		\hline

### 2018-08-05 Draft.tex
Update Draft.tex

@@
 
-We make use of three techniques to decrease variance amongst the estimates.The antithetic and moment matching make use of a similar method to the crude monte carlo.
+We make use of three techniques to decrease variance amongst the estimates.The antithetic and moment matching make use of a similar method to the
+
+monte carlo.
 The difference occurs in the simulation of the normal RV's.
@@
 This is caused by [missing].\\\\
-All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$.
-When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2.
-This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
+All the methods don't result in significant changes to the bond price when sigma is increases from the initial $0.5\%$ to $1\%$.
+When sigma decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2.
+This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when sigma is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
 When alpha is decreased from the initial $0.08$, the bond prices for all methods increase.

### 2018-08-05 Draft.tex
Update Draft.tex

--- 2018-08-05 Draft.tex
@@
 \usepackage{array}
-%\usepackage{appendix}
+\usepackage{float}
+\usepackage{graphicx}
+\usepackage{hyperref}
+\hypersetup{
+	colorlinks=true,
+	linkcolor=blue,
+	filecolor=magenta,      
+	urlcolor=cyan,
+}
+%titleackage{appendix}
 \usepackage[british]{babel}
@@
 
+The term structure of interest rates provides the relationship between time and interest rates \citep{hull2016options}.
+This relationship can be modelled by specifying an underlying probability space $(\Omega,\mathcal{F},\mathbb{P})$ as well as a Brownian Motion process $\{W_{s}:t \leq s \leq T\}$ which generates the natrual filtration $\mathbb{F}^{W} = \{\mathcal{F}_{s}^{W}: t \leq s \leq T\}$.
+A further specification is made for the choice of measure.
+The common approach for pricing financial instruments is to use the risk-neutral measure $\mathbb{Q}$, which allows for no arbitrage according to the Fundamantal Theorem of Asset Pricing \citep{shreve2004stochastic}.
+When pricing the zero-coupon bond, the continously compounded interest rate will be modelled as an Ornstein-Uhlenbeck short rate process $\{r_t\}$ and this satisfies the following stochastic differential equation (SDE):
+\begin{equation}
+dr_{t} = (\alpha-\beta r_{t})dt + \sigma dW_{t} \quad \alpha, \beta \in \mathbb{R}, \sigma>0
+\end{equation}
+
+From this equation, the bond price $B(t,T)$, with boundary condition of $B(T,T) = 1$, can be computed with the following conditional expectation \citep{mamon2004three}.
+\begin{equation}
+B(t,T) = \mathbb{E}^{\mathbb{Q}}\left[exp\left(-\int_{t}^{T}r_{s} ds\right)\middle\vert\mathcal{F}_{t}\right]
+\end{equation}
+
+There are two approaches which can then be used to estimate $B(t,T)$.
+The first is to use the properties of the Ornstein-Uhlenbeck process, which is proven to have a solution to the SDE which is a Gaussian process \citep{finch2004ornstein}.
+This means that Normal random variables can be generated over short increments of time and this estimates the integral in (2).
+This is repeated many times in order to obtain the expected value and this called the Monte Carlo method.
+
+The second approach is to use the partial differential equation (PDE) that is derived from (1) and (2) and the fact that the short rate process obeys the Markov Property \citep{mamon2004three}.
+The partial differential equation, along with the  boundary condition of $B(T,T) = 1$, is given as follows:
+\begin{equation}
+-r_t B(t,T) + \frac{\partial}{\partial t} B(t,T) + \frac{\partial}{\partial r_t}B(t,T)(\alpha - \beta r_t) +\frac{1}{2} \sigma^2 \frac{\partial^2}{\partial r_t^2} B(t,T) = 0 
+\end{equation}
+A series of numerical methods known as finite difference methods are then used to solve this PDE for $B(t,T)$.
+These methods work by specifying a grid using a discretization of the short rate variable between two values and a discretization of the time variable over $[t,T]$ \citep{ketsise2006monitoring}.
+These methods start at the maturity time $T$ and approximate the partial differential terms of the PDE at each grid point \citep{crank}.
+The way in which these terms are approximated vary between the different methods and this leads to salient differences in the resulting bond prices.
+This paper will make use of different variations of the Monte Carlo method and three finite difference methods in order to approximate the bond price.
+A more detailed explanation on how these methods are implemented is given in the methodology
+
 \newpage
@@
 
-According to Cairns, the methodology involves:
+We first discretize the SDE using a scheme over a time period [0,T]. The choice of the scheme is between the Euler Marumaya scheme and the Milstein scheme.
 
-\begin{itemize}
-	\item Discretize the SDE using a scheme over a time period [0,T]
-	\item Simulate random i.i.d standard normal variables.
-	\item Simulate a path of interest rates using the discretized SDE and the i.i.d standard normal variables.
-	\item Evaluate the integral $e^{-\int_{t}^{T} r(u)du}$ using one simulated path.
-	\item Repeat the evaluation for more paths and take the sample mean as the final estimate of the bond price.
+According to Van Appel, the disretization for the Vasicek model is the same under the Euler or Milstein method. The reason for this being the diffusion term does not depend on $r_t$.
 
-	The above steps are mentioned in Cairns(2004:185)
-\end{itemize}
+We discretize the model to obtain:
+$$ \Delta r_t= (\alpha-\beta r_t)\Delta t+ \sigma \sqrt{\Delta t} z_t+1$$ where $Z_i$
 
-A short rate model can be discretized by use of either the Euler or Milstein method.
-According to Van Appel, the disretization for the Vasicek model is the same under the Euler or Milstein method.
-The reason for this being the diffusion term does not depend on $r_t$.
+$$r_=r_t+\Delta r_t$$ given $r_0$ to be the initial short rate.
 
-Under this:
+We then simulate random independent and identically distributed (i.i.d) standard normal variables. These random variables are substituted into the discretized SDE to simulate a path of interest rates.
 
-$$ \Delta r_t= (alpha-beta r_t)\Delta t+ \sigma \sqrt{\Delta t} z_t+1$$ where $Z_i$
+The integral $e^{-\int_{t}^{T} r(u)du}$ is evaluated using one of the paths. This is done by summing up the integrals on one path and then taking its exponential.
 
-$$r_t+1=r_t+\Delta r_t$$ given $r_0$ to be the initial short rate.
+This is then repeated for more paths and we take the sample mean as the final estimate of the bond price.
 
@@
 \label{subsec: Compar}
-	The methodology was implemented in R under an arbitrary set of parameters, where $\alpha = 0.08$, $\beta = 0.8$ and $\sigma=0.005$.
-This implied a mean rate of 0.10 under the short rate model and an initial rate of 0.08 was selected.
+The methodology has been implemented in R under an arbitrary set of parameters, where $\alpha = 0.08$, $\beta = 0.8$ and $\sigma=0.005$.
+This implies a mean rate of 0.10 under the short rate model and an initial rate of 0.08 is selected.
 These are annually effective and the time to maturity is 5 years.
-The Monte Carlo methods were all implemented under 1000 trials and with a partition of 200 subintervals over the time range.
+The Monte Carlo methods are all implemented under 1000 trials and with a partition of 200 subintervals over the time range.
 The partition of time for the finite difference methods was composed of 1250 equally-spaced subintervals, which is consistent with 250 trading days per year.
@@
 \caption{Comparision of Bond Prices for Numerical Methods}
-
-	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|}
+\vspace{0.5cm}
+\label{tab: Table1}
+\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|}
 	\hline
-		Numerical Method & Price & Known Price & Error & Computation Time \\ 
+	Numerical Method & Price & Known Price & Error & System Time \\ 
 	\hline
-		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 & 0.37700\\ 
-		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 & 0.10100\\ 
-		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 & 0.09700\\ 
-		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 & 0.59300\\ 
-		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 & 0.08400\\ 
-		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 & 0.11300\\ 
-		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 & 0.15900\\  
+	Crude Monte Carlo & 0.62114 & 0.62164 & 0.00050 & 0.72 \\ 
+	Antithetic Variates & 0.62460 & 0.62164 & -0.00296 & 0.95 \\ 
+	Moment Matching & 0.62840 & 0.62164 & -0.00676 & 1.01 \\ 
+	Control Variates & 0.62152 & 0.62164 & 0.00011 & 1.33 \\ 
+	Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.1\\ 
+	Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.2 \\ 
+	Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.24 \\ 
 	\hline
@@
 \end{table}
-newpage
-\subsection{Sensitivity tests}
-\label{subsec: Senses}
+
+\subsubsection{Speed}
+The results in \hyperref[tab: Table1]{Table 1} show that the finite difference methods have a significanlty smaller computation time than the Monte Carlo methods.
+The Crude, Antithetic Variates and Moment Matching methods all show higher error terms than the finite difference methods even though their computation times are higher.
+However the Control Variates method produces the closest result to the known solution but it also has the highest run time.
+
+\subsubsection{Convergence}
+
+In terms of the Monte Carlo methods, convergence to the known solution may be achieved as the number of trials increase.
+\hyperref[fig:MC Conv]{Figure 1} is a depiction of how the results behave as the number of trials increases from 0 to 2000 for each Monte Carlo method.
+\begin{figure}[H]	
+	\label{fig:MC Conv}
+	\begin{center}
+		\includegraphics[trim={0 0.5cm 0 0},clip, width = 14cm]{MC_Conv.eps}
+		\caption{Convergence of Monte Carlo Bond Prices}
+	\end{center}
+\end{figure}
+
+All methods show a lack of convergence for smaller trials but the Moment Matching and Antithetic Variates methods demonstrates no clear tendency towards the known solution even for very high trials.
+The Crude Monte Carlo method demonstrates a closer convergence however the Control Variates method shows the highest convergence to the known solution.
+
+In terms of the Finite Difference methods, convergence can be analysed by observing the methods as the partition of the grid becomes dense.
+Since maturity time is held constant, the time partition is made to be finer by increasing the number of subintervals.
+\hyperref[fig:Fig Conv]{Figure 2} shows how the bond price estimates change as the partition of time becomes more dense.
+\begin{figure}[H]
+	\label{fig:Fig Conv}
+	\begin{center}
+		\includegraphics[trim={0 0.5cm 0 0},clip, width = 14cm]{Fin_Conv.eps}
+		\caption{Convergence of Finite Difference Bond Prices}
+	\end{center}
+\end{figure}
+
+All methods tend towards the known solution with the implicit and explicit methods showing a similiar rate of convergence.
+However, Crank-Nicolson method demonstrates a slower rate of convergence than the other methods.
+
+\subsubsection{Stability}
+
+\subsection{Sensitivy Tests}
 In order to confirm that the behaviour of the numerical methods is as expected under different parameters, several different parameter values are tested.
@@
 From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested.
-For each parameter varied, the bond price produced by each numerical method (labelled from 2 to 8 in the order Closed Form,Crude Monte Carlo, Antithetic Variates, Moment Matching, Control Variates, Explicit, Implicit, Crank Nicholson) under the chosen scenarios is plotted along with the bond price produced by the closed form solution (labelled 1).\\\\
+For each parameter varied, the bond price produced by each numerical method under the chosen scenarios is plotted along with the bond price produced by the closed form solution.\\\\
 In varying the interest rate from the initial $8\%$, all methods behave as expected.
@@
 When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$.
-However, the bond price produced by the explicit method decreases significantly and is in fact $-4.873359\times10^{32}$.
+However, the bond price produced by the explicit method decreases significantly and is in fact negative.
 This is caused by [missing].\\\\
-All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$.
-When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2.
-This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
-When alpha is decreased from the initial $0.08$, the bond prices for all methods increase.
-When alpha is increased, the bond prices for all methods decrease, with the price produced by the explicit method again decreasing rapidly to $-1.257679$.
-When the value of beta is decreased from the initial $0.8$, the bond price produced by all methods decreases.
-When beta is increases, the bond price produced by all methods increases, which the exception of the explicit.
-For the explicit method, the price is once again negative and equal to $-2.492100\times10^{45}$.
-If alpha and beta are varied simultaneously such the mean remains constant and only the mean reversion rate changes then the bond prices don't vary significantly, with the prices being higher for the higher mean reversion rates (i.e.
-the higher beta value).
-Again an exception is found with the explicit method, where the price for the increased beta is $-5.065734\times10^{34}$.
-	\newpage
-	\section{Discussion}
-	\label{sec: Discuss}
-
+All the methods behave normally when the standard deviation is increase from the initial $0.5\%$ to $1\%$.
+When the standard deviation is decreases to $0.1\%$, the Monte-Carlo methods produce slightly lower bond prices while the finite differences produce bond prices in excess of 2.
+This highlight the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the partial differential equation from which the tridiagonal matrices used for the methods are created.
+\
 \newpage

### 2018-08-05 Draft.tex
Update Draft.tex
Putting back deleted sensitivity analysis

@@
 From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested.
-For each parameter varied, the bond price produced by each numerical method under the chosen scenarios is plotted along with the bond price produced by the closed form solution.\\\\
+For each parameter varied, the bond price produced by each numerical method under the chosen scenarios is plotted along with the bond price produced by the closed form solution.
 In varying the interest rate from the initial $8\%$, all methods behave as expected.
@@
 However, the bond price produced by the explicit method decreases significantly and is in fact negative.
-This is caused by [missing].\\\\
+This is caused by [missing].
 All the methods behave normally when the standard deviation is increase from the initial $0.5\%$ to $1\%$.
@@
 This highlight the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the partial differential equation from which the tridiagonal matrices used for the methods are created.
+In order to confirm that the behaviour of the numerical methods is as expected under different parameters, several different parameter values are tested.
+The initial set of parameters are those used in section \ref{sec : Compar}.
+From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested.
+For each parameter varied, the bond price produced by each numerical method (labelled from 2 to 8 in the order Closed Form,Crude Monte Carlo, Antithetic Variates, Moment Matching, Control Variates, Explicit, Implicit, Crank Nicholson) under the chosen scenarios is plotted along with the bond price produced by the closed form solution (labelled 1).
+In varying the interest rate from the initial $8\%$, all methods behave as expected.
+When the interest rate is reduced to $5\%$, the bond price decreases.
+When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$.
+However, the bond price produced by the explicit method decreases significantly and is in fact $-4.873359\times10^{32}$.
+This is caused by [missing].
+All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$.
+When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2.
+This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.
+When alpha is decreased from the initial $0.08$, the bond prices for all methods increase.
+When alpha is increased, the bond prices for all methods decrease, with the price produced by the explicit method again decreasing rapidly to $-1.257679$.
+When the value of beta is decreased from the initial $0.8$, the bond price produced by all methods decreases.
+When beta is increases, the bond price produced by all methods increases, which the exception of the explicit.
+For the explicit method, the price is once again negative and equal to $-2.492100\times10^{45}$.
+If alpha and beta are varied simultaneously such the mean remains constant and only the mean reversion rate changes then the bond prices don't vary significantly, with the prices being higher for the higher mean reversion rates (i.e.
+the higher beta value).
+Again an exception is found with the explicit method, where the price for the increased beta is $-5.065734\times10^{34}$.
 \

### 2018-08-05 ZCB Pricing .Rmd
fifa !!!!!
sensitivity plots update

@@
 colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
-xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods
+#xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods
 
@@
 
+par(mfrow=c(1,1))
 plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Variance")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
 #axis(1, at=1:8, labels=xvec)

### 2018-08-05 ZCB Pricing .Rmd
BOundary conditions

--- 2018-08-04 ZCB Pricing .Rmd
@@
   for (i in 1:(length(I)+1)){
+    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
+    C[M,1] <- (pu(M))*Bond_values[M,1]
+    C[1,1] <- pd(1)*Bond_values[1,1]
+
     Bond_values <- Diag_1%*%Bond_values
@@
     C[M,1] <- (-pu(M))*Bond_values[M,1]
-    C[1,1] <- -pd(1)
+    C[1,1] <- -pd(1)*Bond_values[1,1]
 
-    RHS <- Bond_values  # Working backwards recursively 
+    RHS <- Bond_values + C # Working backwards recursively 
     Bond_values <- Inv%*%RHS
@@
 
-  # C_1 <- matrix(0,nrow = M,ncol = 1)
-  # C_1[1,1] <- -2*pd(1)
-  # C_1[M,1] <- -2*pu(M)
-  # 
   # C_2 <- matrix(0,nrow = M,ncol = 1)
@@
   for (i in 1:(length(I)+1)){
-
-    RHS <- Diag_2%*%Bond_values 
+    C_1 <- matrix(0,nrow = M,ncol = 1)
+    C_1[1,1] <- pd(1)*Bond_values[1,1]
+    C_1[M,1] <- pu(M)*Bond_values[M,1]
+    RHS <- Diag_2%*%Bond_values +2*C_1
     Bond_values <- Inv%*%RHS
@@
 for (i in 1: length(xvec)){
-  Expl[i] <- explicit(r = xvec[i])
+  Expl[i] <- explicit(r = xvec[i], I = 1:10000)
 }

### 2018-08-06 ZCB Pricing .Rmd
Fixed Finite Differences

@@
   # Working backwards in time
-  for (i in 1:(length(I)+1)){
+  for (i in 1:(length(I))){
     C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
@@
 
-  for (i in 1:(length(I) +1)){
+  for (i in 1:(length(I))){
     C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
@@
   # Constructing more matricies and iterating the procedure from maturity to time 0
-
-  Bond_values <- matrix(1,nrow = M, ncol = 1)
-
-  # C_2 <- matrix(0,nrow = M,ncol = 1)
-  # C_2[1,1] <- pd(1)
-  # C_2[M,1] <- pu(M)
   Inv <- solve(Diag_1)
 
-  for (i in 1:(length(I)+1)){
+  Bond_values_1 <- matrix(1,nrow = M, ncol = 1)
+  Bond_values_2 <- matrix(1,nrow = M, ncol = 1)
   C_1 <- matrix(0,nrow = M,ncol = 1)
-    C_1[1,1] <- pd(1)*Bond_values[1,1]
-    C_1[M,1] <- pu(M)*Bond_values[M,1]
-    RHS <- Diag_2%*%Bond_values +2*C_1
+  C_1[1,1] <- pd(1)*Bond_values_1[1,1]
+  C_1[M,1] <- pu(M)*Bond_values_1[M,1]
+  RHS <- Diag_2%*%Bond_values_1 +2*C_1
+  Bond_values_1 <- Inv%*%RHS
+
+  for (i in 1:(length(I)-1)){
+    C_2 <- matrix(0,nrow = M,ncol = 1)
+    C_2[1,1] <- pd(1)*Bond_values_2[1,1]
+    C_2[M,1] <- pu(M)*Bond_values_2[1,1]
+
+    C_1 <- matrix(0,nrow = M,ncol = 1)
+    C_1[1,1] <- pd(1)*Bond_values_1[1,1]
+    C_1[M,1] <- pu(M)*Bond_values_1[M,1]
+
+    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_1
     Bond_values <- Inv%*%RHS
+    Bond_values_2 <- Bond_values_1
+    Bond_values_1 <- Bond_values
   }
@@
 
-```{r 10, echo = FALSE}
+```{r 10}
 # Comparison of results for numerical methods

### 2018-08-06 Draft.tex
Methodology

@@
 
-We make use of three techniques to decrease variance amongst the estimates.The antithetic and moment matching make use of a similar method to the crude monte carlo.
-The difference occurs in the simulation of the normal RV's.
-Dependent $Z_i's$  are used to decrease the variance and increase stability amongst the estimate.The control variates makes use of an positively correlated short rate model who's closed form is known.
+To decrease the variance of the estimates , three variance reduction techniques will be used.
 
@@
 
-Under this technique,
-
-\begin{itemize}
-	\item First simulate n i.i.d $Z_i's$ and follow the crude monte carlo technique as above.
-	\item Repeat the same procedure using  $-Z_i's$
-	\item The average of estimates is taken to be the final estimate 
-\end{itemize}
-
-Note that $Z_{i}$ and $-Z_{i}$ are negatively correlated and dependent and as such COV( $Z_{i}$,$-Z_{i}$) <0.
-Therefore if $X$ is the price estimated using $Z_i's$ and $Y$ is estimates using $-Z_i's$, then :
-
-$$Z =\frac{X+Y}{2}$$
-
-and
-
-$$VAR(Z)=(\frac{1}{2})^{2}(VAR(X)+VAR(Y)+2COV(X,Y))$$
-
-Since the covariance is negative, the larger its value, the lower the variance of the estimate.
+Under this technique, First simulate n i.i.d $Z_i's$ and follow the crude monte carlo technique as above.Repeat the same procedure using  $-Z_i's$.The average of estimates is taken to be the final estimate
 
@@
 
-The resulting $\hat{Z}_{i}s$ are not independent and are then used to simulate the short rate values and find the estimates.
+The resulting $\hat{Z}_{i}s$ are not independent and are then used to simulate the short rate values and find the estimates as in the Monte Carlo method.
 
 \subsubsection{Control variates}
-Andersen (1995) made use of the Vasicek model as a control variate process when deriving the bond price using the Cox-Ingersoll-Ross(CIR) model.
-In this paper we use the opposite approach and use the CIR model as the control variate process.
 
-The methodology around this involves
+Define the price under the close form of the CIR model to be $P_{C}$.
+Conduct Monte Carlo simulations for the CIR model and define the price under this to be $\hat{P}_{C}$.Conduct Monte Carlo simulations for the Vasicek model and define the price under this to be $\hat{P}_{V}$
 
-\begin{itemize}
+Define $P_{V}$ to be the numerical estimate of the bond price
 
-	\item Define the price under the close form of the CIR model to be $P_{C}$
-	\item Conduct Monte Carlo simulations for the CIR model and define the price under this to be $\hat{P}_{C}$
-	\item Conduct Monte Carlo simulations for the Vasicek model and define the price under this to be $\hat{P}_{V}$
-	\item Therefore the estimate $P_{V}$:
-	\\$E[P_{V}]=E[P_{C}]-E[\hat{P}_{C}-\hat{P}_{V}]$
-	\\ $= E[P_{V}]$
-	\item The variance under such a method will then be 
+$E[P_{V}]=E[\hat{P}_{V}-\hat{P}_{C}]+P_{V} $
+
+The variance under this method is then:  
 \\$VAR[P_{V}]=VAR[\hat{P}_{V}]+VAR[\hat{P}_{C}]-2COV[\hat{P}_{V},\hat{P}_{C}]$
-
-\end{itemize}
-
-The same case here as a larger covariance will decrease the overall variance.
 
@@
 The y variable is the initial rate whilst the x variable is time.
-A boundary condition exists at time T where the price, f(T,.), is set to be 1.The PDE is first discretized .Partial differentials are then calculated at each point on the grid.
+A boundary condition exists at time T where the price, B(T,.)=1.The PDE is first discretized .Partial differentials are then calculated at each point on the grid.
 The bond price is then calculated iteratively at all the grid points by solving for the PDE.
-The methodology makes use of matrices to solve for the bond prices.
+
+The bond prices are solved for by matrix formulation.
 
@@
 
-$$f_{i-1,j}=a_{j}f_{i,j-1}+b_{j}f_{i,j}+c_{j}f{i,j+1}$$
+$$B_{i-1,j}=pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B_{i,j+1}$$
 
 where i= 0,....,T \\
-j= $r_0, ....r_n$
+      j= $r_0,r_1,....r_n$
 
-Using the boundary values we substitute into $f_{i,j-1}, f_{i,j}, f{i,j+1}$ and work backwards to calculate the value at point $f_{i-1,j}$ and repeat the process until time t to get the prices for varying interest rates.
+First we substitute the boundary values into $B_{i,j-1}, B_{i,j}, B{i,j+1}$ and work backwards to calculate the value at point $B_{i-1,j}$ and repeat the process at each point until time t to get the estimates of the prices for varying interest rates $r_0,r_1,...r_n$
 
 Note that:       
-
-$$a_{j}=(r_t+1/\Delta t)^{-1}\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j}$$
-$$b_{j}=(r_t+1/\Delta t)^{-1}\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2}$$
-$$c_{j}=(r_t+1/\Delta t)^{-1}\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j}$$
+$$pu_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
+$$pm_{j}=(r_j/\Delta t)^{-1}(\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2})$$
+$$pd_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
 
@@
 
-$$F_{i-1}=AF_{i}+K_{i}$$
-
-where
-
-$$F_{i}= \begin{bmatrix}
-f_{i,1} \\
-f_{i,2} \\
+$$\begin{bmatrix}
+	B_{i-1,1} \\
+	B_{i-1,2} \\
 	\vdots \\       
-f_{i,r_{n-1}}
+	B_{i-1,n-1}
 	\end{bmatrix}
-$$
-
-$$K_{i}= \begin{bmatrix}
-a_{1}f_{i,0} \\
+=
+\left( \begin{array}{cccccc}
+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
+pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
+& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & pu_{n-1} & pm_{n-1} \end{array} \right) 
+%
+\begin{bmatrix}
+	B_{i,1} \\
+	B_{i,2} \\
+	\vdots \\       
+	B_{i,n-1}
+\end{bmatrix}
++
+ \begin{bmatrix}
+	pu_{1}B_{i,0} \\
 	0 \\
@@
 	0 \\
-c_{j-1}f_{i, r_{n-1}}
-\end{bmatrix}  $$
-
-$$ A= \left( \begin{array}{cccccc}
-b_{1} & c_{1} & 0 & \cdots  & 0 & 0\\
-a_{2} & b_{2} & c_{2} &\cdots & 0 & 0 \\
-& a_{3} & b_{3} & \cdots & 0 & 0  \\
-& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & a_{n-1} & b_{n-1} \end{array} \right) $$
+	pd_{j-1}B_{i,n-1}
+	\end{bmatrix}  
+$$
 
@@
 
-$$f_{i+1,j}= a_{j}f_{i,j-1}+b_{j}f_{i,j}+c_{j}f{i,j+1} $$
+$$B_{i+1,j}= pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B{i,j+1} $$
 
-In this case the value at $f_{i+1,j}$ is used to work out the other 3 values.
-This can be done simultaneously as when all the equations are written down, there are equal number of equations as to unknowns.
+In this case the value at $B_{i+1,j}$ is used to work out the other 3 values.
+This can be solved simultaneously as when all the equations are written down, there are equal number of equations as to unknowns.
 
@@
 
-$$a_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
-$$b_{j}= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
-$$c_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$
+$$pu_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
+$$pm_{j}= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
+$$pd_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$
 
@@
 
-$$ BF_{i}= F_{i+1}+K{i}$$
-
-$$F_{i}= \begin{bmatrix}
-f_{i,1} \\
-f_{i,2} \\
+$$\left( \begin{array}{cccccc}
+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
+pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
+& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & pd_{n-1} & pm_{n-1} \end{array} \right)
+%
+\begin{bmatrix}
+B_{i,1} \\
+B_{i,2} \\
 \vdots \\
-f_{i,r_{n-1}}
+B_{i,n-1}
+\end{bmatrix}
+=
+\begin{bmatrix}
+B_{i+1,1} \\
+B_{i+1,2} \\
+\vdots \\
+B_{i+1,r_{n-1}}
+\end{bmatrix}
++
+\begin{bmatrix}
+-pu_{1}B_{i,0} \\
+0 \\
+\vdots \\
+0 \\
+-pd_{j-1}B_{i, r_{n-1}}
 \end{bmatrix}
@@
 
-$$K_{i}= \begin{bmatrix}
--a_{1}f_{i,0} \\
+\subsubsection{Crank Nicholson}
+
+This method involves making use of $B_{i,j+1}$, $B_{i,j}$ and $B_{i,j-1}$ to evaluate the prices at $B_{i-11,j+1}$, $B_{i-1,j}$ and $B_{i-1,j-1}$.
+
+$$pu_{j}=\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
+$$pm_{j}= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
+$$pd_{j}=-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
+
+The matrix formulation under this method is:
+
+$$ \left( \begin{array}{cccccc}
+-(1/\Delta t)-pm_{1} & -pd_{1} & 0 & \cdots  & 0 & 0\\
+-pu_{2} & -(1/\Delta t)-pm_{2} & -pd_{2} &\cdots & 0 & 0 \\
+& -pu_{3} & -(1/\Delta t)-pm_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right
+%
+\begin{bmatrix}
+B_{i-1,1} \\
+B_{i-1,2} \\
+\vdots \\
+B_{i-1,n-1}
+\end{bmatrix} 
+\\
+=
+\left( \begin{array}{cccccc}
+-(1/\Delta t)+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
+pu_{2} & -(1/\Delta t)+pm_{2} & pd_{2} &\cdots & 0 & 0 \\
+& pu_{3} & 1+b_{3} & \cdots & 0 & 0  \\
+& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
+& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t+pm_{n-1} \end{array} \right) 
+%
+\begin{bmatrix}
+B_{i,1} \\
+B_{i,2} \\
+\vdots \\
+B_{i,n-1}
+\end{bmatrix}
++
+\begin{bmatrix}
+pu_{1}B_{i-1,0} \\
 0 \\
@@
 0 \\
--c_{j-1}f_{i, r_{n-1}}
-\end{bmatrix}  $$
-
-where $B$ is the tridiagonal matrix with the entries similar to the explicit method.
-
-\subsubsection{Crank Nicholson}
-
-$$a_{j}=(\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}) $$
-
-$$b_{j}= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
-
-$$c_{j}=(-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}) $$
-
-The matrix formulation under this method is :
-
-$$CF_{i-1}=DF_{i-1}+K_{i-1}+K_{i}$$
-
-where
-
-$$ A= \left( \begin{array}{cccccc}
-1-b_{1} & -c_{1} & 0 & \cdots  & 0 & 0\\
--a_{2} & 1-b_{2} & -c_{2} &\cdots & 0 & 0 \\
-& -a_{3} & 1-b_{3} & \cdots & 0 & 0  \\
-& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & -a_{n-1} & 1-b_{n-1} \end{array} \right) $$
-
-$$ D= \left( \begin{array}{cccccc}
-1+b_{1} & c_{1} & 0 & \cdots  & 0 & 0\\
-a_{2} & 1+b_{2} & c_{2} &\cdots & 0 & 0 \\
-& a_{3} & 1+b_{3} & \cdots & 0 & 0  \\
-& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & -a_{n-1} & 1+b_{n-1} \end{array} \right) $$
+pd_{j-1}B_{i-1,n-1}
+\end{bmatrix}
++
+ \begin{bmatrix}
+pu_{1}B_{i,0} \\
+0 \\
+\vdots \\
+0 \\
+pd_{j-1}B_{i,n-1}
+\end{bmatrix}  
+$$
 

### 2018-08-06 ZCB Pricing .Rmd
modified sensitivity graphics

@@
     C_2[1,1] <- pd(1)*Bond_values_2[1,1]
-    C_2[M,1] <- pu(M)*Bond_values_2[1,1]
+    C_2[M,1] <- pu(M)*Bond_values_2[M,1]
 
@@
 
-    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_1
+    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_2
     Bond_values <- Inv%*%RHS
@@
 colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
-#xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods
+xvec=c("Closed Form","Crude","AV","MM","CV","Explicit","Implicit","CN") #list of numerical methods
 
@@
 par(mfrow=c(1,1))
-plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[2,2:9], col="red",type = "p")
-lines(1:8, senses[3,2:9],col ="blue",type = "p")
-legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[2,2:9], col="red",type = "p", pch = 19)
+lines(1:8, senses[3,2:9],col ="blue",type = "p", pch =19)
+legend("bottomright", inset = c(-0,0), legend = c("r = 0.05", "r = 0.08", "r = 0.10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch =19)
 
@@
 
-time_vec <- seq(0,100,1)
+time_vec <- seq(1,100,1)
 
@@
 par(mfrow = c(1,1))
-plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
-lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5)
+plot(closed, x = time_vec, type = "l", ylim = c(0.59,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
+lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5, col = "green")
 lines(x = time_vec, y = Impl_conv, type = "l", lty = 2, col = "blue",lwd =1.5)
 lines(x = time_vec, y = Expl_conv, type = "l", lty = 2, col = "red",lwd =1.5)
-legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","black","blue", "red"), cex = 0.8, bty ="n")
+legend(x = 60, y = 0.62, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","green","blue", "red"), cex = 0.8, bty ="n")
 

### 2018-08-06 Draft.tex
bub

@@
 & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right
+& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right)
 %

### 2018-08-06 Draft.tex
dsfs

--- 2018-08-06 Draft.tex
@@
 
-$$B_{i-1,j}=pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B_{i,j+1}$$
+$$B_{i-1,j}=p_u(j)B_{i,j-1}+p_m(j)B_{i,j}+p_d(j)B_{i,j+1}$$
 
@@
 Note that:       
-$$pu_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
-$$pm_{j}=(r_j/\Delta t)^{-1}(\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2})$$
-$$pd_{j}=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
+$$p_u(j)=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
+$$p_m(j)=(r_j/\Delta t)^{-1}(\frac{1}{\Delta t}-\frac{\sigma^2}{\Delta r_j}^{2})$$
+$$p_d(j)=(r_j/\Delta t)^{-1}(\frac{\sigma^{2}}{2(\Delta r_j)^{2}}+\frac{\alpha-\beta r_j}{2\Delta r_j})$$
 
@@
 \left( \begin{array}{cccccc}
-pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
-& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
+p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
+p_u(2) & p_m(2) & p_d(2) &\cdots & 0 & 0 \\
+& p_u(3) & p_m(3) & \cdots & 0 & 0  \\
 & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & pu_{n-1} & pm_{n-1} \end{array} \right) 
+& 0 & 0 & \cdots & p_u(n-1) & p_m(n-1) \end{array} \right) 
 %
@@
  \begin{bmatrix}
-	pu_{1}B_{i,0} \\
+	p_u(1)B_{i,0} \\
 	0 \\
@@
 	0 \\
-	pd_{j-1}B_{i,n-1}
+	p_d(j-1)B_{i,n-1}
 	\end{bmatrix}  
@@
 
-$$B_{i+1,j}= pu_{j}B_{i,j-1}+pm_{j}B_{i,j}+pd_{j}B{i,j+1} $$
+$$B_{i+1,j}= p_u(j)B_{i,j-1}+p_m(j)B_{i,j}+p_d(j)B{i,j+1} $$
 
@@
 
-$$pu_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
-$$pm_{j}= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
-$$pd_{j}= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$
+$$p_u(j)= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} - \frac{\sigma^2}{2\Delta r^2})\Delta t$$ 
+$$p_m(j)= (r_{j+1}+\frac{1}{\Delta t} + \frac{\sigma^2}{\Delta r ^2})\Delta t$$
+$$p_d(j)= (\frac{\alpha-\beta r_{j+1}}{2\Delta r} + \frac{\sigma^2}{2\Delta r^2})(-\Delta t) $$
 
@@
 $$\left( \begin{array}{cccccc}
-pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & pm_{2} & pd_{2} &\cdots & 0 & 0 \\
-& pu_{3} & pm_{3} & \cdots & 0 & 0  \\
+p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
+p_u(2) & p_m(2) & p_d(2) &\cdots & 0 & 0 \\
+& p_u(3) & p_m(3) & \cdots & 0 & 0  \\
 & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & pd_{n-1} & pm_{n-1} \end{array} \right)
+& 0 & 0 & \cdots & p_d(n-1) & p_m(n-1) \end{array} \right)
 %
@@
 \begin{bmatrix}
--pu_{1}B_{i,0} \\
+-p_u(1)B_{i,0} \\
 0 \\
@@
 0 \\
--pd_{j-1}B_{i, r_{n-1}}
+-p_d(j-1)B_{i, r_{n-1}}
 \end{bmatrix}
@@
 
-$$pu_{j}=\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
-$$pm_{j}= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
-$$pd_{j}=-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
+$$p_u(j)=\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
+$$p_m(j)= \frac{\sigma^2}{2 (\Delta r)^2}+\frac{r_{j}}{2}$$
+$$p_d(j)=-\frac{\alpha-\beta r_{j+1}}{4\Delta r} - \frac{\sigma^2}{4\Delta r^2}$$
 
@@
 
-$$ \left( \begin{array}{cccccc}
--(1/\Delta t)-pm_{1} & -pd_{1} & 0 & \cdots  & 0 & 0\\
--pu_{2} & -(1/\Delta t)-pm_{2} & -pd_{2} &\cdots & 0 & 0 \\
-& -pu_{3} & -(1/\Delta t)-pm_{3} & \cdots & 0 & 0  \\
+$$AB_{i-1}=CB_{i}+F_{i-1}+F_{i}$$
+
+$$A= \left( \begin{array}{cccccc}
+-(1/\Delta t)-p_m(1) & -p_d(1) & 0 & \cdots  & 0 & 0\\
+-p_u(2) & -(1/\Delta t)-p_m(2) & -p_d(2) &\cdots & 0 & 0 \\
+& -p_u(3) & -(1/\Delta t)-p_m(3) & \cdots & 0 & 0  \\
 & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right
-%
-\begin{bmatrix}
-B_{i-1,1} \\
-B_{i-1,2} \\
-\vdots \\
-B_{i-1,n-1}
-\end{bmatrix} 
-\\
-=
-\left( \begin{array}{cccccc}
--(1/\Delta t)+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & -(1/\Delta t)+pm_{2} & pd_{2} &\cdots & 0 & 0 \\
-& pu_{3} & 1+b_{3} & \cdots & 0 & 0  \\
+& 0 & 0 & \cdots & -p_u(n-1) & -(1/\Delta t)-p_m(n-1) \end{array} \right)
+$$
+
+$$C=\left( \begin{array}{cccccc}
+-(1/\Delta t)+p_m(1) & p_d(1) & 0 & \cdots  & 0 & 0\\
+p_u(2) & -(1/\Delta t)+p_m(2) & p_d(2) &\cdots & 0 & 0 \\
+& p_u(3) & 1+b_{3} & \cdots & 0 & 0  \\
 & \vdots &\vdots & \ddots & \vdots & \vdots \\ 
-& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t+pm_{n-1} \end{array} \right) 
-%
-\begin{bmatrix}
-B_{i,1} \\
-B_{i,2} \\
-\vdots \\
-B_{i,n-1}
-\end{bmatrix}
-+
-\begin{bmatrix}
-pu_{1}B_{i-1,0} \\
-0 \\
-\vdots \\
-0 \\
-pd_{j-1}B_{i-1,n-1}
-\end{bmatrix}
-+
- \begin{bmatrix}
-pu_{1}B_{i,0} \\
-0 \\
-\vdots \\
-0 \\
-pd_{j-1}B_{i,n-1}
-\end{bmatrix}  
+& 0 & 0 & \cdots & -p_u(n-1) & -(1/\Delta t+p_m(n-1) \end{array} \right) 
 $$

### 2018-08-06 Draft.tex
Update Draft.tex

@@
 \section{Introduction}
+The pricing of securities is a critical task that many financial institutions must complete.
+In some instances, these securities have simple enough pricing equations with closed form solutions and so they can be solved analytically.
+A zero-coupon bond is an example of such an instrument.
+However, in many cases the closed form solution is not known and a numerical approach is necessary.
+Most options fall into this category.
+As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases.
+Fortunately, we can make use of the fact that we know the analytical solution for a zero coupon bond to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
 \label{sec: Intro}

### 2018-08-07 Draft.tex
Update Draft.tex

@@
 As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases.
-Fortunately, we can make use of the fact that we know the analytical solution for a zero coupon bond to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
+Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
 \label{sec: Intro}

### 2018-08-07 Draft.tex
abstract

@@
 \begin{abstract}
-	Something interesting in this section
+	This paper examines the methods used to price a zero coupon bonds under the Ornstein Uhenbleck process.
+This paper considers the use Monte Carlo simulations together with various variance reduction techniques to verify improvments in stability of estimates.
+The simulation method is compared to various finitie difference techniques to analyse the difference in convergence and speed in evaluating solutions.The various methods are compared to the closed form solution to assess the accuracy.
 \end{abstract}

### 2018-08-07 Draft.tex
Update Draft.tex
kjkh

@@
 		\vspace{1cm}
-		{\Large Pricing a zero coupon bond by Monte Carlo and Finite Difference Methods when the term structure of interest rates is a mean reverting Ornstein-Uhlenbeck process}\\
+		{\Large Pricing a zero-coupon bond by Monte Carlo and Finite Difference Methods when the term structure of interest rates is a mean reverting Ornstein-Uhlenbeck process}\\
 		\vspace{1cm}
@@
 \begin{abstract}
-	This paper examines the methods used to price a zero coupon bonds under the Ornstein Uhenbleck process.
-This paper considers the use Monte Carlo simulations together with various variance reduction techniques to verify improvments in stability of estimates.
+	\noindent This paper examines numerical methods used to price zero coupon bonds under the Ornstein Uhenbleck process.
+This paper considers the use of Monte Carlo simulations together with various variance reduction techniques to verify improvments in the stability of estimates.
 The simulation method is compared to various finitie difference techniques to analyse the difference in convergence and speed in evaluating solutions.The various methods are compared to the closed form solution to assess the accuracy.
@@
 \section{Introduction}
+\label{sec: Intro}
 The pricing of securities is a critical task that many financial institutions must complete.
@@
 Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
-\label{sec: Intro}
 

### 2018-08-07 ZCB Pricing .Rmd

@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[4,2:9], col="red",type = "p")
-lines(1:8, senses[5,2:9],col ="blue",type = "p")
-legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[4,2:9], col="red",type = "p", pch = 19)
+lines(1:8, senses[5,2:9],col ="blue",type = "p", pch = 19)
+legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[6,2:9], col="red",type = "p")
-lines(1:8, senses[7,2:9],col ="blue",type = "p")
-legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.55,0.7), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[6,2:9], col="red",type = "p", pch = 19)
+lines(1:8, senses[7,2:9],col ="blue",type = "p", pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
 

### 2018-08-07 ZCB Pricing .Rmd
column 1

@@
 
+senses[1,1]="-"
+senses[2,1]="r=0.05"
+senses[3,1]="r=0.1"
+senses[4,1]="T=1"
+senses[5,1]="T=10"
+senses[6,1]="sigma=0.001"
+senses[7,1]="sigma=0.01"
+senses[8,1]="alpha=0.01"
+senses[9,1]="alpha=0.16"
+senses[10,1]="beta=0.1"
+senses[11,1]="beta=1.6"
+senses[12,1]="alpha=0.01,beta=0.1"
+senses[13,1]="#alpha=0.16,beta=1.6"
+
 par(mfrow=c(1,1))

### 2018-08-07 ZCB Pricing .Rmd
Graphics

--- 2018-08-06 ZCB Pricing .Rmd
@@
 
+senses[1,1]="-"
+senses[2,1]="r=0.05"
+senses[3,1]="r=0.1"
+senses[4,1]="T=1"
+senses[5,1]="T=10"
+senses[6,1]="sigma=0.001"
+senses[7,1]="sigma=0.01"
+senses[8,1]="alpha=0.01"
+senses[9,1]="alpha=0.16"
+senses[10,1]="beta=0.1"
+senses[11,1]="beta=1.6"
+senses[12,1]="alpha=0.01,beta=0.1"
+senses[13,1]="alpha=0.16,beta=1.6"
+
 par(mfrow=c(1,1))
@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[4,2:9], col="red",type = "p")
-lines(1:8, senses[5,2:9],col ="blue",type = "p")
-legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[4,2:9], col="red",type = "p", pch = 19)
+lines(1:8, senses[5,2:9],col ="blue",type = "p", pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[6,2:9], col="red",type = "p")
-lines(1:8, senses[7,2:9],col ="blue",type = "p")
-legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[6,2:9], col="red",type = "p", pch = 19)
+lines(1:8, senses[7,2:9],col ="blue",type = "p", pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[8,2:9], col="red",type = "p")
-lines(1:8, senses[9,2:9],col ="blue",type = "p")
-legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[8,2:9], col="red",type = "p",pch = 19)
+lines(1:8, senses[9,2:9],col ="blue",type = "p",pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01", "alpha=0.08", "alpha=0.16"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[10,2:9], col="red",type = "p")
-lines(1:8, senses[11,2:9],col ="blue",type = "p")
-legend("topright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(-0.4,1.4), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Beta", xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[10,2:9], col="red",type = "p",pch = 19)
+lines(1:8, senses[11,2:9],col ="blue",type = "p",pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("beta=0.1", "beta=0.8", "beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta")
-#axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[12,2:9], col="red",type = "p")
-lines(1:8, senses[13,2:9],col ="blue",type = "p")
-legend("topright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
+axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[12,2:9], col="red",type = "p",pch = 19)
+lines(1:8, senses[13,2:9],col ="blue",type = "p",pch = 19)
+legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)
 ```
@@
 ```{r 14}
-# Convergence Tests for finite difference methods
-# Varying rate steps
-
-# rate_step <- c(0.02,0.016,0.012,0.010,0.008,0.006,0.005,0.004,0.003,0.002)
-# rate_vec <- NULL
-# for (i in 1:length(rate_step)){
-#   rate_vec[i] <- length(seq(-0.4,0.6,rate_step[i])) 
-# }
-# 
-# 
-# closed_r <- NULL
-# CN_conv_1 <- NULL
-# Impl_conv_1 <- NULL
-# Expl_conv_1 <- NULL
-# 
-# 
-# 
-# for (i in 1:length(rate_step)){
-#   closed_r[i] <- bond_price()
-# }
-# 
-# for (i in 1:length(rate_step)){
-#   CN_conv_1[i] <- CN(J = seq(-0.4,0.6,rate_step[i]))
-# }
-# 
-# for (i in 1:length(rate_step)){
-#   Impl_conv_1[i] <- implicit(J = seq(-0.4,0.6,rate_step[i]))
-# }
-# 
-# for (i in 1:length(rate_step)){
-#   Expl_conv_1[i] <- explicit(J = seq(-0.4,0.6,rate_step[i]))
-# }
-# 
-# par(mfrow = c(1,1))
-# plot(closed_r, x = rate_vec, type = "l", xlab = "Number of time steps", ylab = "Estimated Price")
-# lines(x = rate_vec, y = CN_conv_1, type = "l", lty = 2)
-# lines(x = rate_vec, y = Impl_conv_1, type = "l", lty = 3, col = "blue")
-# lines(x = rate_vec, y = Expl_conv_1, type = "l", lty = 4, col = "red")
-# legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)
-
-```
-
-```{r 15}
 # Covergence tests for Monte Carlo functions

### 2018-08-08 ZCB Pricing .Rmd
Comment changes

--- 2018-08-07 ZCB Pricing .Rmd
@@
       dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
-      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for negative rates
+      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for the use of -Z_i
       sim_path[j,i] =sim_path[j-1,i]+dr
@@
   Sum.= colSums(sim_path_inv[2:(s+1),]*dt)
-  int = exp(-Sum.) #Exponential of the estimate
-  int.= exp(-Sum) #Exponential of the estimate under the negative rv 
+  int = exp(-Sum.) #Exponential of the estimate using Z_i
+  int.= exp(-Sum) #Exponential of the estimate using -Z_i
   mean_1 = mean(int) # Estimate using Z_i
   mean_2 = mean(int.)  # Estimate using -Z_i
-  result = (mean_1+mean_2)/2 # Final estimate
+  result = (mean_1+mean_2)/2 # Final estimate is taken as the average of the two estimates.
   result
@@
   z=rnorm(n)
-  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments
+  z_m= z-mean(z) # Moment matching transformation of Z_i to match finite moments
 
+  # Follow the same process as in the Monte Carlo approach , but use the transformed Z_i's to simulate the rates
   for (i in 1:n){
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] # Simulate rates using the transformed rv 
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] 
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
-# We have decided to make use of the CIR model as our control variate process.
+# Make use of the CIR model as the control variate process.
 # Below is the closed form solution under the CIR model
@@
 }
-# Therefore the control variates estimate:
+# The control variate estimate is taken as the difference between the the Crude MOnte carlo estimates of the Vasicek and CIR model plus the closed form of the CIR model
 
 Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
-  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r)
+  Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)+bond_price_CIR(alpha,beta,sigma,t,T,r)
 }
@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity", xaxt = "n", col ="black", pch = 19, font.main = 1)
-axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[4,2:9], col="red",type = "p", pch = 19)
-lines(1:8, senses[5,2:9],col ="blue",type = "p", pch = 19)
-legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Time to maturity")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[4,2:9], col="red",type = "p")
+lines(1:8, senses[5,2:9],col ="blue",type = "p")
+legend("topright", inset = c(-0,0), legend = c("T=1", "T=5", "T=10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0.55,0.7), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma", xaxt = "n", col ="black", pch = 19, font.main = 1)
-axis(1, at=1:8, labels=xvec)
-lines(1:8, senses[6,2:9], col="red",type = "p", pch = 19)
-lines(1:8, senses[7,2:9],col ="blue",type = "p", pch = 19)
-legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch = 19)
+plot(x=1:8,y=senses[1,2:9], ylim =c(0,2.2), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Sigma")
+#axis(1, at=1:8, labels=xvec)
+lines(1:8, senses[6,2:9], col="red",type = "p")
+lines(1:8, senses[7,2:9],col ="blue",type = "p")
+legend("bottomright", inset = c(-0,0), legend = c("sigma=0.001", "sigma=0.005", "sigma=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")
 
@@
   CR[i]=Crude_Monte_Carlo()
-  #AN[i]=Antithetic_variates()
-  #MM[i]=Moment_Matching()
+  AN[i]=Antithetic_variates()
+  MM[i]=Moment_Matching()
   CV[i]=Control_Variates_estimate()

### 2018-08-08 Draft.tex

--- 2018-08-07 Draft.tex
@@
 As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases.
-Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
+Fortunately, we can make use of the fact that we know the analytical solution for a zero coupon bond to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
 \label{sec: Intro}

### 2018-08-09 ZCB Pricing .Rmd
FInal

@@
 
-Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
+Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
 
@@
 
-Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
+Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
 
@@
 
-Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 200){
+Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 1250){
 
@@
 
-CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=100){
+CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
 
@@
 
-Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=100){
+Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=1250){
   Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)+bond_price_CIR(alpha,beta,sigma,t,T,r)

### 2018-08-09 ZCB Pricing .Rmd
range

--- 2018-08-08 ZCB Pricing .Rmd
@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.7), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
 axis(1, at=1:8, labels=xvec)

### 2018-08-09 ZCB Pricing .Rmd
senses

@@
 legend("bottomright", inset = c(-0,0), legend = c("alpha=0.01,beta=0.1", "alpha=0.08,beta=0.8", "alpha=0.16,beta=1.6"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n",pch = 19)
+
+senses[,2:9] <-round(as.numeric(senses[,2:9]), digits=5)
+library(xtable)
+xtable(senses, digits = 5)
 ```
@@
 plot(closed, x = time_vec, type = "l", ylim = c(0.59,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
-lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5, col = "green")
-lines(x = time_vec, y = Impl_conv, type = "l", lty = 2, col = "blue",lwd =1.5)
-lines(x = time_vec, y = Expl_conv, type = "l", lty = 2, col = "red",lwd =1.5)
-legend(x = 60, y = 0.62, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","green","blue", "red"), cex = 0.8, bty ="n")
+lines(x = time_vec, y = CN_conv, type = "l", lty = 1, lwd =1.5, col = "green")
+lines(x = time_vec, y = Impl_conv, type = "l", lty = 1, col = "blue",lwd =1.5)
+lines(x = time_vec, y = Expl_conv, type = "l", lty = 1, col = "red",lwd =1.5)
+legend(x = 60, y = 0.62, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,1,1,1), col = c("black","green","blue", "red"), cex = 0.8, bty ="n")
 
@@
 
-plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.57,0.70), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
 lines(x = trials_vec, y = CR_conv, type = "l", lty = 1, lwd =1.5)

### 2018-08-09 ZCB Pricing .Rmd
lsdkfjlasfj
lsjfalsjflks

@@
   sim_path[1,]= r # Initial rates on first row.
+  z=rnorm(n)# Generation of standard normal random variables
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sim_path[1,]= r
+  z=rnorm(n) # Generation of standard normal variables
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[i]*sqrt(sim_path[j-1,i]))# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   CR[i]=Crude_Monte_Carlo()
-  #AN[i]=Antithetic_variates()
-  #MM[i]=Moment_Matching()
+  AN[i]=Antithetic_variates()
+  MM[i]=Moment_Matching()
   CV[i]=Control_Variates_estimate()
 }
+
+var(CR)
+var(AN)
+var(MM)
+var(CV)
 

### 2018-08-10 ZCB Pricing .Rmd
Final Version

@@
   Sum=colSums(sim_path[2:(s+1),]*dt)
-  int=exp(-Sum)
-  result=mean(int)
+  int=exp(-Sum)  # Take the exponent of the Integral
+  result=mean(int) # Find the average of expression
   result
@@
 
-    Bond_values <- Diag_1%*%Bond_values
+    Bond_values <- Diag_1%*%Bond_values# New values of bond prices based on next time price
     Bond_values <- Bond_values
@@
   # Constructing more matricies and iterating the procedure from maturity to time 0
-  Inv <- solve(Diag_1)
+  Inv <- solve(Diag_1) # Inverse of 1st tridiagonal matrix
 
+  # These 2 matricies are used for the recursive algorithm
   Bond_values_1 <- matrix(1,nrow = M, ncol = 1) 
   Bond_values_2 <- matrix(1,nrow = M, ncol = 1)
+
+  # Calculation for first time step backwards
   C_1 <- matrix(0,nrow = M,ncol = 1)
-  C_1[1,1] <- pd(1)*Bond_values_1[1,1]
+  C_1[1,1] <- pd(1)*Bond_values_1[1,1] # Matrix for boundary conditions
   C_1[M,1] <- pu(M)*Bond_values_1[M,1]
@@
     Bond_values <- Inv%*%RHS
-    Bond_values_2 <- Bond_values_1
-    Bond_values_1 <- Bond_values
+    Bond_values_2 <- Bond_values_1 # One of the matricies depends on current time
+    Bond_values_1 <- Bond_values # One of the matricies depends on next time step
   }
@@
 ```{r 9}
-# Plots of the different methods
-par(mfrow = c(2,2))
-
-xvec <- seq(-0.4,0.6,0.005) # Vector for rates
-
-known_sol <- NULL # Vector to hold the known closed form solution
-for (r in 1:length(xvec)){
-  known_sol[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
-}
-
-CR <- NULL # Vector to hold Crude Monte Carlo Solutions
-AV <- NULL # Vector to hold Antithetic Monte Carlo Solutions
-MM <- NULL # Vector to hold Moment Matching  Carlo Solutions
-CV <- NULL # Vector to hold Control Variates Monte Carlo Solutions
-
-Expl <- NULL # Vector to hold Explicit method Solutions
-Impl <- NULL # Vector to hold Implicit method Solutions
-Crank <- NULL # Vector to hold Crank-Nicolson Solutions
-
-# Plots of Monte Carlo Methods ----------------------------------------------------------------------
-
-for (i in 1: length(xvec)){
-  CR[i] <- Crude_Monte_Carlo(r = xvec[i])
-}
-
-for (i in 1: length(xvec)){
-  AV[i] <- Antithetic_variates(r = xvec[i])
-}
-
-for (i in 1: length(xvec)){
-  MM[i] <- Moment_Matching(r = xvec[i])
-}
-
-for (i in 1: length(xvec)){
-  CV[i] <- Control_Variates_estimate(r = xvec[i])
-}
-
-plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo Solutions vs Known Solution")
-lines(xvec, known_sol, col ="blue", lty =1.5)
-lines(xvec, AV, col ="black", lty =1.5)
-lines(xvec, MM, col ="yellow", lty =1.5)
-lines(xvec, CV, col ="green", lty =1.5)
-
-# Plots of Finite Difference Methods ----------------------------------------------------------------------
-
-for (i in 1: length(xvec)){
-  Expl[i] <- explicit(r = xvec[i], I = 1:10000)
-}
-
-for (i in 1: length(xvec)){
-  Impl[i] <- implicit(r = xvec[i])
-}
-
-for (i in 1: length(xvec)){
-  Crank[i] <- CN(r = xvec[i])
-}
-
-plot(Expl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Explicit Method vs Known Solution")
-lines(xvec, known_sol, col ="blue", lty =1.5)
-
-plot(Impl, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
-lines(xvec, known_sol, col ="blue", lty =1.5)
-
-plot(Crank, x = xvec ,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank-Nicolson Method vs Known Solution")
-lines(xvec, known_sol, col ="blue", lty =1.5)
-
-```
-
-```{r 10}
 # Comparison of results for numerical methods
@@
 # Crude Monte Carlo
-start_time <- proc.time()[1]
+start_time <- proc.time()[1] # System time before method starts
 compare_mat[1,1] <- Crude_Monte_Carlo()
-compare_mat[1,4] <- proc.time()[1] - start_time
+compare_mat[1,4] <- proc.time()[1] - start_time # Getting difference of times
 compare_mat[1,3] <- compare_mat[1,2] - compare_mat[1,1]
@@
 
-library(xtable)
+library(xtable) # package to get LaTex code for table
 xtable(compare_mat, digits = 5)
@@
 
-```{r 11}
+```{r 10}
 # Sensitivity Tests
@@
 
+# Labels for first column
 senses[1,1]="-"
@@
 
+# Plots of sensitivity tests
 par(mfrow=c(1,1))
@@
 
-```{r 12}
-#Stability Tests
+```{r 11}
+#Stability Tests for Monte Carlo methods
 
@@
 
-var(CR)
-var(AN)
-var(MM)
-var(CV)
+var(CR) # variance of crude monte carlo
+var(AN) # variance of antithetic variates
+var(MM) # variance of moment matching
+var(CV) # variance of control variates
 
@@
 
-```{r 13}
+```{r 12}
 # Convergence Tests for finite difference methods
@@
 
-time_vec <- seq(1,100,1)
+time_vec <- seq(1,100,1) # Steps to use
 
-closed <- NULL
-CN_conv <- NULL
-Impl_conv <- NULL
-Expl_conv <- NULL
+closed <- NULL # vector to hold closed form prices
+CN_conv <- NULL # vector to hold Crank-Nicolson prices
+Impl_conv <- NULL # vector to hold Implicit method prices
+Expl_conv <- NULL # vector to hold Explicit method prices
 
@@
 
+# Plot of convergence 
 par(mfrow = c(1,1))
@@
 
-```{r 14}
+```{r 13}
 # Covergence tests for Monte Carlo functions
+# Varying time steps
 
-trials_vec <- seq(10,2000,50)
+trials_vec <- seq(10,2000,50) # Vector holding time steps
 
-closed_1 <- NULL
-CR_conv <- NULL
-AV_conv <- NULL
-MM_conv <- NULL
-CV_conv <- NULL
+closed_1 <- NULL # vector to hold closed form prices
+CR_conv <- NULL # vector to hold Crude Monte Carlo prices
+AV_conv <- NULL # vector to hold Antithetic Variates prices
+MM_conv <- NULL # vector to hold Moment Matching prices
+CV_conv <- NULL # vector to hold Control Variates prices
 
@@
 
+# Plot of convergence
 plot(closed_1, x = trials_vec, type = "l",ylim = c(0.57,0.70), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")

### 2018-10-13 ZCB Pricing .Rmd
fifa

@@
 
-Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
+Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=10000,s=1250){
 
@@
   sim_path[1,]= r # Initial rates on first row.
-  z=rnorm(n)# Generation of standard normal random variables
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
-Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
+Antithetic_variates = function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=10000,s=1250){
 
@@
   sim_path_inv[1,] = r
-  z = rnorm(n) # Generate standard normal values
-  z. = -z # Negative RV
 
   for (i in 1:n){
+    z = rnorm(1)# Generate standard normal values
+    z.=-z
     for (j in 2:(s+1)){
-      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Same Euler Discretization as in the Crude Monte Carlo function
-      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i] # Euler Discretization for the use of -Z_i
+      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z # Same Euler Discretization as in the Crude Monte Carlo function
+      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z. # Euler Discretization for the use of -Z_i
       sim_path[j,i] =sim_path[j-1,i]+dr
@@
 
-Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 1000, s = 1250){
+Moment_Matching = function(alpha = 0.08, beta = 0.8, sigma = 0.005, T = 5,r = 0.08, n = 10000, s = 1250){
 
@@
 
-CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=1000,s=1250){
+CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=5,r = 0.08,n=10000,s=1250){
 
@@
   sim_path[1,]= r
-  z=rnorm(n) # Generation of standard normal variables
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[i]*sqrt(sim_path[j-1,i]))# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
-Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=1000,s=1250){
+Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08,n=10000,s=1250){
   Crude_Monte_Carlo(alpha,beta,sigma,T,r,n,s)- CIR_MC(alpha,beta,sigma,T,r,n,s)+bond_price_CIR(alpha,beta,sigma,t,T,r)
@@
 
-trials_vec <- seq(10,2000,50) # Vector holding time steps
+trials_vec <- seq(10,10000,50) # Vector holding time steps
 

### 2018-10-15 ZCB Pricing .Rmd
NEW MC

@@
   sim_path[1,]= r # Initial rates on first row.
+  z = rnorm(n)
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 
+    z = rnorm(n)# Generate standard normal values
+    z.=-z
+
   for (i in 1:n){
-    z = rnorm(1)# Generate standard normal values
-    z.=-z
+
     for (j in 2:(s+1)){
-      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z # Same Euler Discretization as in the Crude Monte Carlo function
-      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z. # Euler Discretization for the use of -Z_i
+      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j] # Same Euler Discretization as in the Crude Monte Carlo function
+      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j] # Euler Discretization for the use of -Z_i
       sim_path[j,i] =sim_path[j-1,i]+dr
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] 
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j] 
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sim_path[1,]= r
+  z <- rnorm(n)
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[j]*sqrt(sim_path[j-1,i]))# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr

### 2018-10-18 ZCB Pricing .Rmd

@@
   sim_path[1,]= r # Initial rates on first row.
-  z = rnorm(n)
+  z = matrix(nrow=n, ncol=s)
+  for (i in 1:n){
+    z[i,]=rnorm(s)
+  }
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sim_path_inv[1,] = r
-
-    z = rnorm(n)# Generate standard normal values
+  z = matrix(nrow=n, ncol=s)
+  for (i in 1:n){
+    z[i,]=rnorm(s)
+  }
   z.=-z
@@
     for (j in 2:(s+1)){
-      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j] # Same Euler Discretization as in the Crude Monte Carlo function
-      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j] # Euler Discretization for the use of -Z_i
+      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1] # Same Euler Discretization as in the Crude Monte Carlo function
+      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i,j-1] # Euler Discretization for the use of -Z_i
       sim_path[j,i] =sim_path[j-1,i]+dr
@@
   sim_path[1,]= r
-  z=rnorm(n)
-  z_m= z-mean(z) # Moment matching transformation of Z_i to match finite moments
+  z = matrix(nrow=n, ncol=s)
+  for (i in 1:n){
+    z[i,]=rnorm(s)
+  }
+
+  z_m = matrix(nrow=n, ncol=s)
+  for (i in 1:n){
+    z_m[i,]=z[i,]-mean(z[i,])
+  }
+  # Moment matching transformation of Z_i to match finite moments
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j] 
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i,j-1] 
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sim_path[1,]= r
-  z <- rnorm(n)
+  z = matrix(nrow=n, ncol=s)
+  for (i in 1:n){
+    z[i,]=rnorm(s)
+  }
 
@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[j]*sqrt(sim_path[j-1,i]))# Euler Discretization
+      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[i,j-1]*sqrt(sim_path[j-1,i]))# Euler Discretization
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
 # Plot of convergence
-plot(closed_1, x = trials_vec, type = "l",ylim = c(0.57,0.70), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.619,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
 lines(x = trials_vec, y = CR_conv, type = "l", lty = 1, lwd =1.5)

### 2018-10-18 ZCB Pricing .Rmd

@@
 # Plot of convergence
-plot(closed_1, x = trials_vec, type = "l",ylim = c(0.619,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
 lines(x = trials_vec, y = CR_conv, type = "l", lty = 1, lwd =1.5)
@@
 
-legend(x = 600, y = 0.62, legend = c("Closed Form", "Crude Monte Carlo", "Antithetic Variates"), lty = c(2,1,1), lwd =c(1.5,1.5,1.5),col = c("black","black","blue"), cex = 0.8, bty="n")
+legend(x = 600, y = 0.62, legend = c("Closed Form", "Crude Monte Carlo", "Antithetic Variates"), lty = c(2,1,1), lwd =c(1.5,1.5,1.5),col = c("black","black","blue"), cex = 0.9, bty="n")
 
-legend(x = 1200, y = 0.62, legend = c("Moment Matching","Control Variates"), lty = c(1,1), lwd =c(1.5,1.5),col = c("green","red"), cex = 0.8, bty="n")
+legend(x = 5000, y = 0.62, legend = c("Moment Matching","Control Variates"), lty = c(1,1), lwd =c(1.5,1.5),col = c("green","red"), cex = 0.9, bty="n")
 

### 2018-10-18 ZCB Pricing .Rmd

@@
 
-plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.7), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
+plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.68), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Alpha & Beta",  xaxt = "n", col ="black", pch = 19, font.main = 1)
 axis(1, at=1:8, labels=xvec)
@@
 # Plot of convergence
-plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 2,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
+plot(closed_1, x = trials_vec, type = "l",ylim = c(0.617,0.624), xlab = "Number of Trials", ylab = "Estimated Price", lty = 2, lwd = 3,font.main = 1, main = "Monte Carlo Bond Prices over Number of Trials")
 lines(x = trials_vec, y = CR_conv, type = "l", lty = 1, lwd =1.5)
-lines(x = trials_vec, y = AV_conv, type = "l", lty = 1, col = "blue", lwd =1.5)
-lines(x = trials_vec, y = MM_conv, type = "l", lty = 1, col = "green", lwd =1.5)
-lines(x = trials_vec, y = CV_conv, type = "l", lty = 1, col = "red", lwd = 2)
+lines(x = trials_vec, y = AV_conv, type = "l", lty = 1, col = "blue", lwd =4)
+lines(x = trials_vec, y = MM_conv, type = "l", lty = 1, col = "green", lwd =3)
+lines(x = trials_vec, y = CV_conv, type = "l", lty = 1, col = "red", lwd = 1.5)
 
-legend(x = 600, y = 0.62, legend = c("Closed Form", "Crude Monte Carlo", "Antithetic Variates"), lty = c(2,1,1), lwd =c(1.5,1.5,1.5),col = c("black","black","blue"), cex = 0.9, bty="n")
+legend(x = 600, y = 0.621, legend = c("Closed Form", "Crude Monte Carlo", "Antithetic Variates"), lty = c(2,1,1), lwd =c(1.5,1.5,1.5),col = c("black","black","blue"), cex = 0.9, bty="n")
 
-legend(x = 5000, y = 0.62, legend = c("Moment Matching","Control Variates"), lty = c(1,1), lwd =c(1.5,1.5),col = c("green","red"), cex = 0.9, bty="n")
+legend(x = 5000, y = 0.621, legend = c("Moment Matching","Control Variates"), lty = c(1,1), lwd =c(1.5,1.5),col = c("green","red"), cex = 0.9, bty="n")
 

### 2018-10-18 ZCB Pricing .Rmd
gummy worm

--- 2018-10-18 ZCB Pricing .Rmd
@@
   CR[i]=Crude_Monte_Carlo()
+
+}
+
+for (i in 1:100){
   AN[i]=Antithetic_variates()
+
+}
+
+for (i in 1:100){
   MM[i]=Moment_Matching()
+
+}
+
+for (i in 1:100){
   CV[i]=Control_Variates_estimate()
@@
 
-var(CR) # variance of crude monte carlo
-var(AN) # variance of antithetic variates
-var(MM) # variance of moment matching
-var(CV) # variance of control variates
+VarCR=var(CR) # variance of crude monte carlo
+VarAN=var(AN) # variance of antithetic variates
+VarMM=var(MM) # variance of moment matching
+varCV=var(CV) # variance of control variates
 

### 2018-10-18 ZCB Pricing .Rmd
Comments added

@@
   sim_path[1,]= r # Initial rates on first row.
-  z = matrix(nrow=n, ncol=s)
+  z = matrix(nrow=n, ncol=s) # Create a matrix of standardised normal random variables
   for (i in 1:n){
@@
   for (i in 1:n){
-    z[i,]=rnorm(s)
+    z[i,]=rnorm(s)# Create a matrix of standardised normal random variables
   }
-  z.=-z
+  z.=-z #Take the negative of above matrix
 
@@
   for (i in 1:n){
-    z[i,]=rnorm(s)
+    z[i,]=rnorm(s) # Create a matrix of standardised normal random variables
   }
@@
   for (i in 1:n){
-    z_m[i,]=z[i,]-mean(z[i,])
+    z_m[i,]=z[i,]-mean(z[i,]) # Perform the moment matching transformation on the                                 above generated random variables
   }
@@
 
+# Determine the price under each method 100 times
 for ( i in 1:100){

### 2018-10-19 ZCB Pricing .Rmd
Comment changes

@@
   sim_path[1,]= r # Initial rates on first row.
+
   z = matrix(nrow=n, ncol=s) # Create a matrix of standardised normal random variables
@@
   int = exp(-Sum) # Take the exponent of the Integral
-  mean = mean(int) # Find the average of expression
+  mean = mean(int) # Find the average of expressions
   mean
@@
   sim_path_inv[1,] = r
-  z = matrix(nrow=n, ncol=s)
+
+   z = matrix(nrow=n, ncol=s) # Create a matrix of standardised normal random variables
   for (i in 1:n){
-    z[i,]=rnorm(s)# Create a matrix of standardised normal random variables
+    z[i,]=rnorm(s)
   }
@@
 
-# Make use of the CIR model as the control variate process.
-# Below is the closed form solution under the CIR model
+# Make use of the Cox Ingeresoll Ross (CIR) model as the control variate process.
+# Below is the closed form solution of a ZCB under the CIR model
 bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=5,r = 0.08){
@@
 }
-# The control variate estimate is taken as the difference between the the Crude MOnte carlo estimates of the Vasicek and CIR model plus the closed form of the CIR model
+# The control variate estimate is taken as the difference between the the Crude Monte Carlo estimates of the Vasicek and CIR model plus the closed form solution of the CIR model
 
@@
 
+#Interest rate changes
+#==============================================================================#
 #r=0.05
@@
 
+#Time to maturity changes
+#==============================================================================#
 #T=1
@@
 
+#Changes to the sigma parameter
+#===============================================================================#
 #sigma=0.001
@@
 
+#Changes to the alpha parameter
+#===============================================================================#
 #alpha=0.01
@@
 
+#Changes to the beta value
+#===============================================================================#
 #beta=0.1
@@
 
+#Changes to the alpha and beta parameter
+#===============================================================================#
 #alpha=0.01,beta=0.1

### 2018-10-19 ZCB Pricing .Rmd
New comments and final code

@@
     for (j in 2:(s+1)){
-      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
+      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i,j-1]# Discretize the SDE of the interest model using the Euler Discretization to simulate rates over discrete sub-intervals
       sim_path[j,i]=sim_path[j-1,i]+dr
@@
   sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using negative values of RV
-  sim_path[1,] = r
+  sim_path[1,] = r # Inital rates on first row
   sim_path_inv[1,] = r
@@
   for (i in 1:n){
-
     for (j in 2:(s+1)){
@@
 }
-# The control variate estimate is taken as the difference between the the Crude Monte Carlo estimates of the Vasicek and CIR model plus the closed form solution of the CIR model
+# The Control Variate estimate is taken as the difference between the the Crude Monte Carlo estimates of the Vasicek and CIR model plus the closed form solution of the CIR model
 
@@
 
-compare_mat[,2] <- bond_price()
+compare_mat[,2] <- bond_price() # Known solution bond price
 
@@
 library(xtable) # package to get LaTex code for table
-xtable(compare_mat, digits = 5)
+xtable(compare_mat, digits = 5) # Output of LaTex code for table
 
@@
 library(xtable) 
-xtable(senses, digits = 5)
+xtable(senses, digits = 5) # Table for data on sensitvity tests found in appendix B
 ```
@@
 
-VarCR=var(CR) # variance of crude monte carlo
-VarAN=var(AN) # variance of antithetic variates
-VarMM=var(MM) # variance of moment matching
-varCV=var(CV) # variance of control variates
+VarCR=var(CR) # variance of Crude Monte Carlo
+VarAN=var(AN) # variance of Antithetic Variates
+VarMM=var(MM) # variance of Moment Matching
+varCV=var(CV) # variance of Control Variates
 
